---
title: "M21 2026 July 2026 N400 Component"
author: "Joanna Morris"
date: "`r Sys.Date()`"
output: 
  bookdown::pdf_document2:
    toc: true
    toc_depth: 4
    number_sections: true
header-includes:
  - \setcounter{secnumdepth}{3}
editor_options: 
  chunk_output_type: inline
---

\scriptsize

# Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE, 
                      error = FALSE,
                      comment = "||",
                      fig.height = 4,
                      fig.width = 7)
options(width = 150)
```

Load libraries

```{r load_libraries, echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(ggeffects)
library(lme4)
library(afex)
library(gridExtra)
library(MuMIn)
library(pbkrtest)
library(effectsize)
library(performance)
library(cowplot)  # for use with `plot_grid(x,x,ncol = x)` function
library(e1071) # for use with `skewness()` function
library(lmerTest)
library(emmeans)
# emm_options(lmer.df = "satterthwaite")
```

Set emmeans options

```{r emmeans_options}
emm_options(
  lmer.df = "kenward-roger",
  pbkrtest.limit = 10000,
  disable.pbkrtest = FALSE
)
```

Set ggplot parameters

```{r ggplot_parameters}
# Color palette
my_palette_1 <- c(
  "#E31A1C",   # red
  "#1F78B4"  # blue
)

my_palette_2 <- c(
  "#0072B2",  # dark blue
  "#E69F00"   # orange/gold
)
my_linetypes_1 <- c("dashed", "solid")

# Theme
my_theme <- theme_classic(base_size = 8) +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal",
    legend.box = "horizontal"
  )

# Common guides
my_guides <- guides(
  colour = guide_legend(nrow = 1),
  fill   = guide_legend(nrow = 1)
)

```

Define 2-way interaction table function

Function use for Complexity × LP table:
``` 
emm_complexity_LP_N400 <- emmeans(
  m_nw_N400_fs,
  ~ complexity | LP,
  at = list(LP = c(-1, 0, 1))
)

compact_emm_table(
  emm_complexity_LP_N400,
  by_var = LP,
  condition_prefix = "LP"
)
```
for Family Size × LP table:
```
emm_FS_LP_N400 <- emmeans(
  m_nw_N400_fs,
  ~ family_size | LP,
  at = list(LP = c(-1, 0, 1))
)

compact_emm_table(
  emm_FS_LP_N400,
  by_var = LP,
  condition_prefix = "LP"
)
```


```{r interaction_table_function.2way, echo=FALSE}
compact_emm_table <- function(emm_object,
                              by_var,
                              condition_prefix = NULL,
                              digits_est = 2,
                              digits_df = 1,
                              digits_p = 3) {
  
  by_var_name <- rlang::as_name(rlang::ensym(by_var))
  
  emm_df <- summary(emm_object) |>
    as.data.frame()
  
  contrast_df <- pairs(emm_object) |>
    summary() |>
    as.data.frame()
  
  # Focal factor columns are the EMM columns other than the conditioning variable
  focal_vars <- setdiff(
    names(emm_df),
    c(by_var_name, "emmean", "SE", "df", "lower.CL", "upper.CL")
  )
  
  emm_part <- emm_df |>
    rowwise() |>
    mutate(
      Comparison = paste(c_across(all_of(focal_vars)), collapse = " "),
      Condition = if (is.null(condition_prefix)) {
        as.character(.data[[by_var_name]])
      } else {
        paste(condition_prefix, "=", .data[[by_var_name]])
      }
    ) |>
    ungroup() |>
    transmute(
      Comparison,
      Condition,
      Estimate = emmean,
      SE,
      df,
      lower.CL,
      upper.CL,
      t.ratio = NA_real_,
      p.value = NA_real_
    )
  
  contrast_part <- contrast_df |>
    mutate(
      Comparison = contrast,
      Condition = if (is.null(condition_prefix)) {
        as.character(.data[[by_var_name]])
      } else {
        paste(condition_prefix, "=", .data[[by_var_name]])
      }
    ) |>
    transmute(
      Comparison,
      Condition,
      Estimate = estimate,
      SE,
      df,
      lower.CL = NA_real_,
      upper.CL = NA_real_,
      t.ratio,
      p.value
    )
  
  bind_rows(emm_part, contrast_part) |>
    arrange(Condition, Comparison) |>
    mutate(
      Estimate = round(Estimate, digits_est),
      SE       = round(SE, digits_est),
      df       = round(df, digits_df),
      lower.CL = round(lower.CL, digits_est),
      upper.CL = round(upper.CL, digits_est),
      t.ratio  = round(t.ratio, digits_est),
      p.value  = round(p.value, digits_p)
    )
}
```


For 3-way use this function like this:

```
emm_3way <- emmeans(
  m_nw_N400_fs,
  ~ complexity * family_size | LP,
  at = list(LP = c(-1, 0, 1))
)

compact_3way_table(
  emm_3way,
  by_var = LP,
  condition_prefix = "LP",
  factor1 = complexity,
  factor2 = family_size
)
```

```{r interaction_table_function.3way, echo=FALSE}
compact_3way_table <- function(emm_object,
                               by_var,
                               condition_prefix = NULL,
                               factor1,
                               factor2,
                               digits_est = 2,
                               digits_df = 1,
                               digits_p = 3) {
  
  by_var_name <- rlang::as_name(rlang::ensym(by_var))
  factor1_name <- rlang::as_name(rlang::ensym(factor1))
  factor2_name <- rlang::as_name(rlang::ensym(factor2))
  
  emm_df <- summary(emm_object) |>
    as.data.frame()
  
  make_condition <- function(x) {
    if (is.null(condition_prefix)) {
      as.character(x[[by_var_name]])
    } else {
      paste(condition_prefix, "=", x[[by_var_name]])
    }
  }
  
  emm_part <- emm_df |>
    mutate(
      Comparison = paste(.data[[factor1_name]], .data[[factor2_name]]),
      Condition = make_condition(pick(everything()))
    ) |>
    transmute(
      Comparison,
      Condition,
      Estimate = emmean,
      SE,
      df,
      lower.CL,
      upper.CL,
      t.ratio = NA_real_,
      p.value = NA_real_
    )
  
  factor1_part <- pairs(emm_object, simple = factor1_name) |>
    summary() |>
    as.data.frame() |>
    mutate(
      Comparison = contrast,
      Condition = paste(
        if (is.null(condition_prefix)) .data[[by_var_name]] else paste(condition_prefix, "=", .data[[by_var_name]]),
        "|",
        factor2_name, "=",
        .data[[factor2_name]]
      )
    ) |>
    transmute(
      Comparison,
      Condition,
      Estimate = estimate,
      SE,
      df,
      lower.CL = NA_real_,
      upper.CL = NA_real_,
      t.ratio,
      p.value
    )
  
  factor2_part <- pairs(emm_object, simple = factor2_name) |>
    summary() |>
    as.data.frame() |>
    mutate(
      Comparison = contrast,
      Condition = paste(
        if (is.null(condition_prefix)) .data[[by_var_name]] else paste(condition_prefix, "=", .data[[by_var_name]]),
        "|",
        factor1_name, "=",
        .data[[factor1_name]]
      )
    ) |>
    transmute(
      Comparison,
      Condition,
      Estimate = estimate,
      SE,
      df,
      lower.CL = NA_real_,
      upper.CL = NA_real_,
      t.ratio,
      p.value
    )
  
  interaction_part <- contrast(
  emm_object,
  interaction = c("pairwise", "pairwise")
) |>
  summary() |>
  as.data.frame() |>
  mutate(
    Comparison = paste0(
      "Int: ",
      .data[[paste0(factor1_name, "_pairwise")]],
      " across ",
      .data[[paste0(factor2_name, "_pairwise")]]
    ),
    Condition = make_condition(cur_data())
  ) |>
  transmute(
    Comparison,
    Condition,
    Estimate = estimate,
    SE,
    df,
    lower.CL = NA_real_,
    upper.CL = NA_real_,
    t.ratio,
    p.value
  )
  
  bind_rows(
    emm_part         |> mutate(RowType = 1),
    factor1_part     |> mutate(RowType = 2),
    factor2_part     |> mutate(RowType = 2),
    interaction_part |> mutate(RowType = 3)
  ) |>
    arrange(Condition, RowType, Comparison) |>
    mutate(
      Estimate = round(Estimate, digits_est),
      SE       = round(SE, digits_est),
      df       = round(df, digits_df),
      lower.CL = round(lower.CL, digits_est),
      upper.CL = round(upper.CL, digits_est),
      t.ratio  = round(t.ratio, digits_est),
      p.value  = round(p.value, digits_p)
    ) |>
    select(-RowType)
}
```


# Load Files

```{r load_files, message=FALSE, warning=FALSE}

# Load data: rt words

rt_w <- read_csv("rt_words_frq.csv") |>
  filter(correct == 1) |>
  mutate(
    SubjID = factor(SubjID),
    Item   = factor(target),
    logRT  = log(response_time),
    OS     = as.numeric(Dim.2),
    LP     = as.numeric(Dim.1),
    zLogBF = as.numeric(scale(LogBF)),
    zLogFS = as.numeric(scale(LogFS))
  )

# Load data: rt nonwords
rt_nw <- read_csv("rt_nwords_frq.csv") |>
  filter(correct == 1) |>
  mutate(
    SubjID = factor(SubjID),
    ItemID = factor(ItemID),
    complexity = factor(complexity,
                    levels = c("SIMP", "COMP"),
                    labels = c("Simple", "Complex")),
    logRT  = log(response_time),
    OS     = as.numeric(Dim.2),
    LP     = as.numeric(Dim.1),
    zLogBF = as.numeric(scale(LogBF)),
    zLogFS = as.numeric(scale(LogFS))
  )

# Load data: erp_fs words
erp_fs_w <- read_csv("erp_fs_dmg_words.csv") |>
  mutate(
    SubjID = factor(SubjID),
    chlabel = factor(chlabel),
    family_size = factor(family_size, 
                         levels = c("Small", "Large")),
    time_window = factor(time_window),
    OS = as.numeric(Dim.2),
    LP = as.numeric(Dim.1)
  )

# Load data: erp_fs nonwords
erp_fs_nw <- read_csv("erp_fs_dmg_nonwords.csv") |>
  mutate(
    SubjID = factor(SubjID),
    chlabel = factor(chlabel),
    family_size = factor(family_size, 
                         levels = c("Small", "Large")),
    complexity = factor(complexity,
                    labels = c("Simple", "Complex")),
    time_window = factor(time_window),
    OS = as.numeric(Dim.2),
    LP = as.numeric(Dim.1)
  )

# Load data: erp_bf words
erp_bf_w <- read_csv("erp_bf_dmg_words.csv") |>
  mutate(
    SubjID = factor(SubjID),
    chlabel = factor(chlabel),
    base_frequency = factor(base_frequency, 
                            levels = c("Low", "High")),
    time_window = factor(time_window),
    OS = as.numeric(Dim.2),
    LP = as.numeric(Dim.1)
  )

# Load data: erp_bf nonwords
erp_bf_nw <- read_csv("erp_bf_dmg_nonwords.csv") |>
  mutate(
    SubjID = factor(SubjID),
    chlabel = factor(chlabel),
    base_frequency = factor(base_frequency, 
                            levels = c("Low", "High")),
    complexity = factor(complexity,
                    labels = c("Simple", "Complex")),
    time_window = factor(time_window),
    OS = as.numeric(Dim.2),
    LP = as.numeric(Dim.1)
  )
```



```{r}
range(erp_fs_w$LP)
range(erp_fs_w$OS)
```


# N400 WORD DATA: INTERACTION WITH LP (PRIMARY ANALYSES)

## N400 WORD DATA: BASE FREQUENCY and LP as FIXED EFFECTS; OS as COVARIATE

### Model

```{r anova_N400_words_bf}
contrasts(erp_bf_w$base_frequency) <- c(-0.5, 0.5)

m_w_N400_bf <- lmer(
  value ~ base_frequency * LP + OS +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_bf_w, time_window == "N400"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_w_N400_bf)

# Effect sizes for individual terms
eta_squared(m_w_N400_bf, partial = TRUE)

# Model R²
r2_nakagawa(m_w_N400_bf)
```

### Means and Contrasts

```{r means_N400_words_bf}
as.tibble(emmeans(m_w_N400_bf, ~ base_frequency)) |> print()

emm_bf_LP <- emmeans(m_w_N400_bf,
                      ~ base_frequency | LP,
                      at = list(LP = c(-2.5, -1, 0, 1, 3)))

emm_part <- summary(emm_bf_LP) |>
  as.data.frame() |>
  transmute(LP, Effect = paste("EMM:", base_frequency), Estimate = emmean, SE, df, 
            lower.CL, upper.CL, t.ratio = NA_real_, p.value = NA_real_)

contrast_part <- pairs(emm_bf_LP) |>
  summary() |>
  as.data.frame() |>
  transmute(LP, Effect = paste("Contrast:", contrast), Estimate = estimate, SE, df,
            lower.CL = NA_real_, upper.CL = NA_real_, t.ratio, p.value)

emm_contrast_table_LP_N400_words <- bind_rows(emm_part, contrast_part) |>
  arrange(LP, Effect)|>
  mutate(
    Estimate = round(Estimate, 2),
    SE       = round(SE, 2),
    df       = round(df, 1),
    lower.CL = round(lower.CL, 2),
    upper.CL = round(upper.CL, 2),
    t.ratio  = round(t.ratio, 2),
    p.value  = round(p.value, 3)
  )

as.tibble(emm_contrast_table_LP_N400_words, digits = 3) |> print(n=20)
```
### Plots

```{r plot_N400_words_bf, include=FALSE}

# Predicted values across the observed range of LP

# pred <- ggpredict(
#   m_w_N400_bf,
#   terms = c("LP", "base_frequency")
# )

(pred_BF_LP <- ggemmeans(
  m_w_N400_bf,
  terms = c(
    "LP [all]",
    "base_frequency"
  )
))

(BFxLP_n400 <- ggplot(pred_BF_LP,
       aes(x = x,
           y = predicted,
           color = group,
           fill = group,
           linetype = group)) +
  geom_line(size = 1.2) +
  geom_ribbon(aes(ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              colour = NA) +
  labs(
    x = "Language Proficiency (LP)",
    y = "Predicted N400 amplitude (µV)",
    color = "Base Frequency",
    fill = "Base Frequency",
    linetype = "Base Frequency"
  )  +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  scale_linetype_manual(values = my_linetypes_1) +
  my_theme +
  my_guides)
```

## N400 WORD DATA: FAMILY SIZE and LP as FIXED EFFECTS; OS as COVARIATE

### Model

```{r anova_N400_words_fs}
contrasts(erp_fs_w$family_size) <- c(-0.5, 0.5)

m_w_N400_fs <- lmer(
  value ~ family_size * LP + OS +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_fs_w, time_window == "N400"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_w_N400_fs)

# Effect sizes for individual terms
eta_squared(m_w_N400_fs, partial = TRUE)

# Model R²
r2_nakagawa(m_w_N400_fs)
```

### Means

```{r means_N400_words_fs}
as.tibble(emmeans(m_w_N400_fs, ~ family_size)) |> print()
```

### Plots (Interaction Not significant)

```{r plots_N400_words_fs, include=FALSE}
# Predicted values across the observed range of LP

# pred <- ggpredict(
#   m_w_N400_fs,
#   terms = c("LP", "family_size")
# )

(pred_FS_LP <- ggemmeans(
  m_w_N400_fs,
  terms = c(
    "LP [all]",
    "family_size"
  )
))

(FSxLP_n400 <- ggplot(pred_FS_LP,
       aes(x = x,
           y = predicted,
           color = group,
           fill = group,
           linetype = group)) +
  geom_line(size = 1.2) +
  geom_ribbon(aes(ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              colour = NA) +
  labs(
    x = "Language Proficiency (LP)",
    y = "Predicted N400 amplitude (µV)",
    title = "Interaction Not Significant",
    color = "Family Size",
    fill = "Family Size",
    linetype = "Family Size"
  )  +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  scale_linetype_manual(values = my_linetypes_1) +
  my_theme +
  my_guides)
```

## N400 WORD DATA: Interaction Plots— BASE FREQUENCY x LP; FAMILY SIZE x  LP 

```{r  fig.width=5, fig.height=3}
row1 <- plot_grid(BFxLP_n400,FSxLP_n400,ncol = 2)

plot_grid(
  ggdraw() + draw_label("N400 Word Data", fontface = "bold"),
  row1,
  ncol = 1,
  rel_heights = c(0.08, 1)
)
```

Does the slopes of the lines in the significant interactions, significantly differ from zero?

```{r}
test(emtrends(m_w_N400_bf, ~ base_frequency, var = "LP"))
```



# N400 WORD DATA: INTERACTION WITH OS (EXPLORATORY ANALYSES)
## N400 WORD DATA: BASE FREQUENCY and OS as FIXED EFFECTS; LP as COVARIATE 

```{r}
# BINNED BY BASE FREQUENCY
m_w_N400_bf_OS <- lmer(
  value ~ base_frequency * OS + LP +
    (1 | SubjID) + (1 | SubjID:chlabel),
  data = subset(erp_bf_w, time_window == "N400"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_w_N400_bf_OS)
```

## N400 WORD DATA: FAMILY SIZE and OS as FIXED EFFECTS; LP as COVARIATE


```{r}
# BINNED BY FAMILY SIZE

m_w_N400_fs_OS <- lmer(
  value ~ family_size * OS + LP +
    (1 | SubjID) + (1 | SubjID:chlabel),
  data = subset(erp_fs_w, time_window == "N400"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_w_N400_fs_OS)
```

\newpage

# N400 NONWORD DATA : SYMMETRICAL MODEL, INTERACTION WITH LP AND OS

For the nonword N400, does the symmetric model we just ran replace the separate LP and OS models, or do all three get reported?**

The symmetric model is the cleanest solution — it tests both dimensions in the same model and provides the strongest evidence for the dissociation. The separate models are now superseded.

## N400 NONWORD DATA: Family Size

### Symmetric Model
```{r}
contrasts(erp_fs_nw$complexity) <- c(-0.5, 0.5)
contrasts(erp_fs_nw$family_size) <- c(-0.5, 0.5)

m_nw_N400_fs_symmetric <- lmer(
  value ~ complexity * family_size * LP + 
          complexity * family_size * OS +
    (1 | SubjID) + (1 | SubjID:chlabel),
  data = subset(erp_fs_nw, time_window == "N400"),
  control = lmerControl(optimizer = "bobyqa")
)

summary(m_nw_N400_fs_symmetric)

# Effect Sizes
eta_squared(m_nw_N400_fs_symmetric, partial = TRUE)

# R-squared
r2_nakagawa(m_nw_N400_fs_symmetric)
```

### Means and Contrasts
#### Complexity × Family Size x LP Interaction

```{r}
emm_options(lmer.df = "satterthwaite")

range(erp_bf_nw$LP)
range(erp_bf_nw$OS)

# LP three-way follow-up
emm_3way_LP <- emmeans(m_nw_N400_fs_symmetric, 
        ~ complexity * family_size | LP,
        at = list(LP = c(-2.5, -1, 0, 1, 3)),
        lmerTest.limit = 6480)

LP_3way_contrasts <- compact_3way_table(
  emm_3way_LP,
  by_var = LP,
  condition_prefix = "LP",
  factor1 = complexity,
  factor2 = family_size
)
as.tibble(LP_3way_contrasts) |> print(n = 50)

# OS three-way follow-up
emm_3way_OS <- emmeans(m_nw_N400_fs_symmetric, 
         ~ family_size * complexity | OS,
        at = list(OS = c(-1.9, -1, 0, 1, 1.9)),
        lmerTest.limit = 6480)

OS_3way_contrasts <- compact_3way_table(
  emm_3way_OS,
  by_var = OS,
  condition_prefix = "OS",
  factor1 = complexity,
  factor2 = family_size
)
as.tibble(OS_3way_contrasts) |> print(n = 50)
```

#### Complexity × Family Size interaction averaged across LP


```{r CMPxFSoverLP}
emm_complexity_FS_N400 <- emmeans(
  m_nw_N400_fs_symmetric,
  ~ complexity | family_size,
  lmerTest.limit = 6480)

complexityxfamilysize_table <- as.tibble(compact_emm_table(
  emm_complexity_FS_N400,
  by_var = family_size
)) |> print()

emm_complexity_CMP_N400 <- emmeans(
  m_nw_N400_fs_symmetric,
  ~ family_size | complexity,
  lmerTest.limit = 6480)

familysizexcomplexity_table <- as.tibble(compact_emm_table(
  emm_complexity_CMP_N400,
  by_var = complexity
)) |> print() 

```

`transmute()` creates a new data frame containing only the specified computations.
` factor()` is used to encode a vector as a factor 

```{r include=FALSE}
# Retain only the four condition means, excluding difference scores
complexityxfamilysize_means <- complexityxfamilysize_table |>
  filter(!grepl(" - ", Comparison)) |>
    transmute(complexity = factor( Comparison,levels = c("Simple", "Complex")),
              family_size = factor(Condition,levels = c("Small", "Large")),
              Estimate,
              lower.CL,
              upper.CL)
complexityxfamilysize_means |> print(n=8)

# Plot
complexityxfamilysize_plot <- ggplot(
  complexityxfamilysize_means,
  aes(x = complexity,y = Estimate,
      group = family_size, colour = family_size, fill = family_size, linetype = family_size)) +
  geom_line(linewidth = 1) +
  geom_point(size = 3) +
  geom_ribbon(aes(ymin = lower.CL,
                  ymax = upper.CL),
              alpha = 0.2,
              colour = NA) +
  labs(x = "Complexity",
       y = "Estimated mean amplitude (µV)",
        title = "Complexity x Family Size Interaction",
        colour = "Complexity", 
        linetype = "Complexity", 
        fill = "Complexity") +
  my_theme +
  my_guides +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2)

familysizexcomplexity_plot <- ggplot(
  complexityxfamilysize_means,
  aes(x = family_size, y = Estimate, 
      group = complexity, colour = complexity, fill = complexity, linetype = complexity)) +
  geom_line(linewidth = 1) +
  geom_point(size = 3) +
  geom_ribbon(aes(ymin = lower.CL,
                  ymax = upper.CL),
              alpha = 0.2,
              colour = NA) +
  labs( x = "Family size", 
        y = "Estimated mean amplitude (µV)",
        title = "Family Size x Complexity Interaction",
        colour = "Complexity", 
        linetype = "Complexity", 
        fill = "Complexity") +
  my_theme +
  my_guides +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2)
```

#### Complexity × LP interaction averaged over Family Size:

```{r CMPxLPoverFS}
emm_complexity_LP_N400 <- emmeans(
  m_nw_N400_fs_symmetric,
  ~ complexity | LP,
  at = list(LP = c(-2.5, -1, 0, 1, 3)),
  lmerTest.limit = 6480
)

complexityxLP_table <- as.tibble(compact_emm_table(
  emm_complexity_LP_N400,
  by_var = LP,
  condition_prefix = "LP"
)) |> print(n = 20)
```

```{r include=FALSE}
complexityxLP_means <- complexityxLP_table |>
  filter(!grepl(" - ", Comparison)) |>
  mutate(
    LP = as.numeric(sub("LP = ", "", Condition)),
    complexity = factor(Comparison, levels = c("Simple", "Complex"))) |>
  select(complexity, LP, Estimate)

complexityxLP_means

complexityxLP_plot.a <- ggplot(
  complexityxLP_means,
  aes( x = LP, y = Estimate, group = complexity, colour = complexity, linetype = complexity)) +
  geom_line(linewidth = 1) +
  geom_point(size = 2) +
  labs( x = "Lexical Proficiency (LP)",
        y = "Estimated mean amplitude (µV)",
        title = "Complexity x LP Interaction",
        colour = "Complexity",
        linetype = "Complexity") +
  my_theme +
  my_guides +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  coord_cartesian(
  xlim = c(-2.6, 3.1),
  ylim = c(-3.1, 2.1)
)
```

```{r include=FALSE}
# (complexityxLP_predicted_values <- ggpredict(
#   m_nw_N400_fs_symmetric,
#   terms = c("LP", "complexity")
# ))

(pred_CMP_LP <- ggemmeans(
  m_nw_N400_fs_symmetric,
  terms = c(
    "LP [all]",
    "complexity"
  )))

(complexityxLP_plot.b <- ggplot(pred_CMP_LP,
       aes(x = x,
           y = predicted,
           color = group,
           fill = group,
           linetype = group)) +
  geom_line(size = 1.2) +
  geom_ribbon(aes(ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              colour = NA) +
  labs(
    x = "Language Proficiency (LP)",
    y = "Predicted N400 amplitude (µV)",
    title = "Complexity x LP Interaction",
    color = "Complexity",
    fill = "Complexity",
    linetype = "Complexity"
  )  +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  scale_linetype_manual(values = my_linetypes_1) +
  my_theme +
  my_guides)
```

#### FS × LP interaction averaged over Complexity:

```{r FSxLPoverCMP}
emm_FS_LP_N400 <- emmeans(
  m_nw_N400_fs_symmetric,
  ~ family_size | LP,
  at = list(LP = c(-2.5, -1, 0, 1, 3)),
  lmerTest.limit = 6480
)

familysizexLP_table <- as.tibble(compact_emm_table(
  emm_FS_LP_N400,
  by_var = LP,
  condition_prefix = "LP"
)) |> print()
```


```{r include=FALSE}
(familysizexLP_means <- familysizexLP_table |>
  filter(!grepl(" - ", Comparison)) |>
  mutate(LP = as.numeric(sub("LP = ", "", Condition)),
         family_size = factor(Comparison, levels = c("Small", "Large"))) |>
  select(family_size, LP, Estimate, lower.CL, upper.CL))

familysizexLP_means

(familysizexLP_plot.a <- ggplot(
  familysizexLP_means,
  aes( x = LP, y = Estimate, 
       group = family_size, colour = family_size, fill = family_size, linetype = family_size)) +
  geom_line(linewidth = 1) +
  geom_point(size = 2) +
  labs( x = "Lexical Proficiency (LP)", 
        y = "Estimated mean amplitude (µV)",
       title = "Family Size x LP Interaction",
       colour = "Family Size", 
       linetype = "Family Size",
       fill = "Family Size") +
  my_theme +
  my_guides +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  coord_cartesian(
  xlim = c(-2.6, 3.1),
  ylim = c(-3.1, 2.1)
))
```

```{r include=FALSE}
# (familysizexLP_predicted_values <- ggpredict(
#   m_nw_N400_fs_symmetric,
#   terms = c("LP", "family_size")
# ))

(pred_FS_LP <- ggemmeans(
  m_nw_N400_fs_symmetric,
  terms = c(
    "LP [all]",
    "family_size"
  )))

(familysizexLP_plot.b <- ggplot(pred_FS_LP,
       aes(x = x,
           y = predicted,
           color = group,
           fill = group,
           linetype = group)) +
  geom_line(size = 1.2) +
  geom_ribbon(aes(ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              colour = NA) +
  labs(
    x = "Language Proficiency (LP)",
    y = "Predicted N400 amplitude (µV)",
    title = "Family Size x LP Interaction",
    color = "Family Size",
    fill = "Family Size",
    linetype = "Family Size"
  )  +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  scale_linetype_manual(values = my_linetypes_1) +
  my_theme +
  my_guides)
```

#### Complexity ×  OS interaction averaged over Family Size:

```{r COMxOSoverFS}
emm_complexity_OS_N400 <- emmeans(
  m_nw_N400_fs_symmetric,
  ~ complexity | OS,
  at = list(OS = c(-1.9, -1, 0, 1, 1.9)),
  lmerTest.limit = 6480
)

complexityxOS_table <- as.tibble(compact_emm_table(
  emm_complexity_OS_N400,
  by_var = OS,
  condition_prefix = "OS"
)) |> print(n = 20)
```

```{r include=FALSE}
(complexityxOS_means <- complexityxOS_table |>
  filter(!grepl(" - ", Comparison)) |>
  mutate(
    OS = as.numeric(sub("OS = ", "", Condition)),
    complexity = factor(Comparison, levels = c("Simple", "Complex"))
  ) |>
  select(complexity, OS, Estimate))

(complexityxOS_plot.a <- ggplot(
  complexityxOS_means,
  aes( x = OS, y = Estimate, group = complexity, colour = complexity, linetype = complexity)) +
  geom_line(linewidth = 1) +
  geom_point(size = 2) +
  labs(x = "Orthographic Sensitivity (OS)",
       y = "Estimated mean amplitude (µV)",
       title = "Complexity x OS Interaction",
       colour = "Complexity", 
       linetype = "Complexity") +
  my_theme +
  my_guides +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  coord_cartesian(
  xlim = c(-2.6, 3.1),
  ylim = c(-3.1, 2.1)
))
```

```{r include=FALSE}

# (complexityxOS_predicted_values <- ggpredict(
#   m_nw_N400_fs_symmetric,
#   terms = c("OS", "complexity")
# ))

(pred_CMP_OS <- ggemmeans(
  m_nw_N400_fs_symmetric,
  terms = c(
    "OS [all]",
    "complexity"
  )))

(complexityxOS_plot.b <- ggplot(pred_CMP_OS,
       aes(x = x,
           y = predicted,
           color = group,
           fill = group,
           linetype = group)) +
  geom_line(size = 1.2) +
  geom_ribbon(aes(ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              colour = NA) +
  labs(
    x = "Orthographic Sensitivity (OS)",
    y = "Predicted N400 amplitude (µV)",
    title = "Complexity x OS Interaction",
    color = "Complexity",
    fill = "Complexity",
    linetype = "Complexity"
  )  +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  scale_linetype_manual(values = my_linetypes_1) +
  my_theme +
  my_guides)
```

### PLOT 2-WAY INTERACTIONS

#### FAMILY SIZE X COMPLEXITY Plot

&nbsp;

```{r echo=FALSE, fig.height= 3}
plot_grid(complexityxfamilysize_plot, familysizexcomplexity_plot, ncol = 2)
```

#### COMPLEXITY x LP Plot; FAMILY SIZE X LP Plot; COMPLEXITY x OS Plot

&nbsp;

```{r include=FALSE}
plot_grid(complexityxLP_plot.a, 
          familysizexLP_plot.a, 
          complexityxOS_plot.a, 
          ncol = 3)
```

```{r echo=FALSE, fig.height=3}
plot_grid(complexityxLP_plot.b, familysizexLP_plot.b, complexityxOS_plot.b, ncol = 3 )
```


### PLOT 3-WAY INTERACTIONS

#### Plots: COMPLEXITY x LP faceted by Family size; FAMILY SIZE x  LP Faceted by Complexity 

&nbsp;

```{r plots_n400_nonwords_fs.3way, include=FALSE}
library(ggeffects)
library(ggplot2)

# Facet by Family Size
pred <- ggpredict(
  m_nw_N400_fs_symmetric,
  terms = c("LP [all]", "complexity", "family_size")
)

nw.n400.3way.A <- ggplot(pred,
       aes(x = x,
           y = predicted,
           colour = group,
           fill = group,
           linetype = group)) +
  geom_line(linewidth = 1.2) +
  geom_ribbon(aes(ymin = conf.low,
                  ymax = conf.high),
              alpha = .20,
              colour = NA) +
  facet_wrap(~facet) +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  scale_linetype_manual(values = my_linetypes_1) +
  labs(
    x = "Lexical Proficiency (LP)",
    y = "Predicted N400 amplitude (µV)",
    colour = "Complexity",
    fill = "Complexity",
    linetype = "Complexity"
  ) +
  my_theme +
  my_guides

# Facet by Complexity
pred <- ggpredict(
  m_nw_N400_fs_symmetric,
  terms = c("LP[all]", "family_size", "complexity")
)

nw.n400.3way.B <- ggplot(pred,
       aes(x = x,
           y = predicted,
           colour = group,
           fill = group,
           linetype = group)) +
  geom_line(linewidth = 1.2) +
  geom_ribbon(aes(ymin = conf.low,
                  ymax = conf.high),
              alpha = .20,
              colour = NA,
              linetype = 0) +
  facet_wrap(~facet) +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  scale_linetype_manual(values = my_linetypes_1) +
  labs(
    x = "Lexical Proficiency (LP)",
    y = "Predicted N400 amplitude (µV)",
    colour = "Family Size",
    fill = "Family Size",
    linetype = "Family Size"
  ) +
  my_theme +
  my_guides

```

&nbsp;

```{r echo=FALSE, fig.height=3, fig.width=5}
plot_grid(nw.n400.3way.B, ncol = 1)
```
 
#### COMPLEXITY x LP and FAMILY SIZE x  LP Interaction Plots

Plot Simple-Complex difference across LP

```{r include=FALSE}
library(emmeans)
library(dplyr)
library(ggplot2)

# Create a sequence of LP values across the observed range
LP_seq <- with(
  subset(erp_fs_nw, time_window == "N400"),
  seq(min(LP, na.rm = TRUE),
      max(LP, na.rm = TRUE),
      length.out = 100)
)

# Estimate complexity means at each LP value, separately by family_size
emm_complexity_by_LP_FS <- emmeans(
  m_nw_N400_fs_symmetric,
  ~ complexity | family_size * LP,
  at = list(LP = LP_seq)
)

# Compute Simple - Complex at each LP value and family_size level
complexity_diff_by_LP_FS <- pairs(emm_complexity_by_LP_FS) |>
  summary(infer = TRUE) |>
  as.data.frame()

head(complexity_diff_by_LP_FS)

# Plot graph

complexity_by_LP <- ggplot(
  complexity_diff_by_LP_FS,
  aes(x = LP,
      y = estimate,
      colour = family_size,
      fill = family_size,
      linetype = family_size)
) +
  geom_hline(yintercept = 0,
             linetype = "dashed",
             linewidth = 0.5) +
  geom_line(linewidth = 1.2) +
  geom_ribbon(aes(ymin = lower.CL,
                  ymax = upper.CL),
              alpha = 0.20,
              colour = NA) +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  labs(
    x = "Lexical Proficiency (LP)",
    y = "Simple - Complex difference in predicted N400 amplitude (µV)",
    colour = "Family Size",
    fill = "Family Size",
    linetype = "Family Size"
  ) +
  my_theme +
  my_guides
```

Plot Small Family - Large Family difference across LP

```{r include=FALSE}

library(emmeans)
library(dplyr)
library(ggplot2)

# Create a sequence of LP values across the observed range
LP_seq <- with(
  subset(erp_fs_nw, time_window == "N400"),
  seq(min(LP, na.rm = TRUE),
      max(LP, na.rm = TRUE),
      length.out = 100)
)

# Estimate family-size means at each LP value, separately by complexity
emm_family_by_LP_complexity <- emmeans(
  m_nw_N400_fs_symmetric,
  ~ family_size | complexity * LP,
  at = list(LP = LP_seq)
)

# Build an explicit Small - Large contrast
fs_levels <- emm_family_by_LP_complexity@levels$family_size

small_large_contrast <- rep(0, length(fs_levels))
small_large_contrast[fs_levels == "Small"] <-  1
small_large_contrast[fs_levels == "Large"] <- -1

# Compute Small - Large at each LP value and complexity level
family_size_diff_by_LP_complexity <- contrast(
  emm_family_by_LP_complexity,
  method = list("Small - Large" = small_large_contrast)
) |>
  summary(infer = TRUE) |>
  as.data.frame()

head(family_size_diff_by_LP_complexity)

# Plot graph
familysize_by_LP <- ggplot(
  family_size_diff_by_LP_complexity,
  aes(x = LP,
      y = estimate,
      colour = complexity,
      fill = complexity,
      linetype = complexity)
) +
  geom_hline(yintercept = 0,
             linetype = "dashed",
             linewidth = 0.5) +
  geom_line(linewidth = 1.2) +
  geom_ribbon(aes(ymin = lower.CL,
                  ymax = upper.CL),
              alpha = 0.20,
              colour = NA) +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  labs(
    x = "Lexical Proficiency (LP)",
    y = "Small - Large family-size difference in predicted N400 amplitude (µV)",
    colour = "Complexity",
    fill = "Complexity",
    linetype = "Complexity"
  ) +
  my_theme +
  my_guides
```

Print Both Plots

```{r  echo=FALSE, fig.height=4.5, fig.width=7}
row1 <- plot_grid(complexity_by_LP, familysize_by_LP,ncol = 2)

plot_grid(
  ggdraw() + draw_label("N400 NonWord Data", fontface = "bold"),
  row1,
  ncol = 1,
  rel_heights = c(0.08, 1)
)
```


#### Plots: COMPLEXITY x OS faceted by Family size; FAMILY SIZE x  OS Faceted by Complexity 

```{r 3way_OS, include=FALSE}
library(ggeffects)
library(ggplot2)

# Facet by Family Size
pred <- ggpredict(
  m_nw_N400_fs_symmetric,
  terms = c("OS [all]", "complexity", "family_size")
)

(nw.n400.3way.C <- ggplot(pred,
       aes(x = x,
           y = predicted,
           colour = group,
           fill = group,
           linetype = group)) +
  geom_line(linewidth = 1.2) +
  geom_ribbon(aes(ymin = conf.low,
                  ymax = conf.high),
              alpha = .20,
              colour = NA) +
  facet_wrap(~facet) +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  scale_linetype_manual(values = my_linetypes_1) +
  labs(
    x = "Orthographic Sensitivity (OS)",
    y = "Predicted N400 amplitude (µV)",
    colour = "Complexity",
    fill = "Complexity",
    linetype = "Complexity"
  ) +
  my_theme +
  my_guides)

# Facet by Complexity
pred <- ggpredict(
  m_nw_N400_fs_symmetric,
  terms = c("OS[all]", "family_size", "complexity")
)

(nw.n400.3way.D <- ggplot(pred,
       aes(x = x,
           y = predicted,
           colour = group,
           fill = group,
           linetype = group)) +
  geom_line(linewidth = 1.2) +
  geom_ribbon(aes(ymin = conf.low,
                  ymax = conf.high),
              alpha = .20,
              colour = NA,
              linetype = 0) +
  facet_wrap(~facet) +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  scale_linetype_manual(values = my_linetypes_1) +
  labs(
    x = "Orthographic Sensitivity (OS)",
    y = "Predicted N400 amplitude (µV)",
    colour = "Family Size",
    fill = "Family Size",
    linetype = "Family Size"
  ) +
  my_theme +
  my_guides)

```
&nbsp;

```{r echo=FALSE, fig.height=3, fig.width=5}
plot_grid( nw.n400.3way.D, ncol = 1)
```