---
title: "M21 2026 July 2026 N250 Component"
author: "Joanna Morris"
date: "`r Sys.Date()`"
output: 
  bookdown::pdf_document2:
    toc: true
    toc_depth: 3
    number_sections: true
header-includes:
  - \setcounter{secnumdepth}{3}
editor_options: 
  chunk_output_type: inline
---

\scriptsize

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE, 
                      error = FALSE,
                      comment = "||",
                      fig.height = 4,
                      fig.width = 7)
options(width = 150)
```

Load libraries

```{r load_libraries, echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(ggeffects)
library(lme4)
library(afex)
library(gridExtra)
library(MuMIn)
library(pbkrtest)
library(effectsize)
library(performance)
library(cowplot)  # for use with `plot_grid(x,x,ncol = x)` function
library(e1071) # for use with `skewness()` function
library(lmerTest)
library(emmeans)
# emm_options(lmer.df = "satterthwaite")
```

Set emmeans options

```{r emmeans_options}
emm_options(
  lmer.df = "kenward-roger",
  pbkrtest.limit = 10000,
  disable.pbkrtest = FALSE
)
```

Set ggplot parameters

```{r ggplot_parameters}
# Color palette
my_palette_1 <- c(
  "#E31A1C",   # red
  "#1F78B4"  # blue
)

my_palette_2 <- c(
  "#0072B2",  # dark blue
  "#E69F00"   # orange/gold
)
my_linetypes_1 <- c("dashed", "solid")

# Theme
my_theme <- theme_classic(base_size = 10) +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal",
    legend.box = "horizontal"
  )

# Common guides
my_guides <- guides(
  colour = guide_legend(nrow = 1),
  fill   = guide_legend(nrow = 1)
)

```

Define 2-way interaction table function

```{r interaction_table_function.2way, echo=FALSE}
compact_emm_table <- function(emm_object,
                              by_var,
                              condition_prefix = NULL,
                              digits_est = 2,
                              digits_df = 1,
                              digits_p = 3) {
  
  by_var_name <- rlang::as_name(rlang::ensym(by_var))
  
  emm_df <- summary(emm_object) |>
    as.data.frame()
  
  contrast_df <- pairs(emm_object) |>
    summary() |>
    as.data.frame()
  
  # Focal factor columns are the EMM columns other than the conditioning variable
  focal_vars <- setdiff(
    names(emm_df),
    c(by_var_name, "emmean", "SE", "df", "lower.CL", "upper.CL")
  )
  
  emm_part <- emm_df |>
    rowwise() |>
    mutate(
      Comparison = paste(c_across(all_of(focal_vars)), collapse = " "),
      Condition = if (is.null(condition_prefix)) {
        as.character(.data[[by_var_name]])
      } else {
        paste(condition_prefix, "=", .data[[by_var_name]])
      }
    ) |>
    ungroup() |>
    transmute(
      Comparison,
      Condition,
      Estimate = emmean,
      SE,
      df,
      lower.CL,
      upper.CL,
      t.ratio = NA_real_,
      p.value = NA_real_
    )
  
  contrast_part <- contrast_df |>
    mutate(
      Comparison = contrast,
      Condition = if (is.null(condition_prefix)) {
        as.character(.data[[by_var_name]])
      } else {
        paste(condition_prefix, "=", .data[[by_var_name]])
      }
    ) |>
    transmute(
      Comparison,
      Condition,
      Estimate = estimate,
      SE,
      df,
      lower.CL = NA_real_,
      upper.CL = NA_real_,
      t.ratio,
      p.value
    )
  
  bind_rows(emm_part, contrast_part) |>
    arrange(Condition, Comparison) |>
    mutate(
      Estimate = round(Estimate, digits_est),
      SE       = round(SE, digits_est),
      df       = round(df, digits_df),
      lower.CL = round(lower.CL, digits_est),
      upper.CL = round(upper.CL, digits_est),
      t.ratio  = round(t.ratio, digits_est),
      p.value  = round(p.value, digits_p)
    )
}
```

```{r interaction_table_function.3way, echo=FALSE}
compact_3way_table <- function(emm_object,
                               by_var,
                               condition_prefix = NULL,
                               factor1,
                               factor2,
                               digits_est = 2,
                               digits_df = 1,
                               digits_p = 3) {
  
  by_var_name <- rlang::as_name(rlang::ensym(by_var))
  factor1_name <- rlang::as_name(rlang::ensym(factor1))
  factor2_name <- rlang::as_name(rlang::ensym(factor2))
  
  emm_df <- summary(emm_object) |>
    as.data.frame()
  
  make_condition <- function(x) {
    if (is.null(condition_prefix)) {
      as.character(x[[by_var_name]])
    } else {
      paste(condition_prefix, "=", x[[by_var_name]])
    }
  }
  
  emm_part <- emm_df |>
    mutate(
      Comparison = paste(.data[[factor1_name]], .data[[factor2_name]]),
      Condition = make_condition(cur_data())
    ) |>
    transmute(
      Comparison,
      Condition,
      Estimate = emmean,
      SE,
      df,
      lower.CL,
      upper.CL,
      t.ratio = NA_real_,
      p.value = NA_real_
    )
  
  factor1_part <- pairs(emm_object, simple = factor1_name) |>
    summary() |>
    as.data.frame() |>
    mutate(
      Comparison = contrast,
      Condition = paste(
        if (is.null(condition_prefix)) .data[[by_var_name]] else paste(condition_prefix, "=", .data[[by_var_name]]),
        "|",
        factor2_name, "=",
        .data[[factor2_name]]
      )
    ) |>
    transmute(
      Comparison,
      Condition,
      Estimate = estimate,
      SE,
      df,
      lower.CL = NA_real_,
      upper.CL = NA_real_,
      t.ratio,
      p.value
    )
  
  factor2_part <- pairs(emm_object, simple = factor2_name) |>
    summary() |>
    as.data.frame() |>
    mutate(
      Comparison = contrast,
      Condition = paste(
        if (is.null(condition_prefix)) .data[[by_var_name]] else paste(condition_prefix, "=", .data[[by_var_name]]),
        "|",
        factor1_name, "=",
        .data[[factor1_name]]
      )
    ) |>
    transmute(
      Comparison,
      Condition,
      Estimate = estimate,
      SE,
      df,
      lower.CL = NA_real_,
      upper.CL = NA_real_,
      t.ratio,
      p.value
    )
  
  interaction_part <- contrast(
  emm_object,
  interaction = c("pairwise", "pairwise")
) |>
  summary() |>
  as.data.frame() |>
  mutate(
    Comparison = paste0(
      "Int: ",
      .data[[paste0(factor1_name, "_pairwise")]],
      " across ",
      .data[[paste0(factor2_name, "_pairwise")]]
    ),
    Condition = make_condition(cur_data())
  ) |>
  transmute(
    Comparison,
    Condition,
    Estimate = estimate,
    SE,
    df,
    lower.CL = NA_real_,
    upper.CL = NA_real_,
    t.ratio,
    p.value
  )
  
  bind_rows(
    emm_part         |> mutate(RowType = 1),
    factor1_part     |> mutate(RowType = 2),
    factor2_part     |> mutate(RowType = 2),
    interaction_part |> mutate(RowType = 3)
  ) |>
    arrange(Condition, RowType, Comparison) |>
    mutate(
      Estimate = round(Estimate, digits_est),
      SE       = round(SE, digits_est),
      df       = round(df, digits_df),
      lower.CL = round(lower.CL, digits_est),
      upper.CL = round(upper.CL, digits_est),
      t.ratio  = round(t.ratio, digits_est),
      p.value  = round(p.value, digits_p)
    ) |>
    select(-RowType)
}
```


# Load Files

```{r load_files, message=FALSE, warning=FALSE}

# Load data: rt words

rt_w <- read_csv("rt_words_frq.csv") |>
  filter(correct == 1) |>
  mutate(
    SubjID = factor(SubjID),
    Item   = factor(target),
    logRT  = log(response_time),
    OS     = as.numeric(Dim.2),
    LP     = as.numeric(Dim.1),
    zLogBF = as.numeric(scale(LogBF)),
    zLogFS = as.numeric(scale(LogFS))
  )

# Load data: rt nonwords
rt_nw <- read_csv("rt_nwords_frq.csv") |>
  filter(correct == 1) |>
  mutate(
    SubjID = factor(SubjID),
    ItemID = factor(ItemID),
    complexity = factor(complexity,
                    levels = c("SIMP", "COMP"),
                    labels = c("Simple", "Complex")),
    logRT  = log(response_time),
    OS     = as.numeric(Dim.2),
    LP     = as.numeric(Dim.1),
    zLogBF = as.numeric(scale(LogBF)),
    zLogFS = as.numeric(scale(LogFS))
  )

# Load data: erp_fs words
erp_fs_w <- read_csv("erp_fs_dmg_words.csv") |>
  mutate(
    SubjID = factor(SubjID),
    chlabel = factor(chlabel),
    family_size = factor(family_size, 
                         levels = c("Small", "Large")),
    time_window = factor(time_window),
    OS = as.numeric(Dim.2),
    LP = as.numeric(Dim.1)
  )

# Load data: erp_fs nonwords
erp_fs_nw <- read_csv("erp_fs_dmg_nonwords.csv") |>
  mutate(
    SubjID = factor(SubjID),
    chlabel = factor(chlabel),
    family_size = factor(family_size, 
                         levels = c("Small", "Large")),
    complexity = factor(complexity,
                    labels = c("Simple", "Complex")),
    time_window = factor(time_window),
    OS = as.numeric(Dim.2),
    LP = as.numeric(Dim.1)
  )

# Load data: erp_bf words
erp_bf_w <- read_csv("erp_bf_dmg_words.csv") |>
  mutate(
    SubjID = factor(SubjID),
    chlabel = factor(chlabel),
    base_frequency = factor(base_frequency, 
                            levels = c("Low", "High")),
    time_window = factor(time_window),
    OS = as.numeric(Dim.2),
    LP = as.numeric(Dim.1)
  )

# Load data: erp_bf nonwords
erp_bf_nw <- read_csv("erp_bf_dmg_nonwords.csv") |>
  mutate(
    SubjID = factor(SubjID),
    chlabel = factor(chlabel),
    base_frequency = factor(base_frequency, 
                            levels = c("Low", "High")),
    complexity = factor(complexity,
                    labels = c("Simple", "Complex")),
    time_window = factor(time_window),
    OS = as.numeric(Dim.2),
    LP = as.numeric(Dim.1)
  )
```


# N250 WORD DATA: INTERACTION WITH OS (PRIMARY ANALYSES)

At the N250, both the base frequency and family size models tested the interaction with Orthographic Sensitivity, consistent with the prediction that early form-based processing is selectively modulated by sublexical orthographic knowledge; Language Proficiency was included as a covariate in both models.


## N250 WORD DATA: FAMILY SIZE as Fixed Effect

### Model

```{r anova_n250_words_fs}
contrasts(erp_fs_w$family_size) <- c(-0.5, 0.5)


m_w_N250_fs <- lmer(
  value ~ family_size * OS + LP +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_fs_w, time_window == "N250"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_w_N250_fs)

# Effect sizes for individual terms
eta_squared(m_w_N250_fs, partial = TRUE)

# Model R²
r2_nakagawa(m_w_N250_fs)
```

#### Means and Contrasts

```{r means_n250_words_fs}
# family size
as.tibble(emmeans(m_w_N250_fs, ~ family_size)) |> print()

emm_fs_OS <- emmeans(m_w_N250_fs,
                      ~ family_size | OS,
                      at = list(OS = c(-1.9, -1, 0, 1, 1.9)),
                     lmerTest.limit = 6480)

emm_part <- summary(emm_fs_OS) |>
  as.data.frame() |>
  transmute(OS, Effect = paste("EMM:", family_size), Estimate = emmean, SE, df, 
            lower.CL, upper.CL, t.ratio = NA_real_, p.value = NA_real_)

contrast_part <- pairs(emm_fs_OS) |>
  summary() |>
  as.data.frame() |>
  transmute(OS,Effect = paste("Contrast:", contrast), Estimate = estimate, SE, df,
            lower.CL = NA_real_, upper.CL = NA_real_, t.ratio, p.value)

emm_contrast_table <- bind_rows(emm_part, contrast_part) |>
  arrange(OS, Effect)|>
  mutate(
    Estimate = round(Estimate, 2),
    SE       = round(SE, 2),
    df       = round(df, 1),
    lower.CL = round(lower.CL, 2),
    upper.CL = round(upper.CL, 2),
    t.ratio  = round(t.ratio, 2),
    p.value  = round(p.value, 3)
  )

as.tibble(emm_contrast_table, digits = 3) |> print(n = 20)
```

#### Plots

```{r echo=FALSE, plots_n250_words_fs, include=FALSE }
library(ggeffects)
library(ggplot2)

# Predicted values across the observed range of OS
# pred <- ggpredict(
#   m_w_N250_fs,
#   terms = c("OS", "family_size")
# )

(pred_FS_OS <- ggemmeans(
  m_w_N250_fs,
  terms = c(
    "OS [all]",
    "family_size"
  )))

(FSxOS_n250 <- ggplot(pred_FS_OS,
       aes(x = x,
           y = predicted,
           color = group,
           fill = group,
           linetype = group)) +
  geom_line(size = 1.2) +
  geom_ribbon(aes(ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              colour = NA,
              linetype = 0) +
  labs(
    x = "Orthographic Sensitivity (OS)",
    y = "Predicted N250 amplitude (µV)",
    title = "Interaction Not Significant",
    color = "Family Size",
    fill = "Family Size",
    linetype = "Family Size"
  ) +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  scale_linetype_manual(values = my_linetypes_1) +
  my_theme +
  my_guides)
```

## N250 WORD DATA: BASE FREQUENCY as Fixed Effect

### Model

```{r anova_n250_words_bf}
contrasts(erp_bf_w$base_frequency) <- c(-0.5, 0.5)


m_w_N250_bf <- lmer(
  value ~ base_frequency * OS + LP +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_bf_w, time_window == "N250"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_w_N250_bf)

# Effect sizes for individual terms
eta_squared(m_w_N250_bf, partial = TRUE)

# Model R²
r2_nakagawa(m_w_N250_bf)
```

#### Means and contrasts

```{r means_n250_words_bf}
as.tibble(emmeans(m_w_N250_bf, ~ base_frequency)) |> print()

emm_bf_OS <- emmeans(m_w_N250_bf,
                      ~ base_frequency | OS,
                      at = list(OS = c(-1.9, -1, 0, 1, 1.9)),
                     lmerTest.limit = 6480)

emm_part <- summary(emm_bf_OS) |>
  as.data.frame() |>
  transmute(OS, Effect = paste("EMM:", base_frequency), Estimate = emmean, SE, df, 
            lower.CL, upper.CL, t.ratio = NA_real_, p.value = NA_real_)

contrast_part <- pairs(emm_bf_OS) |>
  summary() |>
  as.data.frame() |>
  transmute(OS,Effect = paste("Contrast:", contrast), Estimate = estimate, SE, df,
            lower.CL = NA_real_, upper.CL = NA_real_, t.ratio, p.value)

emm_contrast_table <- bind_rows(emm_part, contrast_part) |>
  arrange(OS, Effect)|>
  mutate(
    Estimate = round(Estimate, 2),
    SE       = round(SE, 2),
    df       = round(df, 1),
    lower.CL = round(lower.CL, 2),
    upper.CL = round(upper.CL, 2),
    t.ratio  = round(t.ratio, 2),
    p.value  = round(p.value, 3)
  )

as.tibble(emm_contrast_table, digits = 3) |> print(n = 20)
```
#### Plots

```{r echo=FALSE, plots_n250_words_bf, include=FALSE}
library(ggeffects)
library(ggplot2)

# Predicted values across the observed range of OS
# pred <- ggpredict(
#   m_w_N250_bf,
#   terms = c("OS", "base_frequency")
# )

(pred_BF_OS <- ggemmeans(
  m_w_N250_bf,
  terms = c(
    "OS [all]",
    "base_frequency"
  )))

(BFxOS_n250 <- ggplot(pred_BF_OS,
       aes(x = x,
           y = predicted,
           color = group,
           fill = group,
           linetype = group)) +
  geom_line(size = 1.2) +
  geom_ribbon(aes(ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              colour = NA) +
  labs(
    x = "Orthographic Sensitivity (OS)",
    y = "Predicted N250 amplitude (µV)",
    color = "Base Frequency",
    fill = "Base Frequency",
    linetype = "Base Frequency"
  ) +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  scale_linetype_manual(values = my_linetypes_1) +
  my_theme +
  my_guides)

```


## N250 WORD DATA: Combined Plots

```{r echo=FALSE, fig.height=3, fig.width=5}
row1 <- plot_grid(BFxOS_n250,FSxOS_n250,ncol = 2)

plot_grid(
  ggdraw() + draw_label("N250 Word Data", fontface = "bold"),
  row1,
  ncol = 1,
  rel_heights = c(0.08, 1)
)
```

## N250 WORD DATA: INTERACTION WITH LP (EXPLORATORY ANALYSES)

```{r}
# BINNED BY BASE FREQUENCY
m_w_N250_bf_LP <- lmer(
  value ~ base_frequency * LP + OS +
    (1 | SubjID) + (1 | SubjID:chlabel),
  data = subset(erp_bf_w, time_window == "N400"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_w_N250_bf_LP)
```

```{r}
# BINNED BY FAMILY SIZE

m_w_N250_fs_LP <- lmer(
  value ~ family_size * LP + OS +
    (1 | SubjID) + (1 | SubjID:chlabel),
  data = subset(erp_fs_w, time_window == "N400"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_w_N250_fs_LP)
```


\newpage

# NON-WORD DATA 

```{r}
range(erp_fs_nw$LP)
range(erp_fs_nw$OS)
```

## N250 NONWORD DATA: 

For the NonWord data, BASE FREQUENCY and FAMILY SIZE are both COVARIATES. Because they are correlated only one needs to be included. Family Size is included as covariate, not fixed effect, becauses it explains more variance.

### Model

```{r anova_n250_nonwords_fs}
contrasts(erp_fs_nw$complexity)   <- c(-0.5, 0.5)
contrasts(erp_fs_nw$family_size)  <- c(-0.5, 0.5)

m_nw_N250_fs <- lmer(
  value ~ complexity * OS + complexity * LP + family_size +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_fs_nw, time_window == "N250"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_nw_N250_fs)

# Effect sizes for individual terms
eta_squared(m_nw_N250_fs, partial = TRUE)

# Model R²
r2_nakagawa(m_nw_N250_fs)
```

### Means and Contrasts

```{r means_n250_nonwords_fs}
## complexity
as.tibble(emmeans(m_nw_N250_fs, ~ complexity))

## complexity x LP
emm_fs_LP <- emmeans(m_nw_N250_fs,
                      ~ complexity | LP,
                      at = list(LP = c(-2.5, -1, 0, 1, 3.0)))

emm_part <- summary(emm_fs_LP) |>
  as.data.frame() |>
  transmute(LP, Effect = paste("EMM:", complexity), Estimate = emmean, SE, df, 
            lower.CL, upper.CL, t.ratio = NA_real_, p.value = NA_real_)

contrast_part <- pairs(emm_fs_LP) |>
  summary() |>
  as.data.frame() |>
  transmute(LP, Effect = paste("Contrast:", contrast), Estimate = estimate, SE, df,
            lower.CL = NA_real_, upper.CL = NA_real_, t.ratio, p.value)

emm_contrast_table_fs_LP <- bind_rows(emm_part, contrast_part) |>
  arrange(LP, Effect)|>
  mutate(
    Estimate = round(Estimate, 2),
    SE       = round(SE, 2),
    df       = round(df, 1),
    lower.CL = round(lower.CL, 2),
    upper.CL = round(upper.CL, 2),
    t.ratio  = round(t.ratio, 2),
    p.value  = round(p.value, 3)
  )
# Force RStudio to show more rows inline by using the as.tibble() function
as_tibble(emm_contrast_table_fs_LP) |> print(n = 50)

## complexity x OS
emm_fs_OS <- emmeans(m_nw_N250_fs,
                      ~ complexity | OS,
                      at = list(OS = c(-1.9, -1, 0, 1, 1.9)))

emm_part <- summary(emm_fs_OS) |>
  as.data.frame() |>
  transmute(OS, Effect = paste("EMM:", complexity), Estimate = emmean, SE, df, 
            lower.CL, upper.CL, t.ratio = NA_real_, p.value = NA_real_)

contrast_part <- pairs(emm_fs_OS) |>
  summary() |>
  as.data.frame() |>
  transmute(OS, Effect = paste("Contrast:", contrast), Estimate = estimate, SE, df,
            lower.CL = NA_real_, upper.CL = NA_real_, t.ratio, p.value)

emm_contrast_table_fs_OS <- bind_rows(emm_part, contrast_part) |>
  arrange(OS, Effect)|>       # sorts rows in the combined table, first by column "OS", then by "Effect"
  mutate(
    Estimate = round(Estimate, 2),
    SE       = round(SE, 2),
    df       = round(df, 1),
    lower.CL = round(lower.CL, 2),
    upper.CL = round(upper.CL, 2),
    t.ratio  = round(t.ratio, 2),
    p.value  = round(p.value, 3)
  )
# Force RStudio to show more rows inline by using as.tibble()
as_tibble(emm_contrast_table_fs_OS) |> print(n = 50)
```
### Plots

```{r plots_n250_nonwords_fs, include = FALSE}
# Predicted values across the observed range of OS
# pred <- ggpredict(
#   m_nw_N250_fs,
#   terms = c("OS", "complexity")
# )

(pred_CMP_OS <- ggemmeans(
  m_nw_N250_fs,
  terms = c(
    "OS [all]",
    "complexity"
  )))

(CMP.OS.fs.n250.nw <- ggplot(pred_CMP_OS,
       aes(x = x,
           y = predicted,
           color = group,
           fill = group,
           linetype = group)) +
  geom_line(size = 1.2) +
  geom_ribbon(aes(ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              colour = NA) +
  labs(
    x = "Orthographic Sensitivity (OS)",
    y = "Predicted N250 amplitude (µV)",
    color = "Complexity",
    fill = "Complexity",
    linetype = "Complexity"
  )  +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  scale_linetype_manual(values = my_linetypes_1) +
  my_theme +
  my_guides)

# Predicted values across the observed range of LP
# pred <- ggpredict(
#   m_nw_N250_fs,
#   terms = c("LP", "complexity")
# )

(pred_CMP_LP <- ggemmeans(
  m_nw_N250_fs,
  terms = c(
    "LP [all]",
    "complexity"
  )))

(CMP.LP.fs.n250.nw<- ggplot(pred_CMP_LP,
       aes(x = x,
           y = predicted,
           color = group,
           fill = group,
           linetype = group)) +
  geom_line(size = 1.2) +
  geom_ribbon(aes(ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              colour = NA) +
  labs(
    x = "Language Proficiency (LP)",
    y = "Predicted N250 amplitude (µV)",
    color = "Complexity",
    fill = "Complexity",
    linetype = "Complexity"
  )  +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  scale_linetype_manual(values = my_linetypes_1) +
  my_theme +
  my_guides)
```

## N250 NONWORD DATA: OS and LP Interaction Plots

```{r echo=FALSE, fig.width=5, fig.height=3}
row1 <- plot_grid( CMP.OS.fs.n250.nw, CMP.LP.fs.n250.nw, ncol = 2)

plot_grid(
  ggdraw() + draw_label("N250 NonWord Data", fontface = "bold"),
  row1,
  ncol = 1,
  rel_heights = c(0.08, 1)
)
```

