---
title: "M21_20260502"
author: "Joanna Morris"
date: "`r Sys.Date()`"
output: 
  bookdown::pdf_document2:
    toc: true
    toc_depth: 3
    number_sections: true
header-includes:
  - \setcounter{secnumdepth}{3}
editor_options: 
  chunk_output_type: inline
---

\scriptsize

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE, 
                      error = FALSE,
                      comment = "||",
                      fig.height = 4,
                      fig.width = 7)
options(width = 150)
```

Load libraries

```{r load_libraries, echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(ggeffects)
library(lme4)
library(afex)
library(gridExtra)
library(MuMIn)
library(pbkrtest)
library(effectsize)
library(performance)
library(cowplot)  # for use with `plot_grid(x,x,ncol = x)` function
library(e1071) # for use with `skewness()` function
library(lmerTest)
library(emmeans)
# emm_options(lmer.df = "satterthwaite")
```

Set emmeans options

```{r emmeans_options}
emm_options(
  lmer.df = "kenward-roger",
  pbkrtest.limit = 10000,
  disable.pbkrtest = FALSE
)
```

Set ggplot parameters

```{r ggplot_parameters}
# Color palette
my_palette_1 <- c(
  "#E31A1C",   # red
  "#1F78B4"  # blue
)

my_palette_2 <- c(
  "#0072B2",  # dark blue
  "#E69F00"   # orange/gold
)
my_linetypes_1 <- c("dashed", "solid")

# Theme
my_theme <- theme_classic(base_size = 10) +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal",
    legend.box = "horizontal"
  )

# Common guides
my_guides <- guides(
  colour = guide_legend(nrow = 1),
  fill   = guide_legend(nrow = 1)
)

```

Define 2-way interaction table function

```{r interaction_table_function.2way, echo=FALSE}
compact_emm_table <- function(emm_object,
                              by_var,
                              condition_prefix = NULL,
                              digits_est = 2,
                              digits_df = 1,
                              digits_p = 3) {
  
  by_var_name <- rlang::as_name(rlang::ensym(by_var))
  
  emm_df <- summary(emm_object) |>
    as.data.frame()
  
  contrast_df <- pairs(emm_object) |>
    summary() |>
    as.data.frame()
  
  # Focal factor columns are the EMM columns other than the conditioning variable
  focal_vars <- setdiff(
    names(emm_df),
    c(by_var_name, "emmean", "SE", "df", "lower.CL", "upper.CL")
  )
  
  emm_part <- emm_df |>
    rowwise() |>
    mutate(
      Comparison = paste(c_across(all_of(focal_vars)), collapse = " "),
      Condition = if (is.null(condition_prefix)) {
        as.character(.data[[by_var_name]])
      } else {
        paste(condition_prefix, "=", .data[[by_var_name]])
      }
    ) |>
    ungroup() |>
    transmute(
      Comparison,
      Condition,
      Estimate = emmean,
      SE,
      df,
      lower.CL,
      upper.CL,
      t.ratio = NA_real_,
      p.value = NA_real_
    )
  
  contrast_part <- contrast_df |>
    mutate(
      Comparison = contrast,
      Condition = if (is.null(condition_prefix)) {
        as.character(.data[[by_var_name]])
      } else {
        paste(condition_prefix, "=", .data[[by_var_name]])
      }
    ) |>
    transmute(
      Comparison,
      Condition,
      Estimate = estimate,
      SE,
      df,
      lower.CL = NA_real_,
      upper.CL = NA_real_,
      t.ratio,
      p.value
    )
  
  bind_rows(emm_part, contrast_part) |>
    arrange(Condition, Comparison) |>
    mutate(
      Estimate = round(Estimate, digits_est),
      SE       = round(SE, digits_est),
      df       = round(df, digits_df),
      lower.CL = round(lower.CL, digits_est),
      upper.CL = round(upper.CL, digits_est),
      t.ratio  = round(t.ratio, digits_est),
      p.value  = round(p.value, digits_p)
    )
}
```

```{r interaction_table_function.3way, echo=FALSE}
compact_3way_table <- function(emm_object,
                               by_var,
                               condition_prefix = NULL,
                               factor1,
                               factor2,
                               digits_est = 2,
                               digits_df = 1,
                               digits_p = 3) {
  
  by_var_name <- rlang::as_name(rlang::ensym(by_var))
  factor1_name <- rlang::as_name(rlang::ensym(factor1))
  factor2_name <- rlang::as_name(rlang::ensym(factor2))
  
  emm_df <- summary(emm_object) |>
    as.data.frame()
  
  make_condition <- function(x) {
    if (is.null(condition_prefix)) {
      as.character(x[[by_var_name]])
    } else {
      paste(condition_prefix, "=", x[[by_var_name]])
    }
  }
  
  emm_part <- emm_df |>
    mutate(
      Comparison = paste(.data[[factor1_name]], .data[[factor2_name]]),
      Condition = make_condition(cur_data())
    ) |>
    transmute(
      Comparison,
      Condition,
      Estimate = emmean,
      SE,
      df,
      lower.CL,
      upper.CL,
      t.ratio = NA_real_,
      p.value = NA_real_
    )
  
  factor1_part <- pairs(emm_object, simple = factor1_name) |>
    summary() |>
    as.data.frame() |>
    mutate(
      Comparison = contrast,
      Condition = paste(
        if (is.null(condition_prefix)) .data[[by_var_name]] else paste(condition_prefix, "=", .data[[by_var_name]]),
        "|",
        factor2_name, "=",
        .data[[factor2_name]]
      )
    ) |>
    transmute(
      Comparison,
      Condition,
      Estimate = estimate,
      SE,
      df,
      lower.CL = NA_real_,
      upper.CL = NA_real_,
      t.ratio,
      p.value
    )
  
  factor2_part <- pairs(emm_object, simple = factor2_name) |>
    summary() |>
    as.data.frame() |>
    mutate(
      Comparison = contrast,
      Condition = paste(
        if (is.null(condition_prefix)) .data[[by_var_name]] else paste(condition_prefix, "=", .data[[by_var_name]]),
        "|",
        factor1_name, "=",
        .data[[factor1_name]]
      )
    ) |>
    transmute(
      Comparison,
      Condition,
      Estimate = estimate,
      SE,
      df,
      lower.CL = NA_real_,
      upper.CL = NA_real_,
      t.ratio,
      p.value
    )
  
  interaction_part <- contrast(
  emm_object,
  interaction = c("pairwise", "pairwise")
) |>
  summary() |>
  as.data.frame() |>
  mutate(
    Comparison = paste0(
      "Int: ",
      .data[[paste0(factor1_name, "_pairwise")]],
      " across ",
      .data[[paste0(factor2_name, "_pairwise")]]
    ),
    Condition = make_condition(cur_data())
  ) |>
  transmute(
    Comparison,
    Condition,
    Estimate = estimate,
    SE,
    df,
    lower.CL = NA_real_,
    upper.CL = NA_real_,
    t.ratio,
    p.value
  )
  
  bind_rows(
    emm_part         |> mutate(RowType = 1),
    factor1_part     |> mutate(RowType = 2),
    factor2_part     |> mutate(RowType = 2),
    interaction_part |> mutate(RowType = 3)
  ) |>
    arrange(Condition, RowType, Comparison) |>
    mutate(
      Estimate = round(Estimate, digits_est),
      SE       = round(SE, digits_est),
      df       = round(df, digits_df),
      lower.CL = round(lower.CL, digits_est),
      upper.CL = round(upper.CL, digits_est),
      t.ratio  = round(t.ratio, digits_est),
      p.value  = round(p.value, digits_p)
    ) |>
    select(-RowType)
}
```


# Load Files

```{r load_files, message=FALSE, warning=FALSE}

# Load data: rt words

rt_w <- read_csv("rt_words_frq.csv") |>
  filter(correct == 1) |>
  mutate(
    SubjID = factor(SubjID),
    Item   = factor(target),
    logRT  = log(response_time),
    OS     = as.numeric(Dim.2),
    LP     = as.numeric(Dim.1),
    zLogBF = as.numeric(scale(LogBF)),
    zLogFS = as.numeric(scale(LogFS))
  )

# Load data: rt nonwords
rt_nw <- read_csv("rt_nwords_frq.csv") |>
  filter(correct == 1) |>
  mutate(
    SubjID = factor(SubjID),
    ItemID = factor(ItemID),
    complexity = factor(complexity,
                    levels = c("SIMP", "COMP"),
                    labels = c("Simple", "Complex")),
    logRT  = log(response_time),
    OS     = as.numeric(Dim.2),
    LP     = as.numeric(Dim.1),
    zLogBF = as.numeric(scale(LogBF)),
    zLogFS = as.numeric(scale(LogFS))
  )

# Load data: erp_fs words
erp_fs_w <- read_csv("erp_fs_dmg_words.csv") |>
  mutate(
    SubjID = factor(SubjID),
    chlabel = factor(chlabel),
    family_size = factor(family_size, 
                         levels = c("Small", "Large")),
    time_window = factor(time_window),
    OS = as.numeric(Dim.2),
    LP = as.numeric(Dim.1)
  )

# Load data: erp_fs nonwords
erp_fs_nw <- read_csv("erp_fs_dmg_nonwords.csv") |>
  mutate(
    SubjID = factor(SubjID),
    chlabel = factor(chlabel),
    family_size = factor(family_size, 
                         levels = c("Small", "Large")),
    complexity = factor(complexity,
                    labels = c("Simple", "Complex")),
    time_window = factor(time_window),
    OS = as.numeric(Dim.2),
    LP = as.numeric(Dim.1)
  )

# Load data: erp_bf words
erp_bf_w <- read_csv("erp_bf_dmg_words.csv") |>
  mutate(
    SubjID = factor(SubjID),
    chlabel = factor(chlabel),
    base_frequency = factor(base_frequency, 
                            levels = c("Low", "High")),
    time_window = factor(time_window),
    OS = as.numeric(Dim.2),
    LP = as.numeric(Dim.1)
  )

# Load data: erp_bf nonwords
erp_bf_nw <- read_csv("erp_bf_dmg_nonwords.csv") |>
  mutate(
    SubjID = factor(SubjID),
    chlabel = factor(chlabel),
    base_frequency = factor(base_frequency, 
                            levels = c("Low", "High")),
    complexity = factor(complexity,
                    labels = c("Simple", "Complex")),
    time_window = factor(time_window),
    OS = as.numeric(Dim.2),
    LP = as.numeric(Dim.1)
  )
```



```{r}
range(erp_fs_nw$LP)
range(erp_fs_nw$OS)
```
# RESPONSE TIME
## RESPONSE TIME WORD DATA
### Model

```{r anova_rt_words}

library(lmerTest)

m_rt_words <-lmer(
  logRT ~ zLogBF + zLogFS + OS + LP +
    (1 | SubjID) +
    (1 | Item),
  data = rt_w,
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_rt_words)

# Effect sizes for individual terms
eta_squared(m_rt_words, partial = TRUE)

# Model R²
r2_nakagawa(m_rt_words)
```

## RESPONSE TIME NONWORD DATA
### Model
```{r anova_rt_nonwords}
contrasts(rt_nw$complexity) <- c(-0.5, 0.5)

m_rt_nw <- lmer(
  logRT ~ complexity + zLogBF + zLogFS + OS + LP +
    (1 + complexity | SubjID) +
    (1 | ItemID),
  data = rt_nw,
  control = lmerControl(optimizer = "bobyqa")
)
m_rt_nw
summary(m_rt_nw)

# Effect sizes for individual terms
eta_squared(m_rt_nw, partial = TRUE)

# Model R²
r2_nakagawa(m_rt_nw)

# Means
# get means on log scale
emm_logrt <- emmeans(m_rt_nw, ~ complexity)
emm_summary <- summary(emm_logrt)

# back transform manually
emm_summary$mean_ms <- exp(emm_summary$emmean)
emm_summary$lower_ms <- exp(emm_summary$lower.CL)
emm_summary$upper_ms <- exp(emm_summary$upper.CL)
emm_summary

diff_ms <- exp(emm_summary$emmean[emm_summary$complexity == "Complex"]) -
            exp(emm_summary$emmean[emm_summary$complexity == "Simple"])
diff_ms
```

# N250
## N250 WORD DATA: Base Frequency

### Model

```{r anova_n250_words_bf}
contrasts(erp_bf_w$base_frequency) <- c(-0.5, 0.5)


m_w_N250_bf <- lmer(
  value ~ base_frequency * OS + LP +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_bf_w, time_window == "N250"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_w_N250_bf)

# Effect sizes for individual terms
eta_squared(m_w_N250_bf, partial = TRUE)

# Model R²
r2_nakagawa(m_w_N250_bf)
```

### Means and contrasts

```{r means_n250_words_bf}
emmeans(m_w_N250_bf, ~ base_frequency)

emm_bf_OS <- emmeans(m_w_N250_bf,
                      ~ base_frequency | OS,
                      at = list(OS = c(-1, 0, 1)))

emm_part <- summary(emm_bf_OS) |>
  as.data.frame() |>
  transmute(OS, Effect = paste("EMM:", base_frequency), Estimate = emmean, SE, df, 
            lower.CL, upper.CL, t.ratio = NA_real_, p.value = NA_real_)

contrast_part <- pairs(emm_bf_OS) |>
  summary() |>
  as.data.frame() |>
  transmute(OS,Effect = paste("Contrast:", contrast), Estimate = estimate, SE, df,
            lower.CL = NA_real_, upper.CL = NA_real_, t.ratio, p.value)

(emm_contrast_table <- bind_rows(emm_part, contrast_part) |>
  arrange(OS, Effect)|>
  mutate(
    Estimate = round(Estimate, 2),
    SE       = round(SE, 2),
    df       = round(df, 1),
    lower.CL = round(lower.CL, 2),
    upper.CL = round(upper.CL, 2),
    t.ratio  = round(t.ratio, 2),
    p.value  = round(p.value, 3)
  ))

#  kable(emm_contrast_table, digits = 3)


```
### Plots

```{r plots_n250_words_bf, include=FALSE}
library(ggeffects)
library(ggplot2)

# Predicted values across the observed range of OS
pred <- ggpredict(
  m_w_N250_bf,
  terms = c("OS", "base_frequency")
)

(BFxOS_n250 <- ggplot(pred,
       aes(x = x,
           y = predicted,
           color = group,
           fill = group,
           linetype = group)) +
  geom_line(size = 1.2) +
  geom_ribbon(aes(ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              colour = NA) +
  labs(
    x = "Orthographic Sensitivity (OS)",
    y = "Predicted N250 amplitude (µV)",
    color = "Base Frequency",
    fill = "Base Frequency",
    linetype = "Base Frequency"
  ) +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  scale_linetype_manual(values = my_linetypes_1) +
  my_theme +
  my_guides)

```



## N250 WORD DATA: Family Size

### Model

```{r anova_n250_words_fs}
contrasts(erp_fs_w$family_size) <- c(-0.5, 0.5)


m_w_N250_fs <- lmer(
  value ~ family_size * OS + LP +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_fs_w, time_window == "N250"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_w_N250_fs)

# Effect sizes for individual terms
eta_squared(m_w_N250_fs, partial = TRUE)

# Model R²
r2_nakagawa(m_w_N250_fs)
```

### Means and Contrasts

```{r means_n250_words_fs}
# family size
emmeans(m_w_N250_fs, ~ family_size)
```

### Plots

```{r plots_n250_words_fs, include=FALSE }
library(ggeffects)
library(ggplot2)

# Predicted values across the observed range of OS
pred <- ggpredict(
  m_w_N250_fs,
  terms = c("OS", "family_size")
)

(FSxOS_n250 <- ggplot(pred,
       aes(x = x,
           y = predicted,
           color = group,
           fill = group,
           linetype = group)) +
  geom_line(size = 1.2) +
  geom_ribbon(aes(ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              colour = NA,
              linetype = 0) +
  labs(
    x = "Orthographic Sensitivity (OS)",
    y = "Predicted N250 amplitude (µV)",
    title = "Interaction Not Significant",
    color = "Family Size",
    fill = "Family Size",
    linetype = "Family Size"
  ) +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  scale_linetype_manual(values = my_linetypes_1) +
  my_theme +
  my_guides)
```
## N250 WORD DATA: Combined Plots

```{r fig.height=4, fig.width=6}
row1 <- plot_grid(BFxOS_n250,FSxOS_n250,ncol = 2)

plot_grid(
  ggdraw() + draw_label("N250 Word Data", fontface = "bold"),
  row1,
  ncol = 1,
  rel_heights = c(0.08, 1)
)
```

## N250 NONWORD DATA: Base Frequency as covariate (NOT USED IN WRITE-UP)

### Model

```{r anova_n250_nonwords_bf}
contrasts(erp_bf_nw$complexity)   <- c(-0.5, 0.5)
contrasts(erp_bf_nw$base_frequency)  <- c(-0.5, 0.5)

m_nw_N250_bf <- lmer(
  value ~ complexity * OS + complexity * LP + base_frequency +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_bf_nw, time_window == "N250"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_nw_N250_bf)


# Effect sizes for individual terms
eta_squared(m_nw_N250_bf, partial = TRUE)

# Model R²
r2_nakagawa(m_nw_N250_bf)

```

### Means and Contrasts
```{r means_n250_nonwords_bf}
## complexity
emmeans(m_nw_N250_bf, ~ complexity, )

## complexity x LP
emm_bf_LP <- emmeans(m_nw_N250_bf,
                      ~ complexity | LP,
                      at = list(LP = c(-2, -1, 0, 1, 2)))

emm_part <- summary(emm_bf_LP) |>
  as.data.frame() |>
  transmute(LP, Effect = paste("EMM:", complexity), Estimate = emmean, SE, df, 
            lower.CL, upper.CL, t.ratio = NA_real_, p.value = NA_real_)

contrast_part <- pairs(emm_bf_LP) |>
  summary() |>
  as.data.frame() |>
  transmute(LP, Effect = paste("Contrast:", contrast), Estimate = estimate, SE, df,
            lower.CL = NA_real_, upper.CL = NA_real_, t.ratio, p.value)

(emm_contrast_table_bf_LP_n250 <- bind_rows(emm_part, contrast_part) |>
  arrange(LP, Effect)|>
  mutate(
    Estimate = round(Estimate, 2),
    SE       = round(SE, 2),
    df       = round(df, 1),
    lower.CL = round(lower.CL, 2),
    upper.CL = round(upper.CL, 2),
    t.ratio  = round(t.ratio, 2),
    p.value  = round(p.value, 3)
  ))

## complexity x OS
emm_bf_OS <- emmeans(m_nw_N250_bf,
                      ~ complexity | OS,
                      at = list(OS = c(-1, 0, 1)))

emm_part <- summary(emm_bf_OS) |>
  as.data.frame() |>
  transmute(OS, Effect = paste("EMM:", complexity), Estimate = emmean, SE, df, 
            lower.CL, upper.CL, t.ratio = NA_real_, p.value = NA_real_)

contrast_part <- pairs(emm_bf_OS) |>
  summary() |>
  as.data.frame() |>
  transmute(OS, Effect = paste("Contrast:", contrast), Estimate = estimate, SE, df,
            lower.CL = NA_real_, upper.CL = NA_real_, t.ratio, p.value)

(emm_contrast_table <- bind_rows(emm_part, contrast_part) |>
  arrange(OS, Effect)|>
  mutate(
    Estimate = round(Estimate, 2),
    SE       = round(SE, 2),
    df       = round(df, 1),
    lower.CL = round(lower.CL, 2),
    upper.CL = round(upper.CL, 2),
    t.ratio  = round(t.ratio, 2),
    p.value  = round(p.value, 3)
  ))
```
### Plots

```{r plots_n250_nonwords_bf, include = FALSE}
# Predicted values across the observed range of OS
pred <- ggpredict(
  m_nw_N250_bf,
  terms = c("OS", "complexity")
)

(CMP.OS.bf.n250.nw <- ggplot(pred,
       aes(x = x,
           y = predicted,
           color = group,
           fill = group,
           linetype = group)) +
  geom_line(size = 1.2) +
  geom_ribbon(aes(ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              colour = NA) +
  labs(
    x = "Orthographic Sensitivity (OS)",
    y = "Predicted N250 amplitude (µV)",
    color = "Complexity",
    fill = "Complexity",
    linetype = "Complexity"
  )  +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  scale_linetype_manual(values = my_linetypes_1) +
  my_theme +
  my_guides)

# Predicted values across the observed range of LP
pred <- ggpredict(
  m_nw_N250_bf,
  terms = c("LP", "complexity")
)

(CMP.LP.bf.n250.nw <- ggplot(pred,
       aes(x = x,
           y = predicted,
           color = group,
           fill = group,
           linetype = group)) +
  geom_line(size = 1.2) +
  geom_ribbon(aes(ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              colour = NA) +
  labs(
    x = "Language Proficiency (LP)",
    y = "Predicted N250 amplitude (µV)",
    color = "Complexity",
    fill = "Complexity",
    linetype = "Complexity"
  )  +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  scale_linetype_manual(values = my_linetypes_1) +
  my_theme +
  my_guides)
```



## N250 NONWORD DATA: Family Size as covariate

### Model

```{r anova_n250_nonwords_fs}
contrasts(erp_fs_nw$complexity)   <- c(-0.5, 0.5)
contrasts(erp_fs_nw$family_size)  <- c(-0.5, 0.5)

m_nw_N250_fs <- lmer(
  value ~ complexity * OS + complexity * LP + family_size +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_fs_nw, time_window == "N250"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_nw_N250_fs)

# Effect sizes for individual terms
eta_squared(m_nw_N250_fs, partial = TRUE)

# Model R²
r2_nakagawa(m_nw_N250_fs)
```

### Means and Contrasts

```{r means_n250_nonwords_fs}
## complexity
emmeans(m_nw_N250_fs, ~ complexity)

## complexity x LP
emm_fs_LP <- emmeans(m_nw_N250_fs,
                      ~ complexity | LP,
                      at = list(LP = c(-2, -1, 0, 1, 2)))

emm_part <- summary(emm_fs_LP) |>
  as.data.frame() |>
  transmute(LP, Effect = paste("EMM:", complexity), Estimate = emmean, SE, df, 
            lower.CL, upper.CL, t.ratio = NA_real_, p.value = NA_real_)

contrast_part <- pairs(emm_fs_LP) |>
  summary() |>
  as.data.frame() |>
  transmute(LP, Effect = paste("Contrast:", contrast), Estimate = estimate, SE, df,
            lower.CL = NA_real_, upper.CL = NA_real_, t.ratio, p.value)

(emm_contrast_table_fs_LP <- bind_rows(emm_part, contrast_part) |>
  arrange(LP, Effect)|>
  mutate(
    Estimate = round(Estimate, 2),
    SE       = round(SE, 2),
    df       = round(df, 1),
    lower.CL = round(lower.CL, 2),
    upper.CL = round(upper.CL, 2),
    t.ratio  = round(t.ratio, 2),
    p.value  = round(p.value, 3)
  ))

## complexity x OS
emm_fs_OS <- emmeans(m_nw_N250_fs,
                      ~ complexity | OS,
                      at = list(OS = c(-1.9, -1, 0, 1, 1.9)))

emm_part <- summary(emm_fs_OS) |>
  as.data.frame() |>
  transmute(OS, Effect = paste("EMM:", complexity), Estimate = emmean, SE, df, 
            lower.CL, upper.CL, t.ratio = NA_real_, p.value = NA_real_)

contrast_part <- pairs(emm_fs_OS) |>
  summary() |>
  as.data.frame() |>
  transmute(OS, Effect = paste("Contrast:", contrast), Estimate = estimate, SE, df,
            lower.CL = NA_real_, upper.CL = NA_real_, t.ratio, p.value)

(emm_contrast_table_fs_OS <- bind_rows(emm_part, contrast_part) |>
  arrange(OS, Effect)|>       # sorts rows in the combined table, first by column "OS", then by "Effect"
  mutate(
    Estimate = round(Estimate, 2),
    SE       = round(SE, 2),
    df       = round(df, 1),
    lower.CL = round(lower.CL, 2),
    upper.CL = round(upper.CL, 2),
    t.ratio  = round(t.ratio, 2),
    p.value  = round(p.value, 3)
  ))
```
### Plots

```{r plots_n250_nonwords_fs, include = FALSE}
# Predicted values across the observed range of OS
pred <- ggpredict(
  m_nw_N250_fs,
  terms = c("OS", "complexity")
)

(CMP.OS.fs.n250.nw <- ggplot(pred,
       aes(x = x,
           y = predicted,
           color = group,
           fill = group,
           linetype = group)) +
  geom_line(size = 1.2) +
  geom_ribbon(aes(ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              colour = NA) +
  labs(
    x = "Orthographic Sensitivity (OS)",
    y = "Predicted N250 amplitude (µV)",
    color = "Complexity",
    fill = "Complexity",
    linetype = "Complexity"
  )  +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  scale_linetype_manual(values = my_linetypes_1) +
  my_theme +
  my_guides)

# Predicted values across the observed range of LP
pred <- ggpredict(
  m_nw_N250_fs,
  terms = c("LP", "complexity")
)

(CMP.LP.fs.n250.nw<- ggplot(pred,
       aes(x = x,
           y = predicted,
           color = group,
           fill = group,
           linetype = group)) +
  geom_line(size = 1.2) +
  geom_ribbon(aes(ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              colour = NA) +
  labs(
    x = "Language Proficiency (LP)",
    y = "Predicted N250 amplitude (µV)",
    color = "Complexity",
    fill = "Complexity",
    linetype = "Complexity"
  )  +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  scale_linetype_manual(values = my_linetypes_1) +
  my_theme +
  my_guides)
```
## N250 NONWORD DATA: Combined Interaction Plots

```{r  fig.width=6, fig.height=4}
row1 <- plot_grid( CMP.OS.fs.n250.nw,CMP.LP.fs.n250.nw,ncol = 2)

plot_grid(
  ggdraw() + draw_label("N250 NonWord Data", fontface = "bold"),
  row1,
  ncol = 1,
  rel_heights = c(0.08, 1)
)
```

# N400

## N400 WORD DATA: Base Frequency

### Model

```{r anova_N400_words_bf}
contrasts(erp_bf_w$base_frequency) <- c(-0.5, 0.5)

m_w_N400_bf <- lmer(
  value ~ base_frequency * LP + OS +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_bf_w, time_window == "N400"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_w_N400_bf)

# Effect sizes for individual terms
eta_squared(m_w_N400_bf, partial = TRUE)

# Model R²
r2_nakagawa(m_w_N400_bf)
```

### Means and Contrasts

```{r means_N400_words_bf}
emmeans(m_w_N400_bf, ~ base_frequency)

emm_bf_LP <- emmeans(m_w_N400_bf,
                      ~ base_frequency | LP,
                      at = list(LP = c(-2, -1, 0, 1, 2)))

emm_part <- summary(emm_bf_LP) |>
  as.data.frame() |>
  transmute(LP, Effect = paste("EMM:", base_frequency), Estimate = emmean, SE, df, 
            lower.CL, upper.CL, t.ratio = NA_real_, p.value = NA_real_)

contrast_part <- pairs(emm_bf_LP) |>
  summary() |>
  as.data.frame() |>
  transmute(LP, Effect = paste("Contrast:", contrast), Estimate = estimate, SE, df,
            lower.CL = NA_real_, upper.CL = NA_real_, t.ratio, p.value)

(emm_contrast_table_LP_N400_words <- bind_rows(emm_part, contrast_part) |>
  arrange(LP, Effect)|>
  mutate(
    Estimate = round(Estimate, 2),
    SE       = round(SE, 2),
    df       = round(df, 1),
    lower.CL = round(lower.CL, 2),
    upper.CL = round(upper.CL, 2),
    t.ratio  = round(t.ratio, 2),
    p.value  = round(p.value, 3)
  ))

#  kable(emm_contrast_table, digits = 3)
```
### Plots

```{r plot_N400_words_bf, include=FALSE}
library(ggeffects)
library(ggplot2)

# Predicted values across the observed range of LP
pred <- ggpredict(
  m_w_N400_bf,
  terms = c("LP", "base_frequency")
)

(BFxLP_n400 <- ggplot(pred,
       aes(x = x,
           y = predicted,
           color = group,
           fill = group,
           linetype = group)) +
  geom_line(size = 1.2) +
  geom_ribbon(aes(ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              colour = NA) +
  labs(
    x = "Language Proficiency (LP)",
    y = "Predicted N400 amplitude (µV)",
    color = "Base Frequency",
    fill = "Base Frequency",
    linetype = "Base Frequency"
  )  +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  scale_linetype_manual(values = my_linetypes_1) +
  my_theme +
  my_guides)
```

## N400 WORD DATA: Family Size
### Model
```{r anova_N400_words_fs}
contrasts(erp_fs_w$family_size) <- c(-0.5, 0.5)

m_w_N400_fs <- lmer(
  value ~ family_size * LP + OS +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_fs_w, time_window == "N400"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_w_N400_fs)

# Effect sizes for individual terms
eta_squared(m_w_N400_fs, partial = TRUE)

# Model R²
r2_nakagawa(m_w_N400_fs)
```

### Means

```{r means_N400_words_fs}
emmeans(m_w_N400_fs, ~ family_size)
```

### Plots (Interaction Not significant)

```{r plots_N400_words_fs, include=FALSE}
library(ggeffects)
library(ggplot2)

# Predicted values across the observed range of LP
pred <- ggpredict(
  m_w_N400_fs,
  terms = c("LP", "family_size")
)

(FSxLP_n400 <- ggplot(pred,
       aes(x = x,
           y = predicted,
           color = group,
           fill = group,
           linetype = group)) +
  geom_line(size = 1.2) +
  geom_ribbon(aes(ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              colour = NA) +
  labs(
    x = "Language Proficiency (LP)",
    y = "Predicted N400 amplitude (µV)",
    title = "Interaction Not Significant",
    color = "Family Size",
    fill = "Family Size",
    linetype = "Family Size"
  )  +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  scale_linetype_manual(values = my_linetypes_1) +
  my_theme +
  my_guides)
```

## N400 WORD DATA: Combined Interaction Plots

```{r  fig.width=6, fig.height=4}
row1 <- plot_grid(BFxLP_n400,FSxLP_n400,ncol = 2)

plot_grid(
  ggdraw() + draw_label("N400 Word Data", fontface = "bold"),
  row1,
  ncol = 1,
  rel_heights = c(0.08, 1)
)
```

Does the slopes of the lines in the significant interactions, significantly differ from zero?

```{r}
test(emtrends(m_w_N250_bf, ~ base_frequency, var = "OS"))
test(emtrends(m_w_N400_bf, ~ base_frequency, var = "LP"))
```


### N400 NONWORD DATA:  Base Frequency (NOT USED IN WRITE-UP)

### Model

```{r anova_n400_nonwords_bf}

contrasts(erp_bf_nw$complexity)  <- c(-0.5, 0.5)
contrasts(erp_bf_nw$base_frequency) <- c(-0.5, 0.5)

m_nw_N400_bf <- lmer(
  value ~ complexity * base_frequency * LP + OS +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_bf_nw, time_window == "N400"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_nw_N400_bf)


# Effect sizes for individual terms
eta_squared(m_nw_N400_bf, partial = TRUE)

# Model R²
r2_nakagawa(m_nw_N400_bf)
```

### N400 NONWORD DATA: Family Size

##### Model

```{r anova_n400_nonwords_fs}
contrasts(erp_fs_nw$complexity)  <- c(-0.5, 0.5)
contrasts(erp_fs_nw$family_size) <- c(-0.5, 0.5)

m_nw_N400_fs <- lmer(
  value ~ complexity * family_size * LP + OS +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_fs_nw, time_window == "N400"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_nw_N400_fs)

# Effect sizes for individual terms
eta_squared(m_nw_N400_fs, partial = TRUE)

# Model R²
r2_nakagawa(m_nw_N400_fs)
```


##### Means and Contrasts: Complexity × Family Size × LP interaction

```{r means_n400_nonwords_fs.3way}
# emm_3way <- emmeans(
#   m_nw_N400_fs,
#   ~ complexity * family_size | LP,
#   at = list(LP = c(-1, 0, 1))
# )

emm_3way <- emmeans(
  m_nw_N400_fs,
  ~ complexity * family_size | LP,
  at = list(LP = c(-2,-1, 0, 1, 2))
)

compact_3way_table(
  emm_3way,
  by_var = LP,
  condition_prefix = "LP",
  factor1 = complexity,
  factor2 = family_size
)
```


##### Complexity × Family Size interaction averaged across LP

```{r means_n400_nonwords_fs.2way.A}
emm_complexity_FS_N400 <- emmeans(
  m_nw_N400_fs,
  ~ complexity | family_size)

compact_emm_table(
  emm_complexity_FS_N400,
  by_var = family_size
)

emm_complexity_CMP_N400 <- emmeans(
  m_nw_N400_fs,
  ~ family_size | complexity)

compact_emm_table(
  emm_complexity_CMP_N400,
  by_var = complexity
)
```

##### Complexity × LP interaction averaged over Family Size:

```{r means_n400_nonwords_fs.2way.B}
emm_complexity_LP_N400 <- emmeans(
  m_nw_N400_fs,
  ~ complexity | LP,
  at = list(LP = c(-2, -1, 0, 1, 2))
)

compact_emm_table(
  emm_complexity_LP_N400,
  by_var = LP,
  condition_prefix = "LP"
)
```


##### FS × LP interaction averaged over Complexity:

```{r means_n400_nonwords_fs.2way.C}
emm_FS_LP_N400 <- emmeans(
  m_nw_N400_fs,
  ~ family_size | LP,
  at = list(LP = c(-2, -1, 0, 1, 2))
)

compact_emm_table(
  emm_FS_LP_N400,
  by_var = LP,
  condition_prefix = "LP"
)
```

##### complexity effects at each family size level averaged over LP
```{r}
emm_options(lmer.df = "satterthwaite")
emmeans(m_nw_N400_fs, pairwise ~ complexity | family_size)
```

#### Plots

```{r plots_n400_nonwords_fs.3way, include=FALSE}
library(ggeffects)
library(ggplot2)

# Facet by Family Size
pred <- ggpredict(
  m_nw_N400_fs,
  terms = c("LP", "complexity", "family_size")
)

nw.n400.3way.A <- ggplot(pred,
       aes(x = x,
           y = predicted,
           colour = group,
           fill = group,
           linetype = group)) +
  geom_line(linewidth = 1.2) +
  geom_ribbon(aes(ymin = conf.low,
                  ymax = conf.high),
              alpha = .20,
              colour = NA) +
  facet_wrap(~facet) +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  scale_linetype_manual(values = my_linetypes_1) +
  labs(
    x = "Lexical Proficiency (LP)",
    y = "Predicted N400 amplitude (µV)",
    colour = "Complexity",
    fill = "Complexity",
    linetype = "Complexity"
  ) +
  my_theme +
  my_guides

# Facet by Complexity
pred <- ggpredict(
  m_nw_N400_fs,
  terms = c("LP", "family_size", "complexity")
)

nw.n400.3way.B <- ggplot(pred,
       aes(x = x,
           y = predicted,
           colour = group,
           fill = group,
           linetype = group)) +
  geom_line(linewidth = 1.2) +
  geom_ribbon(aes(ymin = conf.low,
                  ymax = conf.high),
              alpha = .20,
              colour = NA,
              linetype = 0) +
  facet_wrap(~facet) +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  scale_linetype_manual(values = my_linetypes_1) +
  labs(
    x = "Lexical Proficiency (LP)",
    y = "Predicted N400 amplitude (µV)",
    colour = "Family Size",
    fill = "Family Size",
    linetype = "Family Size"
  ) +
  my_theme +
  my_guides

```

```{r fig.height= 8}
plot_grid(nw.n400.3way.A, nw.n400.3way.B, ncol = 1)
```

```{r}
library(emmeans)
library(dplyr)
library(ggplot2)

# Create a sequence of LP values across the observed range
LP_seq <- with(
  subset(erp_bf_nw, time_window == "N400"),
  seq(min(LP, na.rm = TRUE),
      max(LP, na.rm = TRUE),
      length.out = 100)
)

# Estimate complexity means at each LP value, separately by family_size
emm_complexity_by_LP_FS <- emmeans(
  m_nw_N400_fs,
  ~ complexity | family_size * LP,
  at = list(LP = LP_seq)
)

# Compute Simple - Complex at each LP value and family_size level
complexity_diff_by_LP_FS <- pairs(emm_complexity_by_LP_FS) |>
  summary(infer = TRUE) |>
  as.data.frame()
```

```{r}
head(complexity_diff_by_LP_FS)
```

```{r fig.height=5 , fig.width=5}
ggplot(
  complexity_diff_by_LP_FS,
  aes(x = LP,
      y = estimate,
      colour = family_size,
      fill = family_size)
) +
  geom_hline(yintercept = 0,
             linetype = "dashed",
             linewidth = 0.5) +
  geom_line(linewidth = 1.2) +
  geom_ribbon(aes(ymin = lower.CL,
                  ymax = upper.CL),
              alpha = 0.20,
              colour = NA) +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  labs(
    x = "Lexical Proficiency (LP)",
    y = "Simple - Complex difference in predicted N400 amplitude (µV)",
    colour = "Family Size",
    fill = "Family Size"
  ) +
  my_theme +
  my_guides
```




---

# EXPLORATORY ANALYSES

## NONWORD DATA: RT interactions of LP and OS with complexity

```{r}
m_rt_nw_os <- lmer(
  logRT ~ complexity * OS + complexity * LP + zLogBF + zLogFS +
    (1 + complexity | SubjID) + (1 | ItemID),
  data = rt_nw,
  control = lmerControl(optimizer = "bobyqa")
)

emm_options(lmer.df = "satterthwaite")
emmeans(m_rt_nw_os, pairwise ~ complexity | OS,
        at = list(OS = c(-1.9, -1, 0, 1, 1.9)))

emmeans(m_rt_nw_os, pairwise ~ complexity | LP,
        at = list(LP = c(-2, -1, 0, 1, 2)),
        tran = "log")
```

## N400 WORD DATA: INTERACTION WITH OS
```{r}
# BINNED BY BASE FREQUENCY
m_w_N400_bf_OS <- lmer(
  value ~ base_frequency * OS + LP +
    (1 | SubjID) + (1 | SubjID:chlabel),
  data = subset(erp_bf_w, time_window == "N400"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_w_N400_bf_OS)
# BINNED BY FAMILY SIZE

m_w_N400_fs_OS <- lmer(
  value ~ family_size * OS + LP +
    (1 | SubjID) + (1 | SubjID:chlabel),
  data = subset(erp_fs_w, time_window == "N400"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_w_N400_fs_OS)
```

## N400 NON-WORD DATA: INTERACTION WITH OS

```{r}
# BINNED BY BASE FREQUENCY
m_nw_N400_bf_OS <- lmer(
  value ~ complexity * base_frequency * OS + LP +
    (1 | SubjID) + (1 | SubjID:chlabel),
  data = subset(erp_bf_nw, time_window == "N400"),
  control = lmerControl(optimizer = "bobyqa")
)

summary(m_nw_N400_bf_OS)

m_nw_N400_fs_OS <- lmer(
  value ~ complexity * family_size * OS + LP +
    (1 | SubjID) + (1 | SubjID:chlabel),
  data = subset(erp_fs_nw, time_window == "N400"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_nw_N400_fs_OS)
```
# GRAPH OF INTERACTIONS

```{r}
emmeans(m_nw_N400_fs_OS, ~ complexity | OS,
        at = list(OS = c(-1.9, -1, 0, 1, 1.9))) %>%
  as.data.frame() %>%
  ggplot(aes(x = OS, y = emmean, colour = complexity)) +
  geom_line() +
  geom_ribbon(aes(ymin = lower.CL, ymax = upper.CL, fill = complexity), 
              alpha = 0.2, colour = NA) +
  labs(y = "N400 amplitude (µV)", x = "Orthographic Sensitivity") +
  theme_minimal()


```

```{r}
emmeans(m_nw_N400_bf_OS, ~ complexity * base_frequency | OS,
        at = list(OS = c(-1.9, -1, 0, 1, 1.9))) %>%
  as.data.frame() %>%
  ggplot(aes(x = OS, y = emmean, colour = complexity, linetype = base_frequency)) +
  geom_line() +
  geom_ribbon(aes(ymin = lower.CL, ymax = upper.CL, fill = complexity), 
              alpha = 0.2, colour = NA) +
  labs(y = "N400 amplitude (µV)", x = "Orthographic Sensitivity") +
  theme_minimal()
```

