---
title: "M21 2026 July 2026 Response Time"
author: "Joanna Morris"
date: "`r Sys.Date()`"
output: 
  bookdown::pdf_document2:
    toc: true
    toc_depth: 3
    number_sections: true
header-includes:
  - \setcounter{secnumdepth}{3}
editor_options: 
  chunk_output_type: console
---

\scriptsize

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE, 
                      error = FALSE,
                      comment = "||",
                      fig.height = 4,
                      fig.width = 7)
options(width = 150)
```

Load libraries

```{r load_libraries, echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(ggeffects)
library(lme4)
library(afex)
library(gridExtra)
library(MuMIn)
library(pbkrtest)
library(effectsize)
library(performance)
library(cowplot)  # for use with `plot_grid(x,x,ncol = x)` function
library(e1071) # for use with `skewness()` function
library(lmerTest)
library(emmeans)
library(broom.mixed)
library(forcats)
# emm_options(lmer.df = "satterthwaite")
```

Set emmeans options

```{r emmeans_options}
emm_options(
  lmer.df = "kenward-roger",
  pbkrtest.limit = 10000,
  disable.pbkrtest = FALSE
)
```

Set ggplot parameters

```{r ggplot_parameters}
# Color palette
my_palette_1 <- c(
  "#E31A1C",   # red
  "#1F78B4"  # blue
)

my_palette_2 <- c(
  "Simple"  = "#0072B2",
  "Complex" = "#E69F00"
)

my_linetypes_1 <- c(
  "Simple"  = "dashed",
  "Complex" = "solid"
)

# Theme
my_theme <- theme_classic(base_size = 10) +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal",
    legend.box = "horizontal"
  )

# Common guides
my_guides <- guides(
  colour = guide_legend(nrow = 1),
  fill   = guide_legend(nrow = 1)
)

```

Define 2-way interaction table function

```{r interaction_table_function.2way, echo=FALSE}
compact_emm_table <- function(emm_object,
                              by_var,
                              condition_prefix = NULL,
                              digits_est = 2,
                              digits_df = 1,
                              digits_p = 3) {
  
  by_var_name <- rlang::as_name(rlang::ensym(by_var))
  
  emm_df <- summary(emm_object) |>
    as.data.frame()
  
  contrast_df <- pairs(emm_object) |>
    summary() |>
    as.data.frame()
  
  # Focal factor columns are the EMM columns other than the conditioning variable
  focal_vars <- setdiff(
    names(emm_df),
    c(by_var_name, "emmean", "SE", "df", "lower.CL", "upper.CL")
  )
  
  emm_part <- emm_df |>
    rowwise() |>
    mutate(
      Comparison = paste(c_across(all_of(focal_vars)), collapse = " "),
      Condition = if (is.null(condition_prefix)) {
        as.character(.data[[by_var_name]])
      } else {
        paste(condition_prefix, "=", .data[[by_var_name]])
      }
    ) |>
    ungroup() |>
    transmute(
      Comparison,
      Condition,
      Estimate = emmean,
      SE,
      df,
      lower.CL,
      upper.CL,
      t.ratio = NA_real_,
      p.value = NA_real_
    )
  
  contrast_part <- contrast_df |>
    mutate(
      Comparison = contrast,
      Condition = if (is.null(condition_prefix)) {
        as.character(.data[[by_var_name]])
      } else {
        paste(condition_prefix, "=", .data[[by_var_name]])
      }
    ) |>
    transmute(
      Comparison,
      Condition,
      Estimate = estimate,
      SE,
      df,
      lower.CL = NA_real_,
      upper.CL = NA_real_,
      t.ratio,
      p.value
    )
  
  bind_rows(emm_part, contrast_part) |>
    arrange(Condition, Comparison) |>
    mutate(
      Estimate = round(Estimate, digits_est),
      SE       = round(SE, digits_est),
      df       = round(df, digits_df),
      lower.CL = round(lower.CL, digits_est),
      upper.CL = round(upper.CL, digits_est),
      t.ratio  = round(t.ratio, digits_est),
      p.value  = round(p.value, digits_p)
    )
}
```

```{r interaction_table_function.3way, echo=FALSE}
compact_3way_table <- function(emm_object,
                               by_var,
                               condition_prefix = NULL,
                               factor1,
                               factor2,
                               digits_est = 2,
                               digits_df = 1,
                               digits_p = 3) {
  
  by_var_name <- rlang::as_name(rlang::ensym(by_var))
  factor1_name <- rlang::as_name(rlang::ensym(factor1))
  factor2_name <- rlang::as_name(rlang::ensym(factor2))
  
  emm_df <- summary(emm_object) |>
    as.data.frame()
  
  make_condition <- function(x) {
    if (is.null(condition_prefix)) {
      as.character(x[[by_var_name]])
    } else {
      paste(condition_prefix, "=", x[[by_var_name]])
    }
  }
  
  emm_part <- emm_df |>
    mutate(
      Comparison = paste(.data[[factor1_name]], .data[[factor2_name]]),
      Condition = make_condition(cur_data())
    ) |>
    transmute(
      Comparison,
      Condition,
      Estimate = emmean,
      SE,
      df,
      lower.CL,
      upper.CL,
      t.ratio = NA_real_,
      p.value = NA_real_
    )
  
  factor1_part <- pairs(emm_object, simple = factor1_name) |>
    summary() |>
    as.data.frame() |>
    mutate(
      Comparison = contrast,
      Condition = paste(
        if (is.null(condition_prefix)) .data[[by_var_name]] else paste(condition_prefix, "=", .data[[by_var_name]]),
        "|",
        factor2_name, "=",
        .data[[factor2_name]]
      )
    ) |>
    transmute(
      Comparison,
      Condition,
      Estimate = estimate,
      SE,
      df,
      lower.CL = NA_real_,
      upper.CL = NA_real_,
      t.ratio,
      p.value
    )
  
  factor2_part <- pairs(emm_object, simple = factor2_name) |>
    summary() |>
    as.data.frame() |>
    mutate(
      Comparison = contrast,
      Condition = paste(
        if (is.null(condition_prefix)) .data[[by_var_name]] else paste(condition_prefix, "=", .data[[by_var_name]]),
        "|",
        factor1_name, "=",
        .data[[factor1_name]]
      )
    ) |>
    transmute(
      Comparison,
      Condition,
      Estimate = estimate,
      SE,
      df,
      lower.CL = NA_real_,
      upper.CL = NA_real_,
      t.ratio,
      p.value
    )
  
  interaction_part <- contrast(
  emm_object,
  interaction = c("pairwise", "pairwise")
) |>
  summary() |>
  as.data.frame() |>
  mutate(
    Comparison = paste0(
      "Int: ",
      .data[[paste0(factor1_name, "_pairwise")]],
      " across ",
      .data[[paste0(factor2_name, "_pairwise")]]
    ),
    Condition = make_condition(cur_data())
  ) |>
  transmute(
    Comparison,
    Condition,
    Estimate = estimate,
    SE,
    df,
    lower.CL = NA_real_,
    upper.CL = NA_real_,
    t.ratio,
    p.value
  )
  
  bind_rows(
    emm_part         |> mutate(RowType = 1),
    factor1_part     |> mutate(RowType = 2),
    factor2_part     |> mutate(RowType = 2),
    interaction_part |> mutate(RowType = 3)
  ) |>
    arrange(Condition, RowType, Comparison) |>
    mutate(
      Estimate = round(Estimate, digits_est),
      SE       = round(SE, digits_est),
      df       = round(df, digits_df),
      lower.CL = round(lower.CL, digits_est),
      upper.CL = round(upper.CL, digits_est),
      t.ratio  = round(t.ratio, digits_est),
      p.value  = round(p.value, digits_p)
    ) |>
    select(-RowType)
}
```


# Load Files

```{r load_files, message=FALSE, warning=FALSE}

# Load data: rt words

rt_w <- read_csv("rt_words_frq.csv") |>
  filter(correct == 1) |>
  mutate(
    SubjID = factor(SubjID),
    Item   = factor(target),
    logRT  = log(response_time),
    OS     = as.numeric(Dim.2),
    LP     = as.numeric(Dim.1),
    zLogBF = as.numeric(scale(LogBF)),
    zLogFS = as.numeric(scale(LogFS))
  )

# Load data: rt nonwords
rt_nw <- read_csv("rt_nwords_frq.csv") |>
  filter(correct == 1) |>
  mutate(
    SubjID = factor(SubjID),
    ItemID = factor(ItemID),
    complexity = factor(complexity,
                    levels = c("SIMP", "COMP"),
                    labels = c("Simple", "Complex")),
    logRT  = log(response_time),
    OS     = as.numeric(Dim.2),
    LP     = as.numeric(Dim.1),
    zLogBF = as.numeric(scale(LogBF)),
    zLogFS = as.numeric(scale(LogFS))
  )

# Load data: erp_fs words
erp_fs_w <- read_csv("erp_fs_dmg_words.csv") |>
  mutate(
    SubjID = factor(SubjID),
    chlabel = factor(chlabel),
    family_size = factor(family_size, 
                         levels = c("Small", "Large")),
    time_window = factor(time_window),
    OS = as.numeric(Dim.2),
    LP = as.numeric(Dim.1)
  )

# Load data: erp_fs nonwords
erp_fs_nw <- read_csv("erp_fs_dmg_nonwords.csv") |>
  mutate(
    SubjID = factor(SubjID),
    chlabel = factor(chlabel),
    family_size = factor(family_size, 
                         levels = c("Small", "Large")),
    complexity = factor(complexity,
                    labels = c("Simple", "Complex")),
    time_window = factor(time_window),
    OS = as.numeric(Dim.2),
    LP = as.numeric(Dim.1)
  )

# Load data: erp_bf words
erp_bf_w <- read_csv("erp_bf_dmg_words.csv") |>
  mutate(
    SubjID = factor(SubjID),
    chlabel = factor(chlabel),
    base_frequency = factor(base_frequency, 
                            levels = c("Low", "High")),
    time_window = factor(time_window),
    OS = as.numeric(Dim.2),
    LP = as.numeric(Dim.1)
  )

# Load data: erp_bf nonwords
erp_bf_nw <- read_csv("erp_bf_dmg_nonwords.csv") |>
  mutate(
    SubjID = factor(SubjID),
    chlabel = factor(chlabel),
    base_frequency = factor(base_frequency, 
                            levels = c("Low", "High")),
    complexity = factor(complexity,
                    labels = c("Simple", "Complex")),
    time_window = factor(time_window),
    OS = as.numeric(Dim.2),
    LP = as.numeric(Dim.1)
  )
```



```{r}
range(erp_fs_nw$LP)
range(erp_fs_nw$OS)
```

# RESPONSE TIME WORD DATA
## Word Model

```{r anova_rt_words}

library(lmerTest)

m_rt_words <-lmer(
  logRT ~ zLogBF + zLogFS + OS + LP +
    (1 | SubjID) +
    (1 | Item),
  data = rt_w,
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_rt_words)

# Effect sizes for individual terms
eta_squared(m_rt_words, partial = TRUE)

# Model R²
r2_nakagawa(m_rt_words)
```


```{r echo=FALSE}
library(ggeffects)
library(ggplot2)
library(patchwork)

plot_model_effect <- function(model, predictor, x_label) {

  pred <- ggpredict(
    model,
    terms = paste0(predictor, " [all]")
  ) |>
    as.data.frame()

  ggplot(
    pred,
    aes(
      x = x,
      y = exp(predicted)
    )
  ) +
    geom_ribbon(
      aes(
        ymin = exp(conf.low),
        ymax = exp(conf.high),
      ),
      fill = my_palette_2[1],
      alpha = 0.20,
      colour = NA
    ) +
    geom_line(linewidth = 1.1,
              colour = "#0072B2",
              linetype = my_linetypes_1[1]) +
    labs(
      x = x_label,
      y = "Predicted reaction time (ms)"
    ) +
#    theme_classic(base_size = 12) +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  my_theme +
  my_guides
}
```


```{r echo=FALSE, fig.height=7, fig.width=6}
BF_plot <- plot_model_effect(
  m_rt_words,
  predictor = "zLogBF",
  x_label = "Base Frequency (standardized log)"
)

FS_plot <- plot_model_effect(
  m_rt_words,
  predictor = "zLogFS",
  x_label = "Family Size (standardized log)"
)

OS_plot <- plot_model_effect(
  m_rt_words,
  predictor = "OS",
  x_label = "Orthographic Sensitivity"
)

LP_plot <- plot_model_effect(
  m_rt_words,
  predictor = "LP",
  x_label = "Language Proficiency"
)

(BF_plot | FS_plot) /
  (OS_plot | LP_plot) +
  plot_annotation(
    title = "Adjusted Effects on Reaction Time"
  )
```
* Higher base frequency predicts faster RTs, $b=-0.0172$, $p<.001$.
* Larger family size predicts faster RTs, $b=-0.0129$, $p=.010$.
* Higher orthographic sensitivity is associated with faster RTs, but the effect does not reach the conventional significance threshold, ($p=.069$).
* Lexical proficiency has little apparent relationship with RT in this model, ($p=.353$).

---
To compare the relative effects of the four continuous predictors, plot their model coefficients and 95% confidence intervals. Because your outcome is `logRT`, it is useful to transform each coefficient into the percentage change in reaction time associated with a one-unit increase in the predictor.

If all four predictors are standardized, that becomes the percentage change associated with a one-standard-deviation increase.

```{r}
library(broom.mixed)
library(forcats)

coef_plot_data <- tidy(
  m_rt_words,
  effects = "fixed",
  conf.int = TRUE,
  conf.level = 0.95
) |>
  filter(term %in% c("zLogBF", "zLogFS", "OS", "LP")) |>
  mutate(
    Predictor = recode(
      term,
      zLogBF = "Base Frequency",
      zLogFS = "Family Size",
      OS     = "Orthographic Sensitivity",
      LP     = "Language Proficiency"
    ),

    # Convert log-RT coefficients to percentage change in RT
    percent_change = 100 * (exp(estimate) - 1),
    conf.low_pct   = 100 * (exp(conf.low) - 1),
    conf.high_pct  = 100 * (exp(conf.high) - 1),

    Predictor = fct_reorder(Predictor, percent_change)
  )
```

Then plot the coefficients:

```{r}
ggplot(
  coef_plot_data,
  aes(
    x = percent_change,
    y = Predictor
  )
) +
  geom_vline(
    xintercept = 0,
    linetype = "dashed",
    colour = "grey50"
  ) +
  geom_errorbar(
    aes(
      xmin = conf.low_pct,
      xmax = conf.high_pct
    ),
    width = 0.15,
    linewidth = 0.8,
    colour = "#0072B2"
  ) +
  geom_point(
    size = 3,
    colour = "#0072B2"
  ) +
  labs(
    x = "Percentage change in predicted reaction time",
    y = NULL,
    title = "Adjusted Effects on Reaction Time"
  ) +
  my_theme
```

Interpretation:

* Values above zero indicate slower reaction times as the predictor increases.
* Values below zero indicate faster reaction times.
* A confidence interval crossing zero indicates that the coefficient is not clearly different from zero.
* The farther the estimate is from zero, the larger the adjusted effect, provided the predictors are on the same standardized scale.

For example, a value of `-4` means that a one-unit increase in the predictor is associated with approximately a 4% reduction in predicted RT, holding the other variables constant.

<!-- If `OS` and `LP` are not standardized, standardize them before fitting the model: -->

```{r}
# rt_nw <- rt_nw |>
#   mutate(
#     zOS = as.numeric(scale(OS)),
#     zLP = as.numeric(scale(LP))
#   )
# ```
# 
# Then refit using `zOS` and `zLP`:
# 
# ```{r}
# m_rt_words_standardized <- lmer(
#   logRT ~ complexity + zLogBF + zLogFS + zOS + zLP +
#     (1 + complexity | SubjID) +
#     (1 | ItemID),
#   data = rt_nw
# )
```




---

# RESPONSE TIME NONWORD DATA
## Model
```{r anova_rt_nonwords}
contrasts(rt_nw$complexity) <- c(-0.5, 0.5)

m_rt_nw <- lmer(
  logRT ~ complexity + zLogBF + zLogFS + OS + LP +
    (1 + complexity | SubjID) +
    (1 | ItemID),
  data = rt_nw,
  control = lmerControl(optimizer = "bobyqa")
)
m_rt_nw
summary(m_rt_nw)

# Effect sizes for individual terms
eta_squared(m_rt_nw, partial = TRUE)

# Model R²
r2_nakagawa(m_rt_nw)

# Means
# get means on log scale
emm_logrt <- emmeans(m_rt_nw, ~ complexity)
emm_summary <- summary(emm_logrt)

# back transform manually
emm_summary$mean_ms <- exp(emm_summary$emmean)
emm_summary$lower_ms <- exp(emm_summary$lower.CL)
emm_summary$upper_ms <- exp(emm_summary$upper.CL)
emm_summary

diff_ms <- exp(emm_summary$emmean[emm_summary$complexity == "Complex"]) -
            exp(emm_summary$emmean[emm_summary$complexity == "Simple"])
diff_ms
```


For this model, use one adjusted-means plot for the categorical predictor `complexity` and four adjusted-effect plots for the continuous predictors. Because there are no interactions, the continuous-predictor slopes do not vary by complexity on the model’s log-RT scale.


```{r echo=FALSE}
library(ggeffects)
library(ggplot2)
library(patchwork)

plot_continuous_effect <- function(model, predictor, x_label) {

  pred <- ggpredict(
    model,
    terms = c(
      paste0(predictor, " [all]"),
      "complexity"
    )
  ) |>
    as.data.frame()

  ggplot(
    pred,
    aes(
      x = x,
      y = exp(predicted),
      colour = group,
      fill = group,
      linetype = group
    )
  ) +
    geom_ribbon(
      aes(
        ymin = exp(conf.low),
        ymax = exp(conf.high)
      ),
      alpha = 0.18,
      colour = NA
    ) +
    geom_line(linewidth = 1.1) +
    scale_colour_manual(
      values = my_palette_2,
      name = "Complexity"
    ) +
    scale_fill_manual(
      values = my_palette_2,
      name = "Complexity"
    ) +
    scale_linetype_manual(
      values = my_linetypes_1,
      name = "Complexity"
    ) +
    labs(
      x = x_label,
      y = "Predicted reaction time (ms)"
    ) +
    theme_classic(base_size = 12) +
    theme(
      legend.position = "bottom"
    )
}
```


```{r echo=FALSE}
#Create the complexity plot:
complexity_pred <- ggpredict(
  m_rt_nw,
  terms = "complexity"
) |>
  as.data.frame()

complexity_plot <- ggplot(
  complexity_pred,
  aes(
    x = x,
    y = exp(predicted),
    colour = x
  )
) +
  geom_point(size = 3.5) +
  geom_errorbar(
    aes(
      ymin = exp(conf.low),
      ymax = exp(conf.high)
    ),
    width = 0.10,
    linewidth = 0.9
  ) +
  scale_colour_manual(
    values = my_palette_2,
    name = "Complexity"
  ) +
  labs(
    x = "Complexity",
    y = "Predicted reaction time (ms)"
  ) +
  theme_classic(base_size = 12) +
  theme(
    legend.position = "none"
  )
```


```{r echo=FALSE}
# Create the four continuous-predictor plots:
BF_plot <- plot_model_effect(
  m_rt_nw,
  predictor = "zLogBF",
  x_label = "Base Frequency (standardized log)"
)

FS_plot <- plot_model_effect(
  m_rt_nw,
  predictor = "zLogFS",
  x_label = "Family Size (standardized log)"
)

OS_plot <- plot_model_effect(
  m_rt_nw,
  predictor = "OS",
  x_label = "Orthographic Sensitivity"
)

LP_plot <- plot_model_effect(
  m_rt_nw,
  predictor = "LP",
  x_label = "Language Proficiency"
)
```

Then combine them:

```{r include=FALSE}

complexity_plot |
  (BF_plot | FS_plot) /
  (OS_plot | LP_plot) +
  plot_layout(widths = c(0.75, 2)) +
  plot_annotation(
    title = "Adjusted Effects on Nonword Reaction Time"
  )

(complexity_plot | BF_plot | FS_plot) /
  (OS_plot | LP_plot | plot_spacer()) +
  plot_layout(guides = "collect") +
  plot_annotation(
    title = "Adjusted Effects on Nonword Reaction Time"
  ) &
  theme(
    legend.position = "bottom"
  )
```

```{r fig.height=9}
# row1 <- plot_grid( BF_plot,  FS_plot, OS_plot, LP_plot, ncol = 2)


row1 <- plot_grid(
  BF_plot,
  FS_plot,
  ncol = 2,
  align = "hv"
)

row2 <- plot_grid(
  OS_plot,
  LP_plot,
  ncol = 2,
  align = "hv"
)

plot_grid(
  ggdraw() + draw_label("Nonword RT Data", fontface = "bold"),
  complexity_plot,
  row1,
  row2,
  ncol = 1,
  rel_heights = c(0.10, 1, 1, 1)
)
```


* Complex nonwords are substantially slower than simple nonwords.
* Higher base frequency predicts slower nonword responses.
* Family size has a small, nonsignificant negative relationship with RT.
* Higher orthographic sensitivity predicts faster responses.
* Lexical proficiency has essentially no adjusted relationship with RT.

---
```{r}
library(broom.mixed)
library(forcats)

coef_plot_data_nw <- tidy(
  m_rt_nw,
  effects = "fixed",
  conf.int = TRUE,
  conf.level = 0.95
) |>
  filter(term %in% c("zLogBF", "zLogFS", "OS", "LP")) |>
  mutate(
    Predictor = recode(
      term,
      zLogBF = "Base Frequency",
      zLogFS = "Family Size",
      OS     = "Orthographic Sensitivity",
      LP     = "Language Proficiency"
    ),

    # Convert log-RT coefficients to percentage change in RT
    percent_change = 100 * (exp(estimate) - 1),
    conf.low_pct   = 100 * (exp(conf.low) - 1),
    conf.high_pct  = 100 * (exp(conf.high) - 1),

    Predictor = fct_reorder(Predictor, percent_change)
  )
```

Then plot the coefficients:

```{r}
nw_coef_plot <-ggplot(
  coef_plot_data_nw,
  aes(
    x = percent_change,
    y = Predictor
  )
) +
  geom_vline(
    xintercept = 0,
    linetype = "dashed",
    colour = "grey50"
  ) +
  geom_errorbar(
    aes(
      xmin = conf.low_pct,
      xmax = conf.high_pct
    ),
    width = 0.15,
    linewidth = 0.8,
    colour = "#0072B2"
  ) +
  geom_point(
    size = 3,
    colour = "#0072B2"
  ) +
  labs(
    x = "Percentage change in predicted reaction time",
    y = NULL,
    title = "Adjusted Effects on Reaction Time"
  ) +
  my_theme
```

```{r}
plot_grid(complexity_plot, nw_coef_plot, ncol = 2, rel_widths = c(1,2))
```

---

# EXPLORATORY ANALYSIS

The original nonword RT model was specified without Complexity × LP or Complexity × OS interactions by design — the RT models were confirmatory and included individual differences as main effects only, reflecting the theoretical decision that RT models were specified for efficiency rather than morphological architecture.
When asignificant Complexity × OS interaction in the exploratory symmetric N400 model was discovered, it was decided to run an exploratory nonword RT model that included both Complexity × OS and Complexity × LP interactions, to check whether the neural patterns had any behavioral counterpart. 

```{r}
m_rt_nw_os_lp <- lmer(
  logRT ~ complexity * OS + complexity * LP + zLogBF + zLogFS +
    (1 + complexity | SubjID) + (1 | ItemID),
  data = rt_nw,
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_rt_nw_os_lp)
```

## Means and Contrasts

```{r}
emm_options(lmer.df = "satterthwaite")
emmeans(m_rt_nw_os_lp, pairwise ~ complexity | LP,
        at = list(LP = c(-2.5, -1, 0, 1, 3)),
        tran = "log")
```

```{r}
## complexity x OS
emm_rt_nw_os_lp <- emmeans(m_rt_nw_os_lp,
                      ~ complexity | LP,
                      at = list(LP = c(-2.5, -1, 0, 1, 3.0)))

emm_part <- summary(emm_rt_nw_os_lp) |>
  as.data.frame() |>
  transmute(LP, Effect = paste("EMM:", complexity), Estimate = emmean, SE, df, 
            lower.CL, upper.CL, t.ratio = NA_real_, p.value = NA_real_)

contrast_part <- pairs(emm_rt_nw_os_lp) |>
  summary() |>
  as.data.frame() |>
  transmute(LP, Effect = paste("Contrast:", contrast), Estimate = estimate, SE, df,
            lower.CL = NA_real_, upper.CL = NA_real_, t.ratio, p.value)

emm_contrast_table_rt_nw_os_lp <- bind_rows(emm_part, contrast_part) |>
  arrange(LP, Effect)|>
  mutate(
    Estimate = round(Estimate, 2),
    SE       = round(SE, 2),
    df       = round(df, 1),
    lower.CL = round(lower.CL, 2),
    upper.CL = round(upper.CL, 2),
    t.ratio  = round(t.ratio, 2),
    p.value  = round(p.value, 3)
  )
# Force RStudio to show more rows inline by using the as.tibble() function
as_tibble(emm_contrast_table_rt_nw_os_lp) |> print(n = 50)

```

## Plots


```{r echo=FALSE}
# Create the four continuous-predictor plots:
BF_plot_exp <- plot_continuous_effect(
  m_rt_nw_os_lp,
  predictor = "zLogBF",
  x_label = "Base Frequency (standardized log)"
)

FS_plot_exp <- plot_continuous_effect(
  m_rt_nw_os_lp,
  predictor = "zLogFS",
  x_label = "Family Size (standardized log)"
)

OS_plot_exp <- plot_continuous_effect(
  m_rt_nw_os_lp,
  predictor = "OS",
  x_label = "Orthographic Sensitivity"
)

LP_plot_exp <- plot_continuous_effect(
  m_rt_nw_os_lp,
  predictor = "LP",
  x_label = "Language Proficiency"
)
```



```{r fig.height=9}
# row1 <- plot_grid( BF_plot,  FS_plot, OS_plot, LP_plot, ncol = 2)


row1 <- plot_grid(
  BF_plot_exp,
  FS_plot_exp,
  ncol = 2,
  align = "hv"
)

row2 <- plot_grid(
  OS_plot_exp,
  LP_plot_exp,
  ncol = 2,
  align = "hv"
)

plot_grid(
  ggdraw() + draw_label("Nonword RT Data", fontface = "bold"),
  complexity_plot,
  row1,
  row2,
  ncol = 1,
  rel_heights = c(0.10, 1, 1, 1)
)
```


