---
title: "M21 2026 July 2026 N250 Component WORDS"
author: "Joanna Morris"
date: "`r Sys.Date()`"
output: 
  bookdown::pdf_document2:
    toc: true
    toc_depth: 3
    number_sections: true
header-includes:
  - \setcounter{secnumdepth}{3}
editor_options: 
  chunk_output_type: inline
---

\scriptsize

# Setup
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE, 
                      error = FALSE,
                      comment = "||",
                      fig.height = 4,
                      fig.width = 7)
options(width = 150)
```

## Load libraries

```{r load_libraries, echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(ggeffects)
library(lme4)
library(afex)
library(gridExtra)
library(MuMIn)
library(pbkrtest)
library(effectsize)
library(performance)
library(cowplot)  # for use with `plot_grid(x,x,ncol = x)` function
library(e1071) # for use with `skewness()` function
library(lmerTest)
library(emmeans)
# emm_options(lmer.df = "satterthwaite")
```

Set emmeans options

```{r emmeans_options}
emm_options(
  lmer.df = "kenward-roger",
  pbkrtest.limit = 10000,
  disable.pbkrtest = FALSE
)
```

## Set ggplot parameters

```{r ggplot_parameters}
# Color palette
my_palette_1 <- c(
  "#E31A1C",   # red
  "#1F78B4"  # blue
)

my_palette_2 <- c(
  "#0072B2",  # dark blue
  "#E69F00"   # orange/gold
)
my_linetypes_1 <- c("dashed", "solid")

# Theme
my_theme <- theme_classic(base_size = 10) +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal",
    legend.box = "horizontal"
  )

# Common guides
my_guides <- guides(
  colour = guide_legend(nrow = 1),
  fill   = guide_legend(nrow = 1)
)

```

## Define interaction table functions

```{r interaction_table_function.2way, echo=FALSE}
compact_emm_table <- function(emm_object,
                              by_var,
                              condition_prefix = NULL,
                              digits_est = 2,
                              digits_df = 1,
                              digits_p = 3) {
  
  by_var_name <- rlang::as_name(rlang::ensym(by_var))
  
  emm_df <- summary(emm_object) |>
    as.data.frame()
  
  contrast_df <- pairs(emm_object) |>
    summary() |>
    as.data.frame()
  
  # Focal factor columns are the EMM columns other than the conditioning variable
  focal_vars <- setdiff(
    names(emm_df),
    c(by_var_name, "emmean", "SE", "df", "lower.CL", "upper.CL")
  )
  
  emm_part <- emm_df |>
    rowwise() |>
    mutate(
      Comparison = paste(c_across(all_of(focal_vars)), collapse = " "),
      Condition = if (is.null(condition_prefix)) {
        as.character(.data[[by_var_name]])
      } else {
        paste(condition_prefix, "=", .data[[by_var_name]])
      }
    ) |>
    ungroup() |>
    transmute(
      Comparison,
      Condition,
      Estimate = emmean,
      SE,
      df,
      lower.CL,
      upper.CL,
      t.ratio = NA_real_,
      p.value = NA_real_
    )
  
  contrast_part <- contrast_df |>
    mutate(
      Comparison = contrast,
      Condition = if (is.null(condition_prefix)) {
        as.character(.data[[by_var_name]])
      } else {
        paste(condition_prefix, "=", .data[[by_var_name]])
      }
    ) |>
    transmute(
      Comparison,
      Condition,
      Estimate = estimate,
      SE,
      df,
      lower.CL = NA_real_,
      upper.CL = NA_real_,
      t.ratio,
      p.value
    )
  
  bind_rows(emm_part, contrast_part) |>
    arrange(Condition, Comparison) |>
    mutate(
      Estimate = round(Estimate, digits_est),
      SE       = round(SE, digits_est),
      df       = round(df, digits_df),
      lower.CL = round(lower.CL, digits_est),
      upper.CL = round(upper.CL, digits_est),
      t.ratio  = round(t.ratio, digits_est),
      p.value  = round(p.value, digits_p)
    )
}
```


```{r interaction_table_function.3way, echo=FALSE}
compact_3way_table <- function(emm_object,
                               by_var,
                               condition_prefix = NULL,
                               factor1,
                               factor2,
                               digits_est = 2,
                               digits_df = 1,
                               digits_p = 3) {
  
  by_var_name <- rlang::as_name(rlang::ensym(by_var))
  factor1_name <- rlang::as_name(rlang::ensym(factor1))
  factor2_name <- rlang::as_name(rlang::ensym(factor2))
  
  emm_df <- summary(emm_object) |>
    as.data.frame()
  
  make_condition <- function(x) {
    if (is.null(condition_prefix)) {
      as.character(x[[by_var_name]])
    } else {
      paste(condition_prefix, "=", x[[by_var_name]])
    }
  }
  
  emm_part <- emm_df |>
    mutate(
      Comparison = paste(.data[[factor1_name]], .data[[factor2_name]]),
      Condition = make_condition(cur_data())
    ) |>
    transmute(
      Comparison,
      Condition,
      Estimate = emmean,
      SE,
      df,
      lower.CL,
      upper.CL,
      t.ratio = NA_real_,
      p.value = NA_real_
    )
  
  factor1_part <- pairs(emm_object, simple = factor1_name) |>
    summary() |>
    as.data.frame() |>
    mutate(
      Comparison = contrast,
      Condition = paste(
        if (is.null(condition_prefix)) .data[[by_var_name]] else paste(condition_prefix, "=", .data[[by_var_name]]),
        "|",
        factor2_name, "=",
        .data[[factor2_name]]
      )
    ) |>
    transmute(
      Comparison,
      Condition,
      Estimate = estimate,
      SE,
      df,
      lower.CL = NA_real_,
      upper.CL = NA_real_,
      t.ratio,
      p.value
    )
  
  factor2_part <- pairs(emm_object, simple = factor2_name) |>
    summary() |>
    as.data.frame() |>
    mutate(
      Comparison = contrast,
      Condition = paste(
        if (is.null(condition_prefix)) .data[[by_var_name]] else paste(condition_prefix, "=", .data[[by_var_name]]),
        "|",
        factor1_name, "=",
        .data[[factor1_name]]
      )
    ) |>
    transmute(
      Comparison,
      Condition,
      Estimate = estimate,
      SE,
      df,
      lower.CL = NA_real_,
      upper.CL = NA_real_,
      t.ratio,
      p.value
    )
  
  interaction_part <- contrast(
  emm_object,
  interaction = c("pairwise", "pairwise")
) |>
  summary() |>
  as.data.frame() |>
  mutate(
    Comparison = paste0(
      "Int: ",
      .data[[paste0(factor1_name, "_pairwise")]],
      " across ",
      .data[[paste0(factor2_name, "_pairwise")]]
    ),
    Condition = make_condition(cur_data())
  ) |>
  transmute(
    Comparison,
    Condition,
    Estimate = estimate,
    SE,
    df,
    lower.CL = NA_real_,
    upper.CL = NA_real_,
    t.ratio,
    p.value
  )
  
  bind_rows(
    emm_part         |> mutate(RowType = 1),
    factor1_part     |> mutate(RowType = 2),
    factor2_part     |> mutate(RowType = 2),
    interaction_part |> mutate(RowType = 3)
  ) |>
    arrange(Condition, RowType, Comparison) |>
    mutate(
      Estimate = round(Estimate, digits_est),
      SE       = round(SE, digits_est),
      df       = round(df, digits_df),
      lower.CL = round(lower.CL, digits_est),
      upper.CL = round(upper.CL, digits_est),
      t.ratio  = round(t.ratio, digits_est),
      p.value  = round(p.value, digits_p)
    ) |>
    select(-RowType)
}
```


```{r interaction_trends_function.3way}
compact_3way_trends_table <- function(model,
                                      focal_var,
                                      moderator_var,
                                      condition_var,
                                      moderator_values,
                                      condition_prefix = NULL,
                                      digits_est = 2,
                                      digits_df = 1,
                                      digits_p = 3,
                                      lmerTest.limit = NULL) {
  
  library(emmeans)
  library(dplyr)
  library(rlang)

  focal_name     <- rlang::as_name(rlang::ensym(focal_var))
  moderator_name <- rlang::as_name(rlang::ensym(moderator_var))
  condition_name <- rlang::as_name(rlang::ensym(condition_var))

  # Construct emtrends formula:
  # ~ condition_var | moderator_var
  trend_formula <- as.formula(
    paste0("~ ", condition_name, " | ", moderator_name)
  )

  # Values at which the moderator is evaluated
  at_list <- setNames(
    list(moderator_values),
    moderator_name
  )

  # ------------------------------------------------------------
  # Estimate focal-variable slopes at each moderator value
  # separately for each categorical condition
  # ------------------------------------------------------------

  if (is.null(lmerTest.limit)) {

    trends <- emtrends(
      model,
      specs = trend_formula,
      var = focal_name,
      at = at_list
    )

  } else {

    trends <- emtrends(
      model,
      specs = trend_formula,
      var = focal_name,
      at = at_list,
      lmerTest.limit = lmerTest.limit
    )
  }

  trend_col <- paste0(focal_name, ".trend")

  # ------------------------------------------------------------
  # Simple slopes
  # ------------------------------------------------------------

  slope_part <- summary(
    trends,
    infer = c(TRUE, TRUE)
  ) |>
    as.data.frame() |>
    mutate(
      Comparison = paste0(
        focal_name,
        " slope: ",
        .data[[condition_name]]
      ),

      Condition = paste0(
        moderator_name,
        " = ",
        .data[[moderator_name]]
      ),

      Estimate = .data[[trend_col]],

      RowType = 1
    ) |>
    transmute(
      Comparison,
      Condition,
      ModeratorValue = .data[[moderator_name]],
      Estimate,
      SE,
      df,
      lower.CL,
      upper.CL,
      t.ratio,
      p.value,
      RowType
    )

  # ------------------------------------------------------------
  # Difference between focal-variable slopes across levels
  # of the categorical factor
  # ------------------------------------------------------------

  contrast_part <- pairs(trends) |>
    summary(
      infer = c(TRUE, TRUE)
    ) |>
    as.data.frame() |>
    mutate(
      Comparison = paste0(
        focal_name,
        " slope difference: ",
        contrast
      ),

      Condition = paste0(
        moderator_name,
        " = ",
        .data[[moderator_name]]
      ),

      RowType = 2
    ) |>
    transmute(
      Comparison,
      Condition,
      ModeratorValue = .data[[moderator_name]],
      Estimate = estimate,
      SE,
      df,
      lower.CL,
      upper.CL,
      t.ratio,
      p.value,
      RowType
    )

  # ------------------------------------------------------------
  # Combine and format
  # ------------------------------------------------------------

  bind_rows(
    slope_part,
    contrast_part
  ) |>
    arrange(
      .data$ModeratorValue,
      .data$RowType,
      .data$Comparison
  ) |>
    mutate(
      Estimate = round(Estimate, digits_est),
      SE       = round(SE, digits_est),
      df       = round(df, digits_df),
      lower.CL = round(lower.CL, digits_est),
      upper.CL = round(upper.CL, digits_est),
      t.ratio  = round(t.ratio, digits_est),
      p.value  = round(p.value, digits_p)
    ) |>
    select(-RowType, -ModeratorValue)
}
```


# Load Files

```{r load_files, message=FALSE, warning=FALSE}

# Load data: rt words

# rt_w <- read_csv("rt_words_frq.csv") |>
#   filter(correct == 1) |>
#   mutate(
#     SubjID = factor(SubjID),
#     Item   = factor(target),
#     logRT  = log(response_time),
#     OS     = as.numeric(Dim.2),
#     LP     = as.numeric(Dim.1),
#     zLogBF = as.numeric(scale(LogBF)),
#     zLogFS = as.numeric(scale(LogFS))
#   )

# Load data: rt nonwords

# rt_nw <- read_csv("rt_nwords_frq.csv") |>
#   filter(correct == 1) |>
#   mutate(
#     SubjID = factor(SubjID),
#     ItemID = factor(ItemID),
#     complexity = factor(complexity,
#                     levels = c("SIMP", "COMP"),
#                     labels = c("Simple", "Complex")),
#     logRT  = log(response_time),
#     OS     = as.numeric(Dim.2),
#     LP     = as.numeric(Dim.1),
#     zLogBF = as.numeric(scale(LogBF)),
#     zLogFS = as.numeric(scale(LogFS))
#   )

# Load data: erp_fs words
erp_fs_w <- read_csv("erp_fs_dmg_words.csv") |>
  mutate(
    SubjID = factor(SubjID),
    chlabel = factor(chlabel),
    family_size = factor(family_size, 
                         levels = c("Small", "Large")),
    time_window = factor(time_window),
    OS = as.numeric(Dim.2),
    LP = as.numeric(Dim.1)
  )

# Load data: erp_fs nonwords

# erp_fs_nw <- read_csv("erp_fs_dmg_nonwords.csv") |>
#   mutate(
#     SubjID = factor(SubjID),
#     chlabel = factor(chlabel),
#     family_size = factor(family_size, 
#                          levels = c("Small", "Large")),
#     complexity = factor(complexity,
#                     labels = c("Simple", "Complex")),
#     time_window = factor(time_window),
#     OS = as.numeric(Dim.2),
#     LP = as.numeric(Dim.1)
#   )

# Load data: erp_bf words

erp_bf_w <- read_csv("erp_bf_dmg_words.csv") |>
  mutate(
    SubjID = factor(SubjID),
    chlabel = factor(chlabel),
    base_frequency = factor(base_frequency, 
                            levels = c("Low", "High")),
    time_window = factor(time_window),
    OS = as.numeric(Dim.2),
    LP = as.numeric(Dim.1)
  )

# Load data: erp_bf nonwords

# erp_bf_nw <- read_csv("erp_bf_dmg_nonwords.csv") |>
#   mutate(
#     SubjID = factor(SubjID),
#     chlabel = factor(chlabel),
#     base_frequency = factor(base_frequency, 
#                             levels = c("Low", "High")),
#     complexity = factor(complexity,
#                     labels = c("Simple", "Complex")),
#     time_window = factor(time_window),
#     OS = as.numeric(Dim.2),
#     LP = as.numeric(Dim.1)
#   )
```


# N250 WORD DATA

## N250 WORD DATA: BASE FREQUENCY 

### Model


Model Comparison

```{r anova_n250_words_bf_max}
contrasts(erp_bf_w$base_frequency) <- c(-0.5, 0.5)


# Model with the two individual-difference interactions with base frequency
m_base_bf <- lmer(
  value ~ base_frequency * OS +
          base_frequency * LP +
          (1 | SubjID) +
          (1 | SubjID:chlabel),
  data = subset(erp_bf_w, time_window == "N250"),
  REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

# Add OS × LP
m_2way_bf <- update(
  m_base_bf,
  . ~ . + OS:LP
)

# Add the three-way interaction
m_3way_bf <- update(
  m_2way_bf,
  . ~ . + base_frequency:OS:LP
)

anova(m_base_bf, m_2way_bf, m_3way_bf)

summary(m_3way_bf)
```

```{r anova_n250_words_bf}
contrasts(erp_bf_w$base_frequency) <- c(-0.5, 0.5)


m_w_N250_bf <- lmer(
  value ~ base_frequency * OS * LP +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_bf_w, time_window == "N250"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_w_N250_bf)

# Effect sizes for individual terms
eta_squared(m_w_N250_bf, partial = TRUE)

# Model R²
r2_nakagawa(m_w_N250_bf)
```

```{r}
library(emmeans)
emm_options(lmer.df = "satterthwaite")

# Base Frequency three-way follow-up
# Representative values: mean and ±1 SD for each continuous IV
os_vals_bf <- c(mean(erp_bf_w$OS) - sd(erp_bf_w$OS), mean(erp_bf_w$OS), mean(erp_bf_w$OS) + sd(erp_bf_w$OS))
lp_vals_bf <- c(mean(erp_bf_w$LP) - sd(erp_bf_w$LP), mean(erp_bf_w$LP), mean(erp_bf_w$LP) + sd(erp_bf_w$LP))

emm_bf <- emmeans(m_3way_bf, ~ base_frequency | OS * LP,
                   at = list(OS = os_vals_bf, LP = lp_vals_bf))
bf_followup <- contrast(emm_bf, method = "revpairwise", by = c("OS", "LP"))
summary(bf_followup, infer = c(TRUE, TRUE))
```

#### Means and contrasts

```{r means_n250_words_bf_OS}
as.tibble(emmeans(m_w_N250_bf, ~ base_frequency)) |> print()

emm_bf_OS <- emmeans(m_w_N250_bf,
                      ~ base_frequency | OS,
                      at = list(OS = c(-1.9, -1.5, -1, 0, 1, 1.5, 1.9)),
                     lmerTest.limit = 6480)

emm_part <- summary(emm_bf_OS) |>
  as.data.frame() |>
  transmute(OS, Effect = paste("EMM:", base_frequency), Estimate = emmean, SE, df, 
            lower.CL, upper.CL, t.ratio = NA_real_, p.value = NA_real_)

contrast_part <- pairs(emm_bf_OS) |>
  summary() |>
  as.data.frame() |>
  transmute(OS,Effect = paste("Contrast:", contrast), Estimate = estimate, SE, df,
            lower.CL = NA_real_, upper.CL = NA_real_, t.ratio, p.value)

emm_contrast_table <- bind_rows(emm_part, contrast_part) |>
  arrange(OS, Effect)|>
  mutate(
    Estimate = round(Estimate, 2),
    SE       = round(SE, 2),
    df       = round(df, 1),
    lower.CL = round(lower.CL, 2),
    upper.CL = round(upper.CL, 2),
    t.ratio  = round(t.ratio, 2),
    p.value  = round(p.value, 3)
  )

as.tibble(emm_contrast_table, digits = 3) |> print(n = 50)
```

```{r means_n250_words_bf_LP}
as.tibble(emmeans(m_w_N250_bf, ~ base_frequency)) |> print()

emm_bf_LP <- emmeans(m_w_N250_bf,
                      ~ base_frequency | LP,
                      at = list(LP = c(-2.5, -1.5, -1, 0, 1, 1.5, 3.0)),
                     lmerTest.limit = 6480)

emm_part <- summary(emm_bf_LP) |>
  as.data.frame() |>
  transmute(LP, Effect = paste("EMM:", base_frequency), Estimate = emmean, SE, df, 
            lower.CL, upper.CL, t.ratio = NA_real_, p.value = NA_real_)

contrast_part <- pairs(emm_bf_LP) |>
  summary() |>
  as.data.frame() |>
  transmute(LP,Effect = paste("Contrast:", contrast), Estimate = estimate, SE, df,
            lower.CL = NA_real_, upper.CL = NA_real_, t.ratio, p.value)

emm_contrast_table <- bind_rows(emm_part, contrast_part) |>
  arrange(LP, Effect)|>
  mutate(
    Estimate = round(Estimate, 2),
    SE       = round(SE, 2),
    df       = round(df, 1),
    lower.CL = round(lower.CL, 2),
    upper.CL = round(upper.CL, 2),
    t.ratio  = round(t.ratio, 2),
    p.value  = round(p.value, 3)
  )

as.tibble(emm_contrast_table, digits = 3) |> print(n = 50)
```

How does the slope of LP change across OS, separately for High and Low base frequency? This gives you an `LP.trend` rather than an `emmean.` Each estimate tells you the predicted change in N250 amplitude for a one-unit increase in LP at that particular value of OS and base frequency.

```{r}
# LP slopes at selected OS values, separately by base frequency

emm_LP_slopes <- emtrends(
  m_w_N250_bf,
  ~ OS | base_frequency,
  var = "LP",
  at = list(
    OS = c(-1.9, -1.5, -1, 0, 1.5, 1, 1.9)
  ),
  lmerTest.limit = 6480
)

summary(emm_LP_slopes, infer = TRUE)

# You can then compare the LP slopes between the two base-frequency conditions:

emm_LP_slopes_bf <- emtrends(
  m_w_N250_bf,
  ~ base_frequency | OS,
  var = "LP",
  at = list(
    OS = c(-1.9, -1.5, -1, 0, 1.5, 1, 1.9)
  ),
  lmerTest.limit = 6480
)

pairs(emm_LP_slopes_bf) |>
  summary(infer = TRUE)
```


```{r}
# OS slopes at selected LP values, separately by base frequency

emm_OS_slopes <- emtrends(
  m_w_N250_bf,
  ~ LP | base_frequency,
  var = "OS",
  at = list(
    LP = c(-2.5, -1, 0, 1, 3)
  ),
  lmerTest.limit = 6480
)

summary(emm_OS_slopes, infer = TRUE)

emm_OS_slopes_bf <- emtrends(
  m_w_N250_bf,
  ~ base_frequency | LP,
  var = "OS",
  at = list(
    LP = c(-2.5, -1, 0, 1, 3)
  ),
  lmerTest.limit = 6480
)

pairs(emm_OS_slopes_bf) |>
  summary(infer = TRUE)
```

```{r}
# To examine LP slopes across selected OS values:
LP_3way_trends_bf <- compact_3way_trends_table(
  model = m_w_N250_bf,
  focal_var = LP,
  moderator_var = OS,
  condition_var = base_frequency,
  moderator_values = c(-1.9, -1.5, -1, 0, 1, 1.5, 1.9),
  condition_prefix = "BF",
  lmerTest.limit = 6480
)

as.tibble(LP_3way_trends_bf) |>
  print(n = 50)

# To examine OS slopes across selected LP values:

OS_3way_trends_bf <- compact_3way_trends_table(
  model = m_w_N250_bf,
  focal_var = OS,
  moderator_var = LP,
  condition_var = base_frequency,
  moderator_values = c(-2.5, -1.5, -1, 0, 1, 1.5, 3),
  condition_prefix = "BF",
  lmerTest.limit = 6480
)

as.tibble(OS_3way_trends_bf) |>
  print(n = 50)
```

#### Plots

```{r plot_n250_words_bf_OS, echo=FALSE,  include=FALSE}
library(ggeffects)
library(ggplot2)

# Predicted values across the observed range of OS
# pred <- ggpredict(
#   m_w_N250_bf,
#   terms = c("OS", "base_frequency")
# )

(pred_BF_OS <- ggemmeans(
  m_w_N250_bf,
  terms = c(
    "OS [all]",
    "base_frequency"
  )))

(BFxOS_n250 <- ggplot(pred_BF_OS,
       aes(x = x,
           y = predicted,
           color = group,
           fill = group,
           linetype = group)) +
  geom_line(size = 1.5) +
  geom_ribbon(aes(ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              colour = NA) +
  labs(
    x = "Orthographic Sensitivity (OS)",
    y = "Predicted N250 amplitude (µV)",
    title = expression(
      beta == -0.450 * "," ~
      plain(SE) == 0.112 * "," ~
      italic(t)(1617) == -4.21 * "," ~
      italic(p) < .001 * "," ~
      eta[p]^2 == .010),
    color = "Base Frequency",
    fill = "Base Frequency",
    linetype = "Base Frequency"
  ) +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  scale_linetype_manual(values = my_linetypes_1) +
  my_theme +
  my_guides)

```

```{r plot_n250_words_bf_LP, echo=FALSE,  include=FALSE}
library(ggeffects)
library(ggplot2)

# Predicted values across the observed range of LP
# pred <- ggpredict(
#   m_w_N250_bf,
#   terms = c("LP", "base_frequency")
# )

(pred_BF_LP <- ggemmeans(
  m_w_N250_bf,
  terms = c(
    "LP [all]",
    "base_frequency"
  )))

(BFxLP_n250 <- ggplot(pred_BF_LP,
       aes(x = x,
           y = predicted,
           color = group,
           fill = group,
           linetype = group)) +
  geom_line(size = 1.5) +
  geom_ribbon(aes(ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              colour = NA) +
  labs(
    x = "Language Proficiency (LP)",
    y = "Predicted N250 amplitude (µV)",
    title = expression(
      beta == 0.173 * "," ~
      plain(SE) == 0.081 * "," ~
      italic(t)(1618) == 2.125 * "," ~
      italic(p) < 0.034 * "," ~
      eta[p]^2 == .0),
    color = "Base Frequency",
    fill = "Base Frequency",
    linetype = "Base Frequency"
  ) +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  scale_linetype_manual(values = my_linetypes_1) +
  my_theme +
  my_guides)
```

```{r plots_n250_words_bf_OS_LP, echo=FALSE, fig.height=3, fig.width=5}
row1 <- plot_grid(BFxOS_n250,BFxLP_n250,ncol = 2)

plot_grid(
  ggdraw() + draw_label("N250 Word Data", fontface = "bold"),
  row1,
  ncol = 1,
  rel_heights = c(0.08, 1)
)
```



\newpage



## N250 WORD DATA: FAMILY SIZE

### Model


Model Comparison

```{r anova_n250_words_fs_max}
contrasts(erp_fs_w$family_size) <- c(-0.5, 0.5)


# Model with the two individual-difference interactions with family size
m_base_fs <- lmer(
  value ~ family_size * OS +
          family_size * LP +
          (1 | SubjID) +
          (1 | SubjID:chlabel),
  data = subset(erp_fs_w, time_window == "N250"),
  REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

# Add OS × LP
m_2way_fs <- update(
  m_base_fs,
  . ~ . + OS:LP
)

# Add the three-way interaction
m_3way_fs <- update(
  m_2way_fs,
  . ~ . + family_size:OS:LP
)

anova(m_base_fs, m_2way_fs, m_3way_fs)

summary(m_3way_fs)

```

```{r anova_n250_words_fs}
contrasts(erp_fs_w$family_size) <- c(-0.5, 0.5)


m_w_N250_fs <- lmer(
  value ~ family_size * OS * LP +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_fs_w, time_window == "N250"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_w_N250_fs)

# Effect sizes for individual terms
eta_squared(m_w_N250_fs, partial = TRUE)

# Model R²
r2_nakagawa(m_w_N250_fs)
```

#### Means and Contrasts

```{r means_n250_words_fs_OS}
# family size
as.tibble(emmeans(m_w_N250_fs, ~ family_size)) |> print()

emm_fs_OS <- emmeans(m_w_N250_fs,
                      ~ family_size | OS,
                      at = list(OS = c(-1.9, -1, 0, 1, 1.9)),
                     lmerTest.limit = 6480)

emm_part <- summary(emm_fs_OS) |>
  as.data.frame() |>
  transmute(OS, Effect = paste("EMM:", family_size), Estimate = emmean, SE, df, 
            lower.CL, upper.CL, t.ratio = NA_real_, p.value = NA_real_)

contrast_part <- pairs(emm_fs_OS) |>
  summary() |>
  as.data.frame() |>
  transmute(OS,Effect = paste("Contrast:", contrast), Estimate = estimate, SE, df,
            lower.CL = NA_real_, upper.CL = NA_real_, t.ratio, p.value)

emm_contrast_table <- bind_rows(emm_part, contrast_part) |>
  arrange(OS, Effect)|>
  mutate(
    Estimate = round(Estimate, 2),
    SE       = round(SE, 2),
    df       = round(df, 1),
    lower.CL = round(lower.CL, 2),
    upper.CL = round(upper.CL, 2),
    t.ratio  = round(t.ratio, 2),
    p.value  = round(p.value, 3)
  )

as.tibble(emm_contrast_table, digits = 3) |> print(n = 20)
```

```{r means_n250_words_fs_LP}
# family size
as.tibble(emmeans(m_w_N250_fs, ~ family_size)) |> print()

emm_fs_LP <- emmeans(m_w_N250_fs,
                      ~ family_size | LP,
                      at = list(LP = c(-2.5, -1, 0, 1, 3.0)),
                     lmerTest.limit = 6480)

emm_part <- summary(emm_fs_LP) |>
  as.data.frame() |>
  transmute(LP, Effect = paste("EMM:", family_size), Estimate = emmean, SE, df, 
            lower.CL, upper.CL, t.ratio = NA_real_, p.value = NA_real_)

contrast_part <- pairs(emm_fs_LP) |>
  summary() |>
  as.data.frame() |>
  transmute(LP,Effect = paste("Contrast:", contrast), Estimate = estimate, SE, df,
            lower.CL = NA_real_, upper.CL = NA_real_, t.ratio, p.value)

emm_contrast_table <- bind_rows(emm_part, contrast_part) |>
  arrange(LP, Effect)|>
  mutate(
    Estimate = round(Estimate, 2),
    SE       = round(SE, 2),
    df       = round(df, 1),
    lower.CL = round(lower.CL, 2),
    upper.CL = round(upper.CL, 2),
    t.ratio  = round(t.ratio, 2),
    p.value  = round(p.value, 3)
  )

as.tibble(emm_contrast_table, digits = 3) |> print(n = 20)
```

3-way Means and Contrasts

```{r}
library(emmeans)
emm_options(lmer.df = "satterthwaite")

# Family Size three-way follow-up: FS simple effect at Low/Mean/High OS x Low/Mean/High LP
# Representative values: mean and ±1 SD for each continuous IV
os_vals_fs <- c(mean(erp_fs_w$OS) - sd(erp_fs_w$OS), mean(erp_fs_w$OS), mean(erp_fs_w$OS) + sd(erp_fs_w$OS))
lp_vals_fs <- c(mean(erp_fs_w$LP) - sd(erp_fs_w$LP), mean(erp_fs_w$LP), mean(erp_fs_w$LP) + sd(erp_fs_w$LP))


emm_fs <- emmeans(m_3way_fs, ~ family_size | OS * LP,
                   at = list(OS = os_vals_fs, LP = lp_vals_fs))
fs_followup <- contrast(emm_fs, method = "revpairwise", by = c("OS", "LP"))
summary(fs_followup, infer = c(TRUE, TRUE))

```

```{r}
# To examine LP slopes across selected OS values:
LP_3way_trends_fs <- compact_3way_trends_table(
  model = m_w_N250_fs,
  focal_var = LP,
  moderator_var = OS,
  condition_var = family_size,
  moderator_values = c(-1.9, -1.5, -1, 0, 1, 1.5, 1.9),
  condition_prefix = "BF",
  lmerTest.limit = 6480
)

as.tibble(LP_3way_trends_fs) |>
  print(n = 50)

# To examine OS slopes across selected LP values:

OS_3way_trends_fs <- compact_3way_trends_table(
  model = m_w_N250_fs,
  focal_var = OS,
  moderator_var = LP,
  condition_var = family_size,
  moderator_values = c(-2.5, -1.5, -1, 0, 1, 1.5, 3),
  condition_prefix = "BF",
  lmerTest.limit = 6480
)

as.tibble(OS_3way_trends_fs) |>
  print(n = 50)
```



#### Plots

```{r plot_n250_words_fs_OS,  echo=FALSE, include=FALSE }
library(ggeffects)
library(ggplot2)

# Predicted values across the observed range of OS
# pred <- ggpredict(
#   m_w_N250_fs,
#   terms = c("OS", "family_size")
# )

(pred_FS_OS <- ggemmeans(
  m_w_N250_fs,
  terms = c(
    "OS [all]",
    "family_size"
  )))

(FSxOS_n250 <- ggplot(pred_FS_OS,
       aes(x = x,
           y = predicted,
           color = group,
           fill = group,
           linetype = group)) +
  geom_line(size = 1.5) +
  geom_ribbon(aes(ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              colour = NA,
              linetype = 0) +
  labs(
    x = "Orthographic Sensitivity (OS)",
    y = "Predicted N250 amplitude (µV)",
    title = expression(
      beta == 0.110 * "," ~
      plain(SE) == 0.065 * "," ~
      italic(t)(1617) == 1.67 * "," ~
      italic(p) < .095),
    color = "Family Size",
    fill = "Family Size",
    linetype = "Family Size") +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  scale_linetype_manual(values = my_linetypes_1) +
  my_theme +
  my_guides)

```

```{r plot_n250_words_fs_LP, echo=FALSE, , include=FALSE }

(pred_FS_LP <- ggemmeans(
  m_w_N250_fs,
  terms = c(
    "LP [all]",
    "family_size"
  )))

(FSxLP_n250 <- ggplot(pred_FS_LP,
       aes(x = x,
           y = predicted,
           color = group,
           fill = group,
           linetype = group)) +
  geom_line(size = 1.5) +
  geom_ribbon(aes(ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              colour = NA,
              linetype = 0) +
  labs(
    x = "Language Proficiency (LP)",
    y = "Predicted N250 voltage (µV)",
    title = expression(
      beta == -0.072 * "," ~
      plain(SE) == 0.047 * "," ~
      italic(t)(1617) == -1.53 * "," ~
      italic(p) < .127),
    color = "Family Size",
    fill = "Family Size",
    linetype = "Family Size") +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  scale_linetype_manual(values = my_linetypes_1) +
  my_theme +
  my_guides)

```


```{r plot_n250_words_fs_OS_LP, echo=FALSE, fig.height=3, fig.width=5}
row1 <- plot_grid(FSxOS_n250,FSxLP_n250,ncol = 2)

plot_grid(
  ggdraw() + draw_label("N250 Word Data", fontface = "bold"),
  row1,
  ncol = 1,
  rel_heights = c(0.08, 1)
)
```

# MODEL ROBUSTNESS CHECKS

## BASE FREQUENCY

```{r}
# Continuous slope-of-slope: how does the OS effect on BF change across a fine LP grid?
lp_grid <- seq(min(erp_bf_w$LP), max(erp_bf_w$LP), length.out = 20)
emm_bf_grid <- emmeans(m_3way_bf, ~ base_frequency | OS * LP,
                        at = list(OS = c(-1, 0, 1), LP = lp_grid))
bf_grid_followup <- contrast(emm_bf_grid, method = "revpairwise", by = c("OS", "LP"))
as.data.frame(summary(bf_grid_followup))
```


```{r}
# quick check of how populated the tails are
erp_bf_w |>
  distinct(SubjID, OS, LP) |>
  summarise(
    n_total = n(),
    n_OS_extreme = sum(abs(OS) > 1.5),
    n_LP_extreme = sum(abs(LP) > 1.5)
  )
```

```{r}
# Joint corner populations
erp_bf_w |>
  distinct(SubjID, OS, LP) |>
  summarise(
    n_low_OS_high_LP  = sum(OS < -0.85 & LP > 1.28),
    n_high_OS_low_LP  = sum(OS >  0.93 & LP < -0.85),
    n_total = n()
  )

# And: where do the SD-based grid endpoints actually fall relative to the data?
# (LP = 3.11 in the grid was the sample max — how many SDs out is that?)
erp_bf_w |>
  distinct(SubjID, LP) |>
  summarise(LP_mean = mean(LP), LP_sd = sd(LP), LP_max = max(LP), LP_max_in_SD = (max(LP) - mean(LP)) / sd(LP))
```

```{r}
# Identify the participant(s) driving the LP tail
extreme_ids <- erp_bf_w |>
  distinct(SubjID, LP) |>
  filter(LP > 2) |>
  pull(SubjID)

# Refit excluding them
m_3way_bf_robust <- update(m_3way_bf, data = subset(erp_bf_w, time_window == "N250" & !SubjID %in% extreme_ids))
summary(m_3way_bf_robust)
```

## FAMILY SIZE

```{r}
# Confirm which participant(s) are in the LP tail for the family size dataset
extreme_ids_fs <- erp_fs_w |>
  distinct(SubjID, LP) |>
  filter(LP > 2) |>
  pull(SubjID)

extreme_ids_fs  # check this matches extreme_ids from the BF check

# Refit excluding them
m_3way_fs_robust <- update(m_3way_fs, data = subset(erp_fs_w, time_window == "N250" & !SubjID %in% extreme_ids_fs))
summary(m_3way_fs_robust)
```

