---
title: "M21 2026 July 2026 N400 Component WORDS"
author: "Joanna Morris"
date: "`r Sys.Date()`"
output: 
  bookdown::pdf_document2:
    toc: true
    toc_depth: 4
    number_sections: true
header-includes:
  - \setcounter{secnumdepth}{3}
editor_options: 
  chunk_output_type: inline
---

\scriptsize

# Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE, 
                      error = FALSE,
                      comment = "||",
                      fig.height = 4,
                      fig.width = 7)
options(width = 150)
```

Load libraries

```{r load_libraries, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
library(tidyverse)
library(ggeffects)
library(lme4)
library(afex)
library(gridExtra)
library(MuMIn)
library(pbkrtest)
library(effectsize)
library(performance)
library(cowplot)  # for use with `plot_grid(x,x,ncol = x)` function
library(e1071) # for use with `skewness()` function
library(lmerTest)
library(emmeans)
# emm_options(lmer.df = "satterthwaite")
```

## Set emmeans options {-}

```{r emmeans_options, include=FALSE}
emm_options(
  lmer.df = "kenward-roger",
  pbkrtest.limit = 10000,
  disable.pbkrtest = FALSE
)
```

## Set ggplot parameters {-}

```{r ggplot_parameters, include=FALSE}
# Color palette
my_palette_1 <- c(
  "#E31A1C",   # red
  "#1F78B4"  # blue
)

my_palette_2 <- c(
  "#0072B2",  # dark blue
  "#E69F00"   # orange/gold
)
my_linetypes_1 <- c("dashed", "solid")

# Theme
my_theme <- theme_classic(base_size = 8) +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal",
    legend.box = "horizontal"
  )

# Common guides
my_guides <- guides(
  colour = guide_legend(nrow = 1),
  fill   = guide_legend(nrow = 1)
)

```

## Define Functions 

### Two-way interaction table function {-}

Function use for Complexity × LP table:

``` 
emm_complexity_LP_N400 <- emmeans(m_nw_N400_fs, ~ complexity | LP, at = list(LP = c(-1, 0, 1)))
compact_emm_table(emm_complexity_LP_N400, by_var = LP, condition_prefix = "LP")
```

for Family Size × LP table:

```
emm_FS_LP_N400 <- emmeans(m_nw_N400_fs,  ~ family_size | LP, at = list(LP = c(-1, 0, 1)))
compact_emm_table(emm_FS_LP_N400,  by_var = LP, condition_prefix = "LP")
```

```{r interaction_table_function.2way, include=FALSE}
compact_emm_table <- function(emm_object,
                              by_var,
                              condition_prefix = NULL,
                              digits_est = 2,
                              digits_df = 1,
                              digits_p = 3) {
  
  by_var_name <- rlang::as_name(rlang::ensym(by_var))
  
  emm_df <- summary(emm_object) |>
    as.data.frame()
  
  contrast_df <- pairs(emm_object) |>
    summary() |>
    as.data.frame()
  
  # Focal factor columns are the EMM columns other than the conditioning variable
  focal_vars <- setdiff(
    names(emm_df),
    c(by_var_name, "emmean", "SE", "df", "lower.CL", "upper.CL")
  )
  
  emm_part <- emm_df |>
    rowwise() |>
    mutate(
      Comparison = paste(c_across(all_of(focal_vars)), collapse = " "),
      Condition = if (is.null(condition_prefix)) {
        as.character(.data[[by_var_name]])
      } else {
        paste(condition_prefix, "=", .data[[by_var_name]])
      }
    ) |>
    ungroup() |>
    transmute(
      Comparison,
      Condition,
      Estimate = emmean,
      SE,
      df,
      lower.CL,
      upper.CL,
      t.ratio = NA_real_,
      p.value = NA_real_
    )
  
  contrast_part <- contrast_df |>
    mutate(
      Comparison = contrast,
      Condition = if (is.null(condition_prefix)) {
        as.character(.data[[by_var_name]])
      } else {
        paste(condition_prefix, "=", .data[[by_var_name]])
      }
    ) |>
    transmute(
      Comparison,
      Condition,
      Estimate = estimate,
      SE,
      df,
      lower.CL = NA_real_,
      upper.CL = NA_real_,
      t.ratio,
      p.value
    )
  
  bind_rows(emm_part, contrast_part) |>
    arrange(Condition, Comparison) |>
    mutate(
      Estimate = round(Estimate, digits_est),
      SE       = round(SE, digits_est),
      df       = round(df, digits_df),
      lower.CL = round(lower.CL, digits_est),
      upper.CL = round(upper.CL, digits_est),
      t.ratio  = round(t.ratio, digits_est),
      p.value  = round(p.value, digits_p)
    )
}
```


### Three-way interaction table function {-}

```
emm_3way <- emmeans(m_nw_N400_fs, ~ complexity * family_size | LP, at = list(LP = c(-1, 0, 1)))
compact_3way_table(emm_3way, by_var = LP, condition_prefix = "LP",  factor1 = complexity,  factor2 = family_size)
```

```{r interaction_table_function.3way, include=FALSE}
compact_3way_table <- function(emm_object,
                               by_var,
                               condition_prefix = NULL,
                               factor1,
                               factor2,
                               digits_est = 2,
                               digits_df = 1,
                               digits_p = 3) {
  
  by_var_name <- rlang::as_name(rlang::ensym(by_var))
  factor1_name <- rlang::as_name(rlang::ensym(factor1))
  factor2_name <- rlang::as_name(rlang::ensym(factor2))
  
  emm_df <- summary(emm_object) |>
    as.data.frame()
  
  make_condition <- function(x) {
    if (is.null(condition_prefix)) {
      as.character(x[[by_var_name]])
    } else {
      paste(condition_prefix, "=", x[[by_var_name]])
    }
  }
  
  emm_part <- emm_df |>
    mutate(
      Comparison = paste(.data[[factor1_name]], .data[[factor2_name]]),
      Condition = make_condition(pick(everything()))
    ) |>
    transmute(
      Comparison,
      Condition,
      Estimate = emmean,
      SE,
      df,
      lower.CL,
      upper.CL,
      t.ratio = NA_real_,
      p.value = NA_real_
    )
  
  factor1_part <- pairs(emm_object, simple = factor1_name) |>
    summary() |>
    as.data.frame() |>
    mutate(
      Comparison = contrast,
      Condition = paste(
        if (is.null(condition_prefix)) .data[[by_var_name]] else paste(condition_prefix, "=", .data[[by_var_name]]),
        "|",
        factor2_name, "=",
        .data[[factor2_name]]
      )
    ) |>
    transmute(
      Comparison,
      Condition,
      Estimate = estimate,
      SE,
      df,
      lower.CL = NA_real_,
      upper.CL = NA_real_,
      t.ratio,
      p.value
    )
  
  factor2_part <- pairs(emm_object, simple = factor2_name) |>
    summary() |>
    as.data.frame() |>
    mutate(
      Comparison = contrast,
      Condition = paste(
        if (is.null(condition_prefix)) .data[[by_var_name]] else paste(condition_prefix, "=", .data[[by_var_name]]),
        "|",
        factor1_name, "=",
        .data[[factor1_name]]
      )
    ) |>
    transmute(
      Comparison,
      Condition,
      Estimate = estimate,
      SE,
      df,
      lower.CL = NA_real_,
      upper.CL = NA_real_,
      t.ratio,
      p.value
    )
  
  interaction_part <- contrast(
  emm_object,
  interaction = c("pairwise", "pairwise")
) |>
  summary() |>
  as.data.frame() |>
  mutate(
    Comparison = paste0(
      "Int: ",
      .data[[paste0(factor1_name, "_pairwise")]],
      " across ",
      .data[[paste0(factor2_name, "_pairwise")]]
    ),
    Condition = make_condition(cur_data())
  ) |>
  transmute(
    Comparison,
    Condition,
    Estimate = estimate,
    SE,
    df,
    lower.CL = NA_real_,
    upper.CL = NA_real_,
    t.ratio,
    p.value
  )
  
  bind_rows(
    emm_part         |> mutate(RowType = 1),
    factor1_part     |> mutate(RowType = 2),
    factor2_part     |> mutate(RowType = 2),
    interaction_part |> mutate(RowType = 3)
  ) |>
    arrange(Condition, RowType, Comparison) |>
    mutate(
      Estimate = round(Estimate, digits_est),
      SE       = round(SE, digits_est),
      df       = round(df, digits_df),
      lower.CL = round(lower.CL, digits_est),
      upper.CL = round(upper.CL, digits_est),
      t.ratio  = round(t.ratio, digits_est),
      p.value  = round(p.value, digits_p)
    ) |>
    select(-RowType)
}
```


# Load Files

```{r load_files, message=FALSE, warning=FALSE}

# Load data: rt words

# rt_w <- read_csv("rt_words_frq.csv") |>
#   filter(correct == 1) |>
#   mutate(
#     SubjID = factor(SubjID),
#     Item   = factor(target),
#     logRT  = log(response_time),
#     OS     = as.numeric(Dim.2),
#     LP     = as.numeric(Dim.1),
#     zLogBF = as.numeric(scale(LogBF)),
#     zLogFS = as.numeric(scale(LogFS))
#   )

# Load data: rt nonwords

# rt_nw <- read_csv("rt_nwords_frq.csv") |>
#   filter(correct == 1) |>
#   mutate(
#     SubjID = factor(SubjID),
#     ItemID = factor(ItemID),
#     complexity = factor(complexity,
#                     levels = c("SIMP", "COMP"),
#                     labels = c("Simple", "Complex")),
#     logRT  = log(response_time),
#     OS     = as.numeric(Dim.2),
#     LP     = as.numeric(Dim.1),
#     zLogBF = as.numeric(scale(LogBF)),
#     zLogFS = as.numeric(scale(LogFS))
#   )

# Load data: erp_fs words
erp_fs_w <- read_csv("erp_fs_dmg_words.csv") |>
  mutate(
    SubjID = factor(SubjID),
    chlabel = factor(chlabel),
    family_size = factor(family_size, 
                         levels = c("Small", "Large")),
    time_window = factor(time_window),
    OS = as.numeric(Dim.2),
    LP = as.numeric(Dim.1)
  )

# Load data: erp_fs nonwords
# erp_fs_nw <- read_csv("erp_fs_dmg_nonwords.csv") |>
#   mutate(
#     SubjID = factor(SubjID),
#     chlabel = factor(chlabel),
#     family_size = factor(family_size, 
#                          levels = c("Small", "Large")),
#     complexity = factor(complexity,
#                     labels = c("Simple", "Complex")),
#     time_window = factor(time_window),
#     OS = as.numeric(Dim.2),
#     LP = as.numeric(Dim.1)
#   )

# Load data: erp_bf words
erp_bf_w <- read_csv("erp_bf_dmg_words.csv") |>
  mutate(
    SubjID = factor(SubjID),
    chlabel = factor(chlabel),
    base_frequency = factor(base_frequency, 
                            levels = c("Low", "High")),
    time_window = factor(time_window),
    OS = as.numeric(Dim.2),
    LP = as.numeric(Dim.1)
  )

# Load data: erp_bf nonwords
# erp_bf_nw <- read_csv("erp_bf_dmg_nonwords.csv") |>
#   mutate(
#     SubjID = factor(SubjID),
#     chlabel = factor(chlabel),
#     base_frequency = factor(base_frequency, 
#                             levels = c("Low", "High")),
#     complexity = factor(complexity,
#                     labels = c("Simple", "Complex")),
#     time_window = factor(time_window),
#     OS = as.numeric(Dim.2),
#     LP = as.numeric(Dim.1)
#   )
```



```{r}
range(erp_fs_w$LP)
range(erp_fs_w$OS)
```


# N400 WORD DATA

## N400 WORD DATA: BASE FREQUENCY 

### Model



```{r}
contrasts(erp_bf_w$base_frequency) <- c(-0.5, 0.5)

# Base model: both individual-difference interactions with base frequency
m_base_bf_n400 <- lmer(
  value ~ base_frequency * OS +
    base_frequency * LP +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_bf_w, time_window == "N400"),
  REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

# Add OS × LP
m_2way_bf_n400 <- update(
  m_base_bf_n400,
  . ~ . + OS:LP
)

# Add the three-way interaction
m_3way_bf_n400 <- update(
  m_2way_bf_n400,
  . ~ . + base_frequency:OS:LP
)

anova(m_base_bf_n400, m_2way_bf_n400, m_3way_bf_n400)
summary(m_3way_bf_n400)
```

```{r}
m_3way_n400 <- lmer(value ~ complexity*OS + complexity*LP + complexity*family_size +
                             OS*LP*family_size + complexity:OS:LP +
                             complexity:OS:family_size + complexity:LP:family_size +
                             (1|SubjID) + (1|SubjID:chlabel),
                     data = subset(erp_fs_nw, time_window == "N400"),
                     REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

m_4way_n400 <- update(m_3way_n400, . ~ . + complexity:OS:LP:family_size)

anova(m_3way_n400, m_4way_n400)
```


```{r anova_N400_words_bf}
contrasts(erp_bf_w$base_frequency) <- c(-0.5, 0.5)

m_w_N400_bf <- lmer(
  value ~ base_frequency * LP  * OS +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_bf_w, time_window == "N400"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_w_N400_bf)

# Effect sizes for individual terms
eta_squared(m_w_N400_bf, partial = TRUE)

# Model R²
r2_nakagawa(m_w_N400_bf)
```

### Means and Contrasts

```{r means_N400_words_bf_LP}
as.tibble(emmeans(m_w_N400_bf, ~ base_frequency)) |> print()

emm_bf_LP <- emmeans(m_w_N400_bf,
                      ~ base_frequency | LP,
                      at = list(LP = c(-2.5, -1.5, -1, 0, 1, 1.5, 3)))

emm_part <- summary(emm_bf_LP) |>
  as.data.frame() |>
  transmute(LP, Effect = paste("EMM:", base_frequency), Estimate = emmean, SE, df, 
            lower.CL, upper.CL, t.ratio = NA_real_, p.value = NA_real_)

contrast_part <- pairs(emm_bf_LP) |>
  summary() |>
  as.data.frame() |>
  transmute(LP, Effect = paste("Contrast:", contrast), Estimate = estimate, SE, df,
            lower.CL = NA_real_, upper.CL = NA_real_, t.ratio, p.value)

emm_contrast_table_LP_N400_words <- bind_rows(emm_part, contrast_part) |>
  arrange(LP, Effect)|>
  mutate(
    Estimate = round(Estimate, 2),
    SE       = round(SE, 2),
    df       = round(df, 1),
    lower.CL = round(lower.CL, 2),
    upper.CL = round(upper.CL, 2),
    t.ratio  = round(t.ratio, 2),
    p.value  = round(p.value, 3)
  )

as.tibble(emm_contrast_table_LP_N400_words, digits = 3) |> print(n=50)
```

```{r means_N400_words_bf_OS}
as.tibble(emmeans(m_w_N400_bf, ~ base_frequency)) |> print()

emm_bf_OS <- emmeans(m_w_N400_bf,
                      ~ base_frequency | OS,
                      at = list(OS = c(-1.9, -1.5, -1, 0, 1, 1.5, 1.9)))

emm_part <- summary(emm_bf_OS) |>
  as.data.frame() |>
  transmute(OS, Effect = paste("EMM:", base_frequency), Estimate = emmean, SE, df, 
            lower.CL, upper.CL, t.ratio = NA_real_, p.value = NA_real_)

contrast_part <- pairs(emm_bf_OS) |>
  summary() |>
  as.data.frame() |>
  transmute(OS, Effect = paste("Contrast:", contrast), Estimate = estimate, SE, df,
            lower.CL = NA_real_, upper.CL = NA_real_, t.ratio, p.value)

emm_contrast_table_OS_N400_words <- bind_rows(emm_part, contrast_part) |>
  arrange(OS, Effect)|>
  mutate(
    Estimate = round(Estimate, 2),
    SE       = round(SE, 2),
    df       = round(df, 1),
    lower.CL = round(lower.CL, 2),
    upper.CL = round(upper.CL, 2),
    t.ratio  = round(t.ratio, 2),
    p.value  = round(p.value, 3)
  )

as.tibble(emm_contrast_table_OS_N400_words, digits = 3) |> print(n=50)
```

### Plots

```{r plot_N400_words_bf, include=FALSE}

# Predicted values across the observed range of LP

# pred <- ggpredict(
#   m_w_N400_bf,
#   terms = c("LP", "base_frequency")
# )

(pred_BF_LP <- ggemmeans(
  m_w_N400_bf,
  terms = c(
    "LP [all]",
    "base_frequency"
  )
))

(BFxLP_n400 <- ggplot(pred_BF_LP,
       aes(x = x,
           y = predicted,
           color = group,
           fill = group,
           linetype = group)) +
  geom_line(size = 1.2) +
  geom_ribbon(aes(ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              colour = NA) +
  labs(
    x = "Language Proficiency (LP)",
    y = "Predicted N400 amplitude (µV)",
    color = "Base Frequency",
    fill = "Base Frequency",
    linetype = "Base Frequency",
    title = expression(
      beta ==  0.344 * "," ~
      plain(SE) == 0.087 * "," ~
      italic(t)(1618) == 3.98 * "," ~
      italic(p) < .001 * "," ~
      eta[p]^2 == .010),
  )  +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  scale_linetype_manual(values = my_linetypes_1) +
  my_theme +
  my_guides)
```

## N400 WORD DATA: FAMILY SIZE 

### Model


```{r}
contrasts(erp_fs_w$family_size) <- c(-0.5, 0.5)

# Base model: both individual-difference interactions with family size
m_base_fs_n400 <- lmer(
  value ~ family_size * OS +
    family_size * LP +
    (1 | SubjID) +
    (1 | SubjID:chlabel),
  data = subset(erp_fs_w, time_window == "N400"),
  REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

# Add OS × LP
m_2way_fs_n400 <- update(
  m_base_fs_n400,
  . ~ . + OS:LP
)

# Add the three-way interaction
m_3way_fs_n400 <- update(
  m_2way_fs_n400,
  . ~ . + family_size:OS:LP
)

anova(m_base_fs_n400, m_2way_fs_n400, m_3way_fs_n400)
summary(m_3way_fs_n400)
```

```{r anova_N400_words_fs}
contrasts(erp_fs_w$family_size) <- c(-0.5, 0.5)

m_w_N400_fs <- lmer(
  value ~ family_size * OS  * LP + 
    (1 | SubjID) + 
    (1 | SubjID:chlabel),
  data = subset(erp_fs_w, time_window == "N400"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_w_N400_fs)

# Effect sizes for individual terms
eta_squared(m_w_N400_fs, partial = TRUE)

# Model R²
r2_nakagawa(m_w_N400_fs)
```

### Means

```{r means_N400_words_fs}
as.tibble(emmeans(m_w_N400_fs, ~ family_size)) |> print()
```

emmeans for plotting CIs in plot
```{r}
emm_fs_n400_by_lp <- emmeans(m_3way_fs_n400, ~ family_size | LP,
                              at = list(LP = c(-2.5, -1.5, -1, 0, 1, 1.5, 3)))
summary(emm_fs_n400_by_lp, infer = c(TRUE, FALSE))
```

### Plots (Interaction Not significant)

```{r plots_N400_words_fs, include=FALSE}
# Predicted values across the observed range of LP

# pred <- ggpredict(
#   m_w_N400_fs,
#   terms = c("LP", "family_size")
# )

(pred_FS_LP <- ggemmeans(
  m_w_N400_fs,
  terms = c(
    "LP [all]",
    "family_size"
  )
))

(FSxLP_n400 <- ggplot(pred_FS_LP,
       aes(x = x,
           y = predicted,
           color = group,
           fill = group,
           linetype = group)) +
  geom_line(size = 1.2) +
  geom_ribbon(aes(ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              colour = NA) +
  labs(
    x = "Language Proficiency (LP)",
    y = "Predicted N400 amplitude (µV)",
    title = expression(
      beta == -0.071 * "," ~
      plain(SE) == 0.052 * "," ~
      italic(t)(1618) == -1.37 * "," ~
      italic(p) < .172),
    color = "Family Size",
    fill = "Family Size",
    linetype = "Family Size"
  )  +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  scale_linetype_manual(values = my_linetypes_1) +
  my_theme +
  my_guides)
```


