---
title: "M21 2026 July 2026 N400 Component"
author: "Joanna Morris"
date: "`r Sys.Date()`"
output: 
  bookdown::pdf_document2:
    toc: true
    toc_depth: 4
    number_sections: true
header-includes:
  - \setcounter{secnumdepth}{3}
editor_options: 
  chunk_output_type: inline
---

\scriptsize

# Setup {-}
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE, 
                      error = FALSE,
                      comment = "||",
                      fig.height = 4,
                      fig.width = 7)
options(width = 150)
```

## Load libraries {-}

```{r load_libraries, echo=FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(ggeffects)
library(lme4)
library(afex)
library(gridExtra)
library(MuMIn)
library(pbkrtest)
library(effectsize)
library(performance)
library(cowplot)  # for use with `plot_grid(x,x,ncol = x)` function
library(e1071) # for use with `skewness()` function
library(lmerTest)
library(emmeans)
# emm_options(lmer.df = "satterthwaite")
```

## Set emmeans options {-}

```{r emmeans_options}
emm_options(
  lmer.df = "kenward-roger",
  pbkrtest.limit = 10000,
  disable.pbkrtest = FALSE
)
```

## Set ggplot parameters {-}

```{r ggplot_parameters}
# Color palette
my_palette_1 <- c(
  "#E31A1C",   # red
  "#1F78B4"  # blue
)

my_palette_2 <- c(
  "#0072B2",  # dark blue
  "#E69F00"   # orange/gold
)
my_linetypes_1 <- c("dashed", "solid")

# Theme
my_theme <- theme_classic(base_size = 10) +
  theme(
    legend.position = "bottom",
    legend.direction = "horizontal",
    legend.box = "horizontal"
  )

# Common guides
my_guides <- guides(
  colour = guide_legend(nrow = 1),
  fill   = guide_legend(nrow = 1)
)

```

## Define  interaction table functions {-}

```{r interaction_table_function.2way, echo=FALSE}
compact_emm_table <- function(emm_object,
                              by_var,
                              condition_prefix = NULL,
                              digits_est = 2,
                              digits_df = 1,
                              digits_p = 3) {
  
  by_var_name <- rlang::as_name(rlang::ensym(by_var))
  
  emm_df <- summary(emm_object) |>
    as.data.frame()
  
  contrast_df <- pairs(emm_object) |>
    summary() |>
    as.data.frame()
  
  # Focal factor columns are the EMM columns other than the conditioning variable
  focal_vars <- setdiff(
    names(emm_df),
    c(by_var_name, "emmean", "SE", "df", "lower.CL", "upper.CL")
  )
  
  emm_part <- emm_df |>
    rowwise() |>
    mutate(
      Comparison = paste(c_across(all_of(focal_vars)), collapse = " "),
      Condition = if (is.null(condition_prefix)) {
        as.character(.data[[by_var_name]])
      } else {
        paste(condition_prefix, "=", .data[[by_var_name]])
      }
    ) |>
    ungroup() |>
    transmute(
      Comparison,
      Condition,
      Estimate = emmean,
      SE,
      df,
      lower.CL,
      upper.CL,
      t.ratio = NA_real_,
      p.value = NA_real_
    )
  
  contrast_part <- contrast_df |>
    mutate(
      Comparison = contrast,
      Condition = if (is.null(condition_prefix)) {
        as.character(.data[[by_var_name]])
      } else {
        paste(condition_prefix, "=", .data[[by_var_name]])
      }
    ) |>
    transmute(
      Comparison,
      Condition,
      Estimate = estimate,
      SE,
      df,
      lower.CL = NA_real_,
      upper.CL = NA_real_,
      t.ratio,
      p.value
    )
  
  bind_rows(emm_part, contrast_part) |>
    arrange(Condition, Comparison) |>
    mutate(
      Estimate = round(Estimate, digits_est),
      SE       = round(SE, digits_est),
      df       = round(df, digits_df),
      lower.CL = round(lower.CL, digits_est),
      upper.CL = round(upper.CL, digits_est),
      t.ratio  = round(t.ratio, digits_est),
      p.value  = round(p.value, digits_p)
    )
}
```

```{r interaction_table_function.3way, echo=FALSE}
compact_3way_table <- function(emm_object,
                               by_var,
                               condition_prefix = NULL,
                               factor1,
                               factor2,
                               digits_est = 2,
                               digits_df = 1,
                               digits_p = 3) {
  
  by_var_name <- rlang::as_name(rlang::ensym(by_var))
  factor1_name <- rlang::as_name(rlang::ensym(factor1))
  factor2_name <- rlang::as_name(rlang::ensym(factor2))
  
  emm_df <- summary(emm_object) |>
    as.data.frame()
  
  make_condition <- function(x) {
    if (is.null(condition_prefix)) {
      as.character(x[[by_var_name]])
    } else {
      paste(condition_prefix, "=", x[[by_var_name]])
    }
  }
  
  emm_part <- emm_df |>
    mutate(
      Comparison = paste(.data[[factor1_name]], .data[[factor2_name]]),
      Condition = make_condition(cur_data())
    ) |>
    transmute(
      Comparison,
      Condition,
      Estimate = emmean,
      SE,
      df,
      lower.CL,
      upper.CL,
      t.ratio = NA_real_,
      p.value = NA_real_
    )
  
  factor1_part <- pairs(emm_object, simple = factor1_name) |>
    summary() |>
    as.data.frame() |>
    mutate(
      Comparison = contrast,
      Condition = paste(
        if (is.null(condition_prefix)) .data[[by_var_name]] else paste(condition_prefix, "=", .data[[by_var_name]]),
        "|",
        factor2_name, "=",
        .data[[factor2_name]]
      )
    ) |>
    transmute(
      Comparison,
      Condition,
      Estimate = estimate,
      SE,
      df,
      lower.CL = NA_real_,
      upper.CL = NA_real_,
      t.ratio,
      p.value
    )
  
  factor2_part <- pairs(emm_object, simple = factor2_name) |>
    summary() |>
    as.data.frame() |>
    mutate(
      Comparison = contrast,
      Condition = paste(
        if (is.null(condition_prefix)) .data[[by_var_name]] else paste(condition_prefix, "=", .data[[by_var_name]]),
        "|",
        factor1_name, "=",
        .data[[factor1_name]]
      )
    ) |>
    transmute(
      Comparison,
      Condition,
      Estimate = estimate,
      SE,
      df,
      lower.CL = NA_real_,
      upper.CL = NA_real_,
      t.ratio,
      p.value
    )
  
  interaction_part <- contrast(
  emm_object,
  interaction = c("pairwise", "pairwise")
) |>
  summary() |>
  as.data.frame() |>
  mutate(
    Comparison = paste0(
      "Int: ",
      .data[[paste0(factor1_name, "_pairwise")]],
      " across ",
      .data[[paste0(factor2_name, "_pairwise")]]
    ),
    Condition = make_condition(cur_data())
  ) |>
  transmute(
    Comparison,
    Condition,
    Estimate = estimate,
    SE,
    df,
    lower.CL = NA_real_,
    upper.CL = NA_real_,
    t.ratio,
    p.value
  )
  
  bind_rows(
    emm_part         |> mutate(RowType = 1),
    factor1_part     |> mutate(RowType = 2),
    factor2_part     |> mutate(RowType = 2),
    interaction_part |> mutate(RowType = 3)
  ) |>
    arrange(Condition, RowType, Comparison) |>
    mutate(
      Estimate = round(Estimate, digits_est),
      SE       = round(SE, digits_est),
      df       = round(df, digits_df),
      lower.CL = round(lower.CL, digits_est),
      upper.CL = round(upper.CL, digits_est),
      t.ratio  = round(t.ratio, digits_est),
      p.value  = round(p.value, digits_p)
    ) |>
    select(-RowType)
}
```

```{r interaction_trends_function.3way}
compact_3way_trends_table <- function(model,
                                      focal_var,
                                      moderator_var,
                                      condition_var,
                                      moderator_values,
                                      condition_prefix = NULL,
                                      digits_est = 2,
                                      digits_df = 1,
                                      digits_p = 3,
                                      lmerTest.limit = NULL) {
  
  library(emmeans)
  library(dplyr)
  library(rlang)

  focal_name     <- rlang::as_name(rlang::ensym(focal_var))
  moderator_name <- rlang::as_name(rlang::ensym(moderator_var))
  condition_name <- rlang::as_name(rlang::ensym(condition_var))

  # Construct emtrends formula:
  # ~ condition_var | moderator_var
  trend_formula <- as.formula(
    paste0("~ ", condition_name, " | ", moderator_name)
  )

  # Values at which the moderator is evaluated
  at_list <- setNames(
    list(moderator_values),
    moderator_name
  )

  # ------------------------------------------------------------
  # Estimate focal-variable slopes at each moderator value
  # separately for each categorical condition
  # ------------------------------------------------------------

  if (is.null(lmerTest.limit)) {

    trends <- emtrends(
      model,
      specs = trend_formula,
      var = focal_name,
      at = at_list
    )

  } else {

    trends <- emtrends(
      model,
      specs = trend_formula,
      var = focal_name,
      at = at_list,
      lmerTest.limit = lmerTest.limit
    )
  }

  trend_col <- paste0(focal_name, ".trend")

  # ------------------------------------------------------------
  # Simple slopes
  # ------------------------------------------------------------

  slope_part <- summary(
    trends,
    infer = c(TRUE, TRUE)
  ) |>
    as.data.frame() |>
    mutate(
      Comparison = paste0(
        focal_name,
        " slope: ",
        .data[[condition_name]]
      ),

      Condition = paste0(
        moderator_name,
        " = ",
        .data[[moderator_name]]
      ),

      Estimate = .data[[trend_col]],

      RowType = 1
    ) |>
    transmute(
      Comparison,
      Condition,
      ModeratorValue = .data[[moderator_name]],
      Estimate,
      SE,
      df,
      lower.CL,
      upper.CL,
      t.ratio,
      p.value,
      RowType
    )

  # ------------------------------------------------------------
  # Difference between focal-variable slopes across levels
  # of the categorical factor
  # ------------------------------------------------------------

  contrast_part <- pairs(trends) |>
    summary(
      infer = c(TRUE, TRUE)
    ) |>
    as.data.frame() |>
    mutate(
      Comparison = paste0(
        focal_name,
        " slope difference: ",
        contrast
      ),

      Condition = paste0(
        moderator_name,
        " = ",
        .data[[moderator_name]]
      ),

      RowType = 2
    ) |>
    transmute(
      Comparison,
      Condition,
      ModeratorValue = .data[[moderator_name]],
      Estimate = estimate,
      SE,
      df,
      lower.CL,
      upper.CL,
      t.ratio,
      p.value,
      RowType
    )

  # ------------------------------------------------------------
  # Combine and format
  # ------------------------------------------------------------

  bind_rows(
    slope_part,
    contrast_part
  ) |>
    arrange(
      .data$ModeratorValue,
      .data$RowType,
      .data$Comparison
  ) |>
    mutate(
      Estimate = round(Estimate, digits_est),
      SE       = round(SE, digits_est),
      df       = round(df, digits_df),
      lower.CL = round(lower.CL, digits_est),
      upper.CL = round(upper.CL, digits_est),
      t.ratio  = round(t.ratio, digits_est),
      p.value  = round(p.value, digits_p)
    ) |>
    select(-RowType, -ModeratorValue)
}
```



# Load Files

```{r load_files, message=FALSE, warning=FALSE}

# Load data: rt words

# rt_w <- read_csv("rt_words_frq.csv") |>
#   filter(correct == 1) |>
#   mutate(
#     SubjID = factor(SubjID),
#     Item   = factor(target),
#     logRT  = log(response_time),
#     OS     = as.numeric(Dim.2),
#     LP     = as.numeric(Dim.1),
#     zLogBF = as.numeric(scale(LogBF)),
#     zLogFS = as.numeric(scale(LogFS))
#   )

# Load data: rt nonwords
# rt_nw <- read_csv("rt_nwords_frq.csv") |>
#   filter(correct == 1) |>
#   mutate(
#     SubjID = factor(SubjID),
#     ItemID = factor(ItemID),
#     complexity = factor(complexity,
#                     levels = c("SIMP", "COMP"),
#                     labels = c("Simple", "Complex")),
#     logRT  = log(response_time),
#     OS     = as.numeric(Dim.2),
#     LP     = as.numeric(Dim.1),
#     zLogBF = as.numeric(scale(LogBF)),
#     zLogFS = as.numeric(scale(LogFS))
#   )

# Load data: erp_fs words
# erp_fs_w <- read_csv("erp_fs_dmg_words.csv") |>
#   mutate(
#     SubjID = factor(SubjID),
#     chlabel = factor(chlabel),
#     family_size = factor(family_size, 
#                          levels = c("Small", "Large")),
#     time_window = factor(time_window),
#     OS = as.numeric(Dim.2),
#     LP = as.numeric(Dim.1)
#   )

# Load data: erp_fs nonwords
erp_fs_nw <- read_csv("erp_fs_dmg_nonwords.csv") |>
  mutate(
    SubjID = factor(SubjID),
    chlabel = factor(chlabel),
    family_size = factor(family_size, 
                         levels = c("Small", "Large")),
    complexity = factor(complexity,
                    labels = c("Simple", "Complex")),
    time_window = factor(time_window),
    OS = as.numeric(Dim.2),
    LP = as.numeric(Dim.1)
  )

# Load data: erp_bf words
# erp_bf_w <- read_csv("erp_bf_dmg_words.csv") |>
#   mutate(
#     SubjID = factor(SubjID),
#     chlabel = factor(chlabel),
#     base_frequency = factor(base_frequency, 
#                             levels = c("Low", "High")),
#     time_window = factor(time_window),
#     OS = as.numeric(Dim.2),
#     LP = as.numeric(Dim.1)
#   )

# Load data: erp_bf nonwords
erp_bf_nw <- read_csv("erp_bf_dmg_nonwords.csv") |>
  mutate(
    SubjID = factor(SubjID),
    chlabel = factor(chlabel),
    base_frequency = factor(base_frequency, 
                            levels = c("Low", "High")),
    complexity = factor(complexity,
                    labels = c("Simple", "Complex")),
    time_window = factor(time_window),
    OS = as.numeric(Dim.2),
    LP = as.numeric(Dim.1)
  )
```



```{r}
range(erp_fs_w$LP)
range(erp_fs_w$OS)
```



# N400 NONWORD DATA : SYMMETRICAL MODEL, INTERACTION WITH LP AND OS

For the nonword N400, does the symmetric model we just ran replace the separate LP and OS models, or do all three get reported?**

The symmetric model is the cleanest solution — it tests both dimensions in the same model and provides the strongest evidence for the dissociation. The separate models are now superseded.

## N400 NONWORD DATA: Family Size

### Symmetric Model
```{r}
contrasts(erp_fs_nw$complexity) <- c(-0.5, 0.5)
contrasts(erp_fs_nw$family_size) <- c(-0.5, 0.5)

m_nw_N400_fs_symmetric <- lmer(
  value ~ complexity * family_size * LP + 
          complexity * family_size * OS +
    (1 | SubjID) + (1 | SubjID:chlabel),
  data = subset(erp_fs_nw, time_window == "N400"),
  control = lmerControl(optimizer = "bobyqa")
)

summary(m_nw_N400_fs_symmetric)

# Effect Sizes
eta_squared(m_nw_N400_fs_symmetric, partial = TRUE)

# R-squared
r2_nakagawa(m_nw_N400_fs_symmetric)
```

### Model Comparisons
```{r}
# Base model: current confirmed N400 structure, OS now fully crossed rather than covariate-only
m_base_nw_n400 <- lmer(
  value ~ complexity * family_size * LP + complexity * OS + family_size * OS +
    (1 | SubjID) + (1 | SubjID:chlabel),
  data = subset(erp_fs_nw, time_window == "N400"),
  REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

# Full four-way
m_full_nw_n400 <- lmer(
  value ~ complexity * family_size * LP * OS +
    (1 | SubjID) + (1 | SubjID:chlabel),
  data = subset(erp_fs_nw, time_window == "N400"),
  REML = FALSE,
  control = lmerControl(optimizer = "bobyqa")
)

anova(m_base_nw_n400, m_full_nw_n400)
summary(m_full_nw_n400)
```

```{r}
m_3way_n400 <- lmer(value ~ complexity*OS + complexity*LP + complexity*family_size +
                             OS*LP*family_size + complexity:OS:LP +
                             complexity:OS:family_size + complexity:LP:family_size +
                             (1|SubjID) + (1|SubjID:chlabel),
                     data = subset(erp_fs_nw, time_window == "N400"),
                     REML = FALSE, control = lmerControl(optimizer = "bobyqa"))

m_4way_n400 <- update(m_3way_n400, . ~ . + complexity:OS:LP:family_size)

anova(m_3way_n400, m_4way_n400)
```


```{r}
contrasts(erp_fs_nw$complexity)  <- c(-0.5, 0.5)
contrasts(erp_fs_nw$family_size) <- c(-0.5, 0.5)

# N400: theoretically-motivated confirmatory model per the agreed principle
# complexity crossed with each of OS, LP, family_size (affix-led/stem-led + processing cost tests)
# OS, LP, family_size fully crossed with each other (parallel individual-difference dimensions)
# No complexity four-way (already ruled out)

m_confirm_nw_n400 <- lmer(
  value ~ complexity * OS + complexity * LP + complexity * family_size +
    OS * LP * family_size +
    (1 | SubjID) + (1 | SubjID:chlabel),
  data = subset(erp_fs_nw, time_window == "N400"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_confirm_nw_n400)

# Effect Sizes
eta_squared(m_confirm_nw_n400, partial = TRUE)

# R-squared
r2_nakagawa(m_confirm_nw_n400)
```


```{r}
# Identify extreme LP participant(s) in the nonword dataset
extreme_ids_nw <- erp_fs_nw |>
  distinct(SubjID, LP) |>
  filter(LP > 2) |>
  pull(SubjID)

extreme_ids_nw  # confirm this is S153 again


# Robustness check: N400
m_confirm_nw_n400_robust <- update(
  m_confirm_nw_n400,
  data = subset(erp_fs_nw, time_window == "N400" & !SubjID %in% extreme_ids_nw)
)
summary(m_confirm_nw_n400_robust)
```

### Means and Contrasts

#### Simple-effects follow-ups for complexity:OS and complexity:LP

```{r means_n400_nonwords_fs}
## complexity
as.tibble(emmeans(m_confirm_nw_n400, ~ complexity))

## complexity x LP
emm_fs_LP <- emmeans(m_confirm_nw_n400,
                      ~ complexity | LP,
                      at = list(LP = c(-2.5, -1, 0, 1, 3.0)))

emm_part <- summary(emm_fs_LP) |>
  as.data.frame() |>
  transmute(LP, Effect = paste("EMM:", complexity), Estimate = emmean, SE, df, 
            lower.CL, upper.CL, t.ratio = NA_real_, p.value = NA_real_)

contrast_part <- pairs(emm_fs_LP) |>
  summary() |>
  as.data.frame() |>
  transmute(LP, Effect = paste("Contrast:", contrast), Estimate = estimate, SE, df,
            lower.CL = NA_real_, upper.CL = NA_real_, t.ratio, p.value)

emm_contrast_table_fs_LP <- bind_rows(emm_part, contrast_part) |>
  arrange(LP, Effect)|>
  mutate(
    Estimate = round(Estimate, 2),
    SE       = round(SE, 2),
    df       = round(df, 1),
    lower.CL = round(lower.CL, 2),
    upper.CL = round(upper.CL, 2),
    t.ratio  = round(t.ratio, 2),
    p.value  = round(p.value, 3)
  )
# Force RStudio to show more rows inline by using the as.tibble() function
as_tibble(emm_contrast_table_fs_LP) |> print(n = 50)

## complexity x OS
emm_fs_OS <- emmeans(m_confirm_nw_n400,
                      ~ complexity | OS,
                      at = list(OS = c(-1.9, -1, 0, 1, 1.9)))

emm_part <- summary(emm_fs_OS) |>
  as.data.frame() |>
  transmute(OS, Effect = paste("EMM:", complexity), Estimate = emmean, SE, df, 
            lower.CL, upper.CL, t.ratio = NA_real_, p.value = NA_real_)

contrast_part <- pairs(emm_fs_OS) |>
  summary() |>
  as.data.frame() |>
  transmute(OS, Effect = paste("Contrast:", contrast), Estimate = estimate, SE, df,
            lower.CL = NA_real_, upper.CL = NA_real_, t.ratio, p.value)

emm_contrast_table_fs_OS <- bind_rows(emm_part, contrast_part) |>
  arrange(OS, Effect)|>       # sorts rows in the combined table, first by column "OS", then by "Effect"
  mutate(
    Estimate = round(Estimate, 2),
    SE       = round(SE, 2),
    df       = round(df, 1),
    lower.CL = round(lower.CL, 2),
    upper.CL = round(upper.CL, 2),
    t.ratio  = round(t.ratio, 2),
    p.value  = round(p.value, 3)
  )
# Force RStudio to show more rows inline by using as.tibble()
as_tibble(emm_contrast_table_fs_OS) |> print(n = 50)
```

#### Simple-effects breakdown of `complexity:family_size` and `LP:family_size` and `OS: family_size`:

```{r}
## complexity x family_size
emm_complexity_fs_N400 <- emmeans(
  m_confirm_nw_n400,
  ~ complexity | family_size,
  lmerTest.limit = 6480)

complexityxfamilysize_table <- as.tibble(compact_emm_table(
  emm_complexity_fs_N400,
  by_var = family_size
)) |> print()


## family_size x LP
emm_fs_LP <- emmeans(m_confirm_nw_n400,
                      ~ family_size | LP,
                      at = list(LP = c(-2.5, -1.5, -1, 0, 1, 1.5, 1.9)))

emm_part <- summary(emm_fs_LP) |>
  as.data.frame() |>
  transmute(LP, Effect = paste("EMM:", family_size), Estimate = emmean, SE, df, 
            lower.CL, upper.CL, t.ratio = NA_real_, p.value = NA_real_)

contrast_part <- pairs(emm_fs_LP) |>
  summary() |>
  as.data.frame() |>
  transmute(LP, Effect = paste("Contrast:", contrast), Estimate = estimate, SE, df,
            lower.CL = NA_real_, upper.CL = NA_real_, t.ratio, p.value)

emm_contrast_table_fs_LP <- bind_rows(emm_part, contrast_part) |>
  arrange(LP, Effect)|>       # sorts rows in the combined table, first by column "LP", then by "Effect"
  mutate(
    Estimate = round(Estimate, 2),
    SE       = round(SE, 2),
    df       = round(df, 1),
    lower.CL = round(lower.CL, 2),
    upper.CL = round(upper.CL, 2),
    t.ratio  = round(t.ratio, 2),
    p.value  = round(p.value, 3)
  )
# Force RStudio to show more rows inline by using as.tibble()
as_tibble(emm_contrast_table_fs_LP) |> print(n = 50)


## family_size x OS
emm_fs_OS <- emmeans(m_confirm_nw_n400,
                      ~ family_size | OS,
                      at = list(OS = c(-1.9, -1.5, -1, 0, 1, 1.5, 1.9)))

emm_part <- summary(emm_fs_OS) |>
  as.data.frame() |>
  transmute(OS, Effect = paste("EMM:", family_size), Estimate = emmean, SE, df, 
            lower.CL, upper.CL, t.ratio = NA_real_, p.value = NA_real_)

contrast_part <- pairs(emm_fs_OS) |>
  summary() |>
  as.data.frame() |>
  transmute(OS, Effect = paste("Contrast:", contrast), Estimate = estimate, SE, df,
            lower.CL = NA_real_, upper.CL = NA_real_, t.ratio, p.value)

emm_contrast_table_fs_OS <- bind_rows(emm_part, contrast_part) |>
  arrange(OS, Effect)|>       # sorts rows in the combined table, first by column "OS", then by "Effect"
  mutate(
    Estimate = round(Estimate, 2),
    SE       = round(SE, 2),
    df       = round(df, 1),
    lower.CL = round(lower.CL, 2),
    upper.CL = round(upper.CL, 2),
    t.ratio  = round(t.ratio, 2),
    p.value  = round(p.value, 3)
  )
# Force RStudio to show more rows inline by using as.tibble()
as_tibble(emm_contrast_table_fs_OS) |> print(n = 50)


```


#### Follow-up decomposition of OS:LP:family_size (by-OS and by-LP tables, same structure as the N250 crossover)

```{r}
# To examine LP slopes across selected OS values:
LP_3way_trends_fs_n400 <- compact_3way_trends_table(
  model = m_confirm_nw_n400,
  focal_var = LP,
  moderator_var = OS,
  condition_var = family_size,
  moderator_values = c(-1.9, -1.5, -1, 0, 1, 1.5, 1.9),
  condition_prefix = "FS",
  lmerTest.limit = 6480
)

as.tibble(LP_3way_trends_fs_n400) |>
  print(n = 50)

# To examine OS slopes across selected LP values:

OS_3way_trends_fs_n400 <- compact_3way_trends_table(
  model = m_confirm_nw_n400,
  focal_var = OS,
  moderator_var = LP,
  condition_var = family_size,
  moderator_values = c(-2.5, -1.5, -1, 0, 1, 1.5, 3),
  condition_prefix = "FS",
  lmerTest.limit = 6480
)

as.tibble(OS_3way_trends_fs_n400) |>
  print(n = 50)
```

### Model BASE FREQUENCY

```{r}
contrasts(erp_bf_nw$complexity)      <- c(-0.5, 0.5)
contrasts(erp_bf_nw$base_frequency)  <- c(-0.5, 0.5)

# N400 nonwords: specificity check for base frequency, matching the family_size
# confirmatory structure so it's a fair parallel test
m_confirm_nw_n400_bf <- lmer(
  value ~ complexity * OS + complexity * LP + complexity * base_frequency +
    OS * LP * base_frequency +
    (1 | SubjID) + (1 | SubjID:chlabel),
  data = subset(erp_bf_nw, time_window == "N400"),
  control = lmerControl(optimizer = "bobyqa")
)
summary(m_confirm_nw_n400_bf)

# Effect Sizes
eta_squared(m_confirm_nw_n400_bf, partial = TRUE)

# R-squared
r2_nakagawa(m_confirm_nw_n400_bf)

```

#### Simple-effects breakdown of `LP:base_frequency` and `OS: base_frequency`:

```{r}

## base_frequency x LP
emm_bf_LP <- emmeans(m_confirm_nw_n400_bf,
                      ~ base_frequency | LP,
                      at = list(LP = c(-2.5, -1.5, -1, 0, 1, 1.5, 1.9)))

emm_part <- summary(emm_bf_LP) |>
  as.data.frame() |>
  transmute(LP, Effect = paste("EMM:", base_frequency), Estimate = emmean, SE, df, 
            lower.CL, upper.CL, t.ratio = NA_real_, p.value = NA_real_)

contrast_part <- pairs(emm_bf_LP) |>
  summary() |>
  as.data.frame() |>
  transmute(LP, Effect = paste("Contrast:", contrast), Estimate = estimate, SE, df,
            lower.CL = NA_real_, upper.CL = NA_real_, t.ratio, p.value)

emm_contrast_table_bf_LP <- bind_rows(emm_part, contrast_part) |>
  arrange(LP, Effect)|>       # sorts rows in the combined table, first by column "LP", then by "Effect"
  mutate(
    Estimate = round(Estimate, 2),
    SE       = round(SE, 2),
    df       = round(df, 1),
    lower.CL = round(lower.CL, 2),
    upper.CL = round(upper.CL, 2),
    t.ratio  = round(t.ratio, 2),
    p.value  = round(p.value, 3)
  )
# Force RStudio to show more rows inline by using as.tibble()
as_tibble(emm_contrast_table_bf_LP) |> print(n = 50)


## base_frequency x OS
emm_bf_OS <- emmeans(m_confirm_nw_n400_bf,
                      ~ base_frequency | OS,
                      at = list(OS = c(-1.9, -1.5, -1, 0, 1, 1.5, 1.9)))

emm_part <- summary(emm_bf_OS) |>
  as.data.frame() |>
  transmute(OS, Effect = paste("EMM:", base_frequency), Estimate = emmean, SE, df, 
            lower.CL, upper.CL, t.ratio = NA_real_, p.value = NA_real_)

contrast_part <- pairs(emm_bf_OS) |>
  summary() |>
  as.data.frame() |>
  transmute(OS, Effect = paste("Contrast:", contrast), Estimate = estimate, SE, df,
            lower.CL = NA_real_, upper.CL = NA_real_, t.ratio, p.value)

emm_contrast_table_bf_OS <- bind_rows(emm_part, contrast_part) |>
  arrange(OS, Effect)|>       # sorts rows in the combined table, first by column "OS", then by "Effect"
  mutate(
    Estimate = round(Estimate, 2),
    SE       = round(SE, 2),
    df       = round(df, 1),
    lower.CL = round(lower.CL, 2),
    upper.CL = round(upper.CL, 2),
    t.ratio  = round(t.ratio, 2),
    p.value  = round(p.value, 3)
  )
# Force RStudio to show more rows inline by using as.tibble()
as_tibble(emm_contrast_table_bf_OS) |> print(n = 50)


```

#### Follow-up decomposition of OS:LP:base_frequency (by-OS and by-LP tables, same structure as the N250 crossover)


```{r}
# To examine LP slopes across selected OS values:
LP_3way_trends_bf_n400 <- compact_3way_trends_table(
  model = m_confirm_nw_n400_bf,
  focal_var = LP,
  moderator_var = OS,
  condition_var = base_frequency,
  moderator_values = c(-1.9, -1.5, -1, 0, 1, 1.5, 1.9),
  condition_prefix = "BF",
  lmerTest.limit = 6480
)

as.tibble(LP_3way_trends_bf_n400) |>
  print(n = 50)

# To examine OS slopes across selected LP values:

OS_3way_trends_bf_n400 <- compact_3way_trends_table(
  model = m_confirm_nw_n400_bf,
  focal_var = OS,
  moderator_var = LP,
  condition_var = base_frequency,
  moderator_values = c(-2.5, -1.5, -1, 0, 1, 1.5, 3),
  condition_prefix = "BF",
  lmerTest.limit = 6480
)

as.tibble(OS_3way_trends_bf_n400) |>
  print(n = 50)
```


## PLOTS

`transmute()` creates a new data frame containing only the specified computations.
` factor()` is used to encode a vector as a factor 

```{r include=FALSE}
# Retain only the four condition means, excluding difference scores
complexityxfamilysize_means <- complexityxfamilysize_table |>
  filter(!grepl(" - ", Comparison)) |>
    transmute(complexity = factor( Comparison,levels = c("Simple", "Complex")),
              family_size = factor(Condition,levels = c("Small", "Large")),
              Estimate,
              lower.CL,
              upper.CL)
complexityxfamilysize_means |> print(n=8)

# Plot
complexityxfamilysize_plot <- ggplot(
  complexityxfamilysize_means,
  aes(x = complexity,y = Estimate,
      group = family_size, colour = family_size, fill = family_size, linetype = family_size)) +
  geom_line(linewidth = 1) +
  geom_point(size = 3) +
  geom_ribbon(aes(ymin = lower.CL,
                  ymax = upper.CL),
              alpha = 0.2,
              colour = NA) +
  labs(x = "Complexity",
       y = "Estimated mean amplitude (µV)",
        title = "Complexity x Family Size Interaction",
        colour = "Complexity", 
        linetype = "Complexity", 
        fill = "Complexity") +
  my_theme +
  my_guides +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2)

familysizexcomplexity_plot <- ggplot(
  complexityxfamilysize_means,
  aes(x = family_size, y = Estimate, 
      group = complexity, colour = complexity, fill = complexity, linetype = complexity)) +
  geom_line(linewidth = 1) +
  geom_point(size = 3) +
  geom_ribbon(aes(ymin = lower.CL,
                  ymax = upper.CL),
              alpha = 0.2,
              colour = NA) +
  labs( x = "Family size", 
        y = "Estimated mean amplitude (µV)",
        title = "Family Size x Complexity Interaction",
        colour = "Complexity", 
        linetype = "Complexity", 
        fill = "Complexity") +
  my_theme +
  my_guides +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2)


```

##### Complexity × LP interaction averaged over Family Size:

```{r CMPxLPoverFS}
emm_complexity_LP_N400 <- emmeans(
  m_nw_N400_fs_symmetric,
  ~ complexity | LP,
  at = list(LP = c(-2.5, -1, 0, 1, 3)),
  lmerTest.limit = 6480
)

complexityxLP_table <- as.tibble(compact_emm_table(
  emm_complexity_LP_N400,
  by_var = LP,
  condition_prefix = "LP"
)) |> print(n = 20)
```

```{r include=FALSE}
complexityxLP_means <- complexityxLP_table |>
  filter(!grepl(" - ", Comparison)) |>
  mutate(
    LP = as.numeric(sub("LP = ", "", Condition)),
    complexity = factor(Comparison, levels = c("Simple", "Complex"))) |>
  select(complexity, LP, Estimate)

complexityxLP_means

complexityxLP_plot.a <- ggplot(
  complexityxLP_means,
  aes( x = LP, y = Estimate, group = complexity, colour = complexity, linetype = complexity)) +
  geom_line(linewidth = 1) +
  geom_point(size = 2) +
  labs( x = "Lexical Proficiency (LP)",
        y = "Estimated mean amplitude (µV)",
        title = " Complexity × LP interaction (averaged over Family Size)",
        colour = "Complexity",
        linetype = "Complexity") +
  theme(plot.title = element_text(hjust = 0.5))  + 
  my_theme +
  my_guides +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  coord_cartesian(
  xlim = c(-2.6, 3.1),
  ylim = c(-3.1, 2.1)
)
```

```{r include=FALSE}
# (complexityxLP_predicted_values <- ggpredict(
#   m_nw_N400_fs_symmetric,
#   terms = c("LP", "complexity")
# ))

(pred_CMP_LP <- ggemmeans(
  m_nw_N400_fs_symmetric,
  terms = c(
    "LP [all]",
    "complexity"
  )))

(complexityxLP_plot.b <- ggplot(pred_CMP_LP,
       aes(x = x,
           y = predicted,
           color = group,
           fill = group,
           linetype = group)) +
  geom_line(size = 1.2) +
  geom_ribbon(aes(ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              colour = NA) +
  labs(
    x = "Language Proficiency (LP)",
    y = "Predicted N400 amplitude (µV)",
    title = "Complexity x LP Interaction",
    color = "Complexity",
    fill = "Complexity",
    linetype = "Complexity"
  )  +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  scale_linetype_manual(values = my_linetypes_1) +
  my_theme +
  my_guides)
```

##### FS × LP interaction averaged over Complexity:

```{r FSxLPoverCMP}
emm_FS_LP_N400 <- emmeans(
  m_nw_N400_fs_symmetric,
  ~ family_size | LP,
  at = list(LP = c(-2.5, -1, 0, 1, 3)),
  lmerTest.limit = 6480
)

familysizexLP_table <- as.tibble(compact_emm_table(
  emm_FS_LP_N400,
  by_var = LP,
  condition_prefix = "LP"
)) |> print()
```


```{r include=FALSE}
(familysizexLP_means <- familysizexLP_table |>
  filter(!grepl(" - ", Comparison)) |>
  mutate(LP = as.numeric(sub("LP = ", "", Condition)),
         family_size = factor(Comparison, levels = c("Small", "Large"))) |>
  select(family_size, LP, Estimate, lower.CL, upper.CL))

familysizexLP_means

(familysizexLP_plot.a <- ggplot(
  familysizexLP_means,
  aes( x = LP, y = Estimate, 
       group = family_size, colour = family_size, fill = family_size, linetype = family_size)) +
  geom_line(linewidth = 1) +
  geom_point(size = 2) +
  labs( x = "Lexical Proficiency (LP)", 
        y = "Estimated mean amplitude (µV)",
       title = "Family Size x LP Interaction",
       colour = "Family Size", 
       linetype = "Family Size",
       fill = "Family Size") +
  my_theme +
  my_guides +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  coord_cartesian(
  xlim = c(-2.6, 3.1),
  ylim = c(-3.1, 2.1)
))
```

```{r include=FALSE}
# (familysizexLP_predicted_values <- ggpredict(
#   m_nw_N400_fs_symmetric,
#   terms = c("LP", "family_size")
# ))

(pred_FS_LP <- ggemmeans(
  m_nw_N400_fs_symmetric,
  terms = c(
    "LP [all]",
    "family_size"
  )))

(familysizexLP_plot.b <- ggplot(pred_FS_LP,
       aes(x = x,
           y = predicted,
           color = group,
           fill = group,
           linetype = group)) +
  geom_line(size = 1.2) +
  geom_ribbon(aes(ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              colour = NA) +
  labs(
    x = "Language Proficiency (LP)",
    y = "Predicted N400 amplitude (µV)",
    title = "Family Size x LP Interaction",
    color = "Family Size",
    fill = "Family Size",
    linetype = "Family Size"
  )  +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  scale_linetype_manual(values = my_linetypes_1) +
  my_theme +
  my_guides)
```


#### Complexity × Family Size × OS Interaction
##### Complexity ×  OS interaction averaged over Family Size:

```{r COMxOSoverFS}
emm_complexity_OS_N400 <- emmeans(
  m_nw_N400_fs_symmetric,
  ~ complexity | OS,
  at = list(OS = c(-1.9, -1, 0, 1, 1.9)),
  lmerTest.limit = 6480
)

complexityxOS_table <- as.tibble(compact_emm_table(
  emm_complexity_OS_N400,
  by_var = OS,
  condition_prefix = "OS"
)) |> print(n = 20)
```

```{r include=FALSE}
(complexityxOS_means <- complexityxOS_table |>
  filter(!grepl(" - ", Comparison)) |>
  mutate(
    OS = as.numeric(sub("OS = ", "", Condition)),
    complexity = factor(Comparison, levels = c("Simple", "Complex"))
  ) |>
  select(complexity, OS, Estimate))

(complexityxOS_plot.a <- ggplot(
  complexityxOS_means,
  aes( x = OS, y = Estimate, group = complexity, colour = complexity, linetype = complexity)) +
  geom_line(linewidth = 1) +
  geom_point(size = 2) +
  labs(x = "Orthographic Sensitivity (OS)",
       y = "Estimated mean amplitude (µV)",
       title = "Complexity x OS Interaction",
       colour = "Complexity", 
       linetype = "Complexity") +
  my_theme +
  my_guides +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  coord_cartesian(
  xlim = c(-2.6, 3.1),
  ylim = c(-3.1, 2.1)
))
```

```{r include=FALSE}

# (complexityxOS_predicted_values <- ggpredict(
#   m_nw_N400_fs_symmetric,
#   terms = c("OS", "complexity")
# ))

(pred_CMP_OS <- ggemmeans(
  m_nw_N400_fs_symmetric,
  terms = c(
    "OS [all]",
    "complexity"
  )))

(complexityxOS_plot.b <- ggplot(pred_CMP_OS,
       aes(x = x,
           y = predicted,
           color = group,
           fill = group,
           linetype = group)) +
  geom_line(size = 1.2) +
  geom_ribbon(aes(ymin = conf.low,
                  ymax = conf.high),
              alpha = 0.2,
              colour = NA) +
  labs(
    x = "Orthographic Sensitivity (OS)",
    y = "Predicted N400 amplitude (µV)",
    title = "Complexity x OS Interaction",
    color = "Complexity",
    fill = "Complexity",
    linetype = "Complexity"
  )  +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  scale_linetype_manual(values = my_linetypes_1) +
  my_theme +
  my_guides)
```




### PLOT 2-WAY INTERACTIONS

#### FAMILY SIZE X COMPLEXITY Plot

&nbsp;

```{r echo=FALSE, fig.height= 3}
plot_grid(complexityxfamilysize_plot, familysizexcomplexity_plot, ncol = 2)
```

#### COMPLEXITY x LP Plot; FAMILY SIZE X LP Plot; COMPLEXITY x OS Plot

&nbsp;

```{r include=FALSE}
plot_grid(complexityxLP_plot.a, 
          familysizexLP_plot.a, 
          complexityxOS_plot.a, 
          ncol = 3)
```

```{r echo=FALSE, fig.height=3}
plot_grid(complexityxLP_plot.b, familysizexLP_plot.b, complexityxOS_plot.b, ncol = 3 )
```


### PLOT 3-WAY INTERACTIONS

#### Plots: COMPLEXITY x LP faceted by Family size; FAMILY SIZE x  LP Faceted by Complexity 

&nbsp;

```{r plots_n400_nonwords_fs.3way, include=FALSE}
library(ggeffects)
library(ggplot2)

# Facet by Family Size
pred <- ggpredict(
  m_nw_N400_fs_symmetric,
  terms = c("LP [all]", "complexity", "family_size")
)

nw.n400.3way.A <- ggplot(pred,
       aes(x = x,
           y = predicted,
           colour = group,
           fill = group,
           linetype = group)) +
  geom_line(linewidth = 1.5) +
  geom_ribbon(aes(ymin = conf.low,
                  ymax = conf.high),
              alpha = .20,
              colour = NA) +
  facet_wrap(~facet) +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  scale_linetype_manual(values = my_linetypes_1) +
  labs(
    x = "Lexical Proficiency (LP)",
    y = "Predicted N400 amplitude (µV)",
    title = expression(
      beta == 0.229 * "," ~
      plain(SE) == 0.100 * "," ~
      italic(t)(4851) == 2.29 * "," ~
      italic(p) < .022 * "," ~
      eta[p]^2 == .001),
    colour = "Complexity",
    fill = "Complexity",
    linetype = "Complexity"
  ) +
my_theme +
 theme(plot.title = element_text(hjust = 0.5)) +
  my_guides

# Facet by Complexity
pred <- ggpredict(
  m_nw_N400_fs_symmetric,
  terms = c("LP[all]", "family_size", "complexity")
)

nw.n400.3way.B <- ggplot(pred,
       aes(x = x,
           y = predicted,
           colour = group,
           fill = group,
           linetype = group)) +
  geom_line(linewidth = 1.5) +
  geom_ribbon(aes(ymin = conf.low,
                  ymax = conf.high),
              alpha = .20,
              colour = NA,
              linetype = 0) +
  facet_wrap(~facet) +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  scale_linetype_manual(values = my_linetypes_1) +
  labs(
    x = "Lexical Proficiency (LP)",
    y = "Predicted N400 amplitude (µV)",
    title = expression(
      beta == 0.229 * "," ~
      plain(SE) == 0.100 * "," ~
      italic(t)(4851) == 2.29 * "," ~
      italic(p) < .022 * "," ~
      eta[p]^2 == .001),
    colour = "Family Size",
    fill = "Family Size",
    linetype = "Family Size"
  ) +
  my_theme +
  theme(plot.title = element_text(hjust = 0.5)) + 
  my_guides

```

&nbsp;

```{r echo=FALSE, fig.height=3, fig.width=5}
plot_grid(nw.n400.3way.B, ncol = 1)
```
 
#### COMPLEXITY x LP and FAMILY SIZE x  LP Interaction Plots

Plot Simple-Complex difference across LP

```{r include=FALSE}
library(emmeans)
library(dplyr)
library(ggplot2)

# Create a sequence of LP values across the observed range
LP_seq <- with(
  subset(erp_fs_nw, time_window == "N400"),
  seq(min(LP, na.rm = TRUE),
      max(LP, na.rm = TRUE),
      length.out = 100)
)

# Estimate complexity means at each LP value, separately by family_size
emm_complexity_by_LP_FS <- emmeans(
  m_nw_N400_fs_symmetric,
  ~ complexity | family_size * LP,
  at = list(LP = LP_seq)
)

# Compute Simple - Complex at each LP value and family_size level
complexity_diff_by_LP_FS <- pairs(emm_complexity_by_LP_FS) |>
  summary(infer = TRUE) |>
  as.data.frame()

head(complexity_diff_by_LP_FS)

# Plot graph

complexity_by_LP <- ggplot(
  complexity_diff_by_LP_FS,
  aes(x = LP,
      y = estimate,
      colour = family_size,
      fill = family_size,
      linetype = family_size)
) +
  geom_hline(yintercept = 0,
             linetype = "dashed",
             linewidth = 0.5) +
  geom_line(linewidth = 1.5) +
  geom_ribbon(aes(ymin = lower.CL,
                  ymax = upper.CL),
              alpha = 0.20,
              colour = NA) +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  labs(
    x = "Lexical Proficiency (LP)",
    y = "Simple - Complex difference in predicted N400 amplitude (µV)",
    colour = "Family Size",
    fill = "Family Size",
    linetype = "Family Size"
  ) +
  my_theme +
  my_guides
```

Plot Small Family - Large Family difference across LP

```{r include=FALSE}

library(emmeans)
library(dplyr)
library(ggplot2)

# Create a sequence of LP values across the observed range
LP_seq <- with(
  subset(erp_fs_nw, time_window == "N400"),
  seq(min(LP, na.rm = TRUE),
      max(LP, na.rm = TRUE),
      length.out = 100)
)

# Estimate family-size means at each LP value, separately by complexity
emm_family_by_LP_complexity <- emmeans(
  m_nw_N400_fs_symmetric,
  ~ family_size | complexity * LP,
  at = list(LP = LP_seq)
)

# Build an explicit Small - Large contrast
fs_levels <- emm_family_by_LP_complexity@levels$family_size

small_large_contrast <- rep(0, length(fs_levels))
small_large_contrast[fs_levels == "Small"] <-  1
small_large_contrast[fs_levels == "Large"] <- -1

# Compute Small - Large at each LP value and complexity level
family_size_diff_by_LP_complexity <- contrast(
  emm_family_by_LP_complexity,
  method = list("Small - Large" = small_large_contrast)
) |>
  summary(infer = TRUE) |>
  as.data.frame()

head(family_size_diff_by_LP_complexity)

# Plot graph
familysize_by_LP <- ggplot(
  family_size_diff_by_LP_complexity,
  aes(x = LP,
      y = estimate,
      colour = complexity,
      fill = complexity,
      linetype = complexity)
) +
  geom_hline(yintercept = 0,
             linetype = "dashed",
             linewidth = 0.5) +
  geom_line(linewidth = 1.5) +
  geom_ribbon(aes(ymin = lower.CL,
                  ymax = upper.CL),
              alpha = 0.20,
              colour = NA) +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  labs(
    x = "Lexical Proficiency (LP)",
    y = "Small - Large family-size difference in predicted N400 amplitude (µV)",
    colour = "Complexity",
    fill = "Complexity",
    linetype = "Complexity"
  ) +
  my_theme +
  my_guides
```

Print Both Plots

```{r  echo=FALSE, fig.height=4.5, fig.width=7}
row1 <- plot_grid(complexity_by_LP, familysize_by_LP,ncol = 2)

plot_grid(
  ggdraw() + draw_label("N400 NonWord Data", fontface = "bold"),
  row1,
  ncol = 1,
  rel_heights = c(0.08, 1)
)
```


#### Plots: COMPLEXITY x OS faceted by Family size; FAMILY SIZE x  OS Faceted by Complexity 

```{r 3way_OS, include=FALSE}
library(ggeffects)
library(ggplot2)

# Facet by Family Size
pred <- ggpredict(
  m_nw_N400_fs_symmetric,
  terms = c("OS [all]", "complexity", "family_size")
)

(nw.n400.3way.C <- ggplot(pred,
       aes(x = x,
           y = predicted,
           colour = group,
           fill = group,
           linetype = group)) +
  geom_line(linewidth = 1.5) +
  geom_ribbon(aes(ymin = conf.low,
                  ymax = conf.high),
              alpha = .20,
              colour = NA) +
  facet_wrap(~facet) +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  scale_linetype_manual(values = my_linetypes_1) +
  labs(
    x = "Orthographic Sensitivity (OS)",
    y = "Predicted N400 amplitude (µV)",
    title = expression(
      beta == 0.143 * "," ~
      plain(SE) == 0.138 * "," ~
      italic(t)(4851) == 1.04 * "," ~
      italic(p) < .3),
    colour = "Complexity",
    fill = "Complexity",
    linetype = "Complexity"
  ) +
  my_theme +
  theme(plot.title = element_text(hjust = 0.5)) + 
  my_guides)

# Facet by Complexity
pred <- ggpredict(
  m_nw_N400_fs_symmetric,
  terms = c("OS[all]", "family_size", "complexity")
)

(nw.n400.3way.D <- ggplot(pred,
       aes(x = x,
           y = predicted,
           colour = group,
           fill = group,
           linetype = group)) +
  geom_line(linewidth = 1.5) +
  geom_ribbon(aes(ymin = conf.low,
                  ymax = conf.high),
              alpha = .20,
              colour = NA,
              linetype = 0) +
  facet_wrap(~facet) +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  scale_linetype_manual(values = my_linetypes_1) +
  labs(
    x = "Orthographic Sensitivity (OS)",
    y = "Predicted N400 amplitude (µV)",
    title = expression(
      beta == 0.143 * "," ~
      plain(SE) == 0.138 * "," ~
      italic(t)(4851) == 1.04 * "," ~
      italic(p) < .3),
    colour = "Family Size",
    fill = "Family Size",
    linetype = "Family Size"
  ) +
  my_theme +
  theme(plot.title = element_text(hjust = 0.5)) + 
  my_guides)

```
&nbsp;

```{r echo=FALSE, fig.height=3, fig.width=5}
plot_grid( nw.n400.3way.D, ncol = 1)
```


Plot Small Family - Large Family difference across OS

```{r include=FALSE}

library(emmeans)
library(dplyr)
library(ggplot2)

# Create a sequence of OS values across the observed range
OS_seq <- with(
  subset(erp_fs_nw, time_window == "N400"),
  seq(min(OS, na.rm = TRUE),
      max(OS, na.rm = TRUE),
      length.out = 100)
)

# Estimate family-size means at each OS value, separately by complexity
emm_family_by_OS_complexity <- emmeans(
  m_nw_N400_fs_symmetric,
  ~ family_size | complexity * OS,
  at = list(OS = OS_seq)
)

# Build an explicit Small - Large contrast
fs_levels <- emm_family_by_OS_complexity@levels$family_size

small_large_contrast <- rep(0, length(fs_levels))
small_large_contrast[fs_levels == "Small"] <-  1
small_large_contrast[fs_levels == "Large"] <- -1

# Compute Small - Large at each OS value and complexity level
family_size_diff_by_OS_complexity <- contrast(
  emm_family_by_OS_complexity,
  method = list("Small - Large" = small_large_contrast)
) |>
  summary(infer = TRUE) |>
  as.data.frame()

head(family_size_diff_by_OS_complexity)

# Plot graph
familysize_by_OS <- ggplot(
  family_size_diff_by_OS_complexity,
  aes(x = OS,
      y = estimate,
      colour = complexity,
      fill = complexity,
      linetype = complexity)
) +
  geom_hline(yintercept = 0,
             linetype = "dashed",
             linewidth = 0.5) +
  geom_line(linewidth = 1.5) +
  geom_ribbon(aes(ymin = lower.CL,
                  ymax = upper.CL),
              alpha = 0.20,
              colour = NA) +
  scale_colour_manual(values = my_palette_2) +
  scale_fill_manual(values = my_palette_2) +
  labs(
    x = "Lexical Proficiency (OS)",
    y = "Small - Large family-size difference in predicted N400 amplitude (µV)",
    colour = "Complexity",
    fill = "Complexity",
    linetype = "Complexity"
  ) +
  my_theme +
  my_guides

```



# DATA CHECKS

```{r}
nrow(subset(erp_bf_nw, time_window == "N400"))
nrow(subset(erp_fs_nw, time_window == "N400"))
length(unique(subset(erp_bf_nw, time_window == "N400")$SubjID))
length(unique(subset(erp_fs_nw, time_window == "N400")$SubjID))
```
```{r}
summary(subset(erp_bf_nw, time_window == "N400")$value)
summary(subset(erp_fs_nw, time_window == "N400")$value)
sd(subset(erp_bf_nw, time_window == "N400")$value)
sd(subset(erp_fs_nw, time_window == "N400")$value)
```

```{r}
m_check_bf <- lmer(value ~ complexity*OS + (1|SubjID) + (1|SubjID:chlabel),
                    data = subset(erp_bf_nw, time_window == "N400"))
m_check_fs <- lmer(value ~ complexity*OS + (1|SubjID) + (1|SubjID:chlabel),
                    data = subset(erp_fs_nw, time_window == "N400"))
summary(m_check_bf)
summary(m_check_fs)
```

```{r}
table(erp_bf_nw$base_frequency)
table(erp_fs_nw$family_size)
```

